### 2023-10-28 recs-abund-yield-parameters.qmd
initial commit

---
title: "Recruits, abundance, and yield time series and contours"
author: "Botsford, Hastings, White, and Kilduff"
execute: 
  warning: false
format:
  html: 
    page-layout: full
    embed-resources: true
    anchor-sections: true
    fig-width: 7
    fig-height: 5
  pdf:
    fig-width: 7
    fig-height: 5
  docx:
    fig-width: 7
    fig-height: 5
editor: visual
params:
  experiment: "larval_pool_blue_rockfish_mei_135_75"
---

```{r}
#| label: Extract experiemental parameters
#| echo: false

exp <- params$experiment

valid_dispersal <- c("larval_pool", "no_dispersal")
valid_species <- c("blue_rockfish", "cabezon", "china_rockfish", "pacific_cod", "kelp_bass")
valid_noise <- c("mei_135_75", "white_135_75")

current_dispersal <- valid_dispersal[stringr::str_detect(exp, valid_dispersal)]
current_species <- valid_species[stringr::str_detect(exp, valid_species)]
current_noise <- valid_noise[stringr::str_detect(exp, valid_noise)]

pretty_dispersal <- c("Larval pool", "No dispersal")
pretty_species <- c("Blue rockfish", "Cabezon", "China rockfish", "Pacific cod", "Kelp bass")
pretty_noise <- c("ENSO", "White")

nice_dispersal <- pretty_dispersal[stringr::str_detect(exp, valid_dispersal)]
nice_species <- pretty_species[stringr::str_detect(exp, valid_species)]
nice_noise <- pretty_noise[stringr::str_detect(exp, valid_noise)]

out_path <- file.path("output", current_species)

if (!dir.exists(out_path)) {
  dir.create(out_path, recursive = TRUE) 
}

```

### Experiment: `r params$experimenft`

This is a parameterized report for:

-   `r nice_species`
-   `r nice_noise`
-   `r nice_dispersal`

```{r}
#| label: load-packages-data
#| echo: false

library(targets)
suppressMessages(library(tidyverse))
library(duckdb)
options(dplyr.summarise.inform = FALSE)
# Load relevant data from target objexts
tar_load(sim_len)
tar_load(species_flep_fished_ind)
tar_load(fishing_mortality_values)
tar_load(species_parms)
tar_load(sim_species_parms)
tar_load(sim_species_derived_vars)

# Load project functions
source("R/functions.R")

# constants
burn_in_parm <- 500
sim_len_parm <- 135

x_text_position_parm <- 550

waa_g <- sim_species_parms[[nice_species]][["biom_const"]] * sim_species_derived_vars[[nice_species]][["length_at_age"]] ^
                    sim_species_parms[[nice_species]][["biom_exp"]]

# use functions to create useful data structures
# FLEP to F reference tables by species
spec_fleps_2_fs <-
  get_fs_from_fleps(species = nice_species,
                    flep_inds = species_flep_fished_ind,
                    f_vals =  fishing_mortality_values)

```

```{r}
#| label: functions
#| echo: false

# query specified simulation results and aggregate yield or recruits for subsequent analyses
qry_results_table_agg <- function(ddb_table,
                                  metric = c("recruits", "yield", "abundance"),
                                  burn_in = 500,
                                  sim_len = 135,
                                  reserve_fracs = NULL,
                                  flep_ratios = NULL,
                                  dir_duckdb = "data/sim_out.duckdb") {
  sim_yrs <- burn_in + sim_len
  age_filter <- ifelse(metric == "recruits", "age = 1 and ", "")

  reserve_fracs_qry <- ifelse(length(reserve_fracs) > 0,
                              paste0(" and cast(reserve_frac as decimal(5, 2)) in (", stringr::str_flatten_comma(format(reserve_fracs,  nsmall = 2)), ")"),
                              "")
  flep_ratios_qry <- ifelse(length(flep_ratios) > 0, 
                           paste0(" and cast(reserve_frac as decimal(5, 2)) in (", stringr::str_flatten_comma(format(flep_ratios, nsmall = 2)), ")"),
                           "")

  agg_qry <-
    paste0(
      "SELECT experiment, noise, species, bh_alpha, rec_sd, reserve_frac,
             flep_ratio, sim_num, year, age, sum(",
      ifelse(metric == "yield", "yield", "number"), ") as ",  metric,
      " FROM '", ddb_table,
      "' WHERE ", age_filter, "year > ", burn_in,
      " and year <= ", sim_yrs,
      reserve_fracs_qry, 
      flep_ratios_qry,
      " GROUP BY experiment, noise, species, bh_alpha, rec_sd, reserve_frac, flep_ratio, sim_num, year, age
        ORDER BY experiment, noise, species, bh_alpha, rec_sd, reserve_frac, flep_ratio, sim_num, year, age"
    )
  con <- DBI::dbConnect(duckdb::duckdb(),
                      dbdir = dir_duckdb,
                      read_only = FALSE)
  agg_df <- dbGetQuery(con, agg_qry)
  DBI::dbDisconnect(con, shutdown = TRUE)
  return(dplyr::tibble(agg_df))
}

make_df_yield_exp_spec_noise_rec_fs <-
  function(df_exp_spec_noise_rec,
           fleps_2_fs,
           f_maxes_yield) {
    df_exp_spec_noise_rec_fs <- df_exp_spec_noise_rec |>
      left_join(.,
                y = fleps_2_fs,
                by = join_by(flep_ratio_ch == flep_vals_ch)) %>%
      dplyr::mutate(f_fmsy = round(f_vals / f_maxes_yield, 2))
    return(df_exp_spec_noise_rec_fs)
  }

get_exp_details <- function(df_after_qry_results_table_agg) {
  exp_details <- df_after_qry_results_table_agg %>%
  summarise(experiment = unique(experiment), 
            noise = unique(noise),
            species = unique(species),
            bh_alpha = round(unique(bh_alpha), 4),
            rec_sd = unique(rec_sd))
  return(exp_details)
}

get_f_maxes_yield <- function(yield_disp_sp_noise, 
                              fleps_2_fs) {
  # Find the fishing mortality level that maximizes yield
  # with no reserves
  F_maxes_yield <- yield_disp_sp_noise %>%
  dplyr::filter(near(reserve_frac, 0)) %>%
  dplyr::left_join(., y = fleps_2_fs, by = join_by(flep_ratio_ch == flep_vals_ch)) %>%
  dplyr::group_by(f_vals, flep_ratio) %>%
  dplyr::summarise(yields = sum(yield)) %>%
  dplyr::ungroup() %>%
  dplyr::filter(yields == max(yields)) %>%
  .$f_vals

  return(F_maxes_yield[[1]])
}

# Time series prep tplotting function
make_df_exp_spec_noise_rec_fs <- function(df_exp_spec_noise_rec,
                                          fleps_2_fs,
                                          f_maxes_yield) {
  df_exp_spec_noise_rec_fs <- df_exp_spec_noise_rec %>%
    mutate(flep_ratio_ch = as.character(flep_ratio)) %>%
      left_join(., y = fleps_2_fs, by = join_by(flep_ratio_ch == flep_vals_ch)) %>%
      dplyr::mutate(f_fmsy = round(f_vals / f_maxes_yield, 2)) %>%
    select(-flep_vals)
  return(df_exp_spec_noise_rec_fs)
}

prep_ann_yield_for_plot <- function(df_exp_spec_noise_rec_fs,
                                    frac_reserves = c(0, 0.25, 0.50),
                                    f_fmsys = c(0.52, 1.00, 2.09)) {

  if (length(f_fmsys) < 1 | is.null(f_fmsys)) {
    stop("Please specify f_fmsy values to use")
  }

  if (length(frac_reserves) < 1 | is.null(frac_reserves)) {
    stop("Please specify frac_reserves values to use")
  }

  # make a sub function
    med_yield <- df_exp_spec_noise_rec_fs %>%
      dplyr::filter(near(f_fmsy, 1), near(reserve_frac, 0))  %>%
      dplyr::group_by(
        experiment,
        noise,
        species,
        bh_alpha,
        rec_sd,
        reserve_frac,
        flep_ratio,
        sim_num,
        year
      ) %>%
      dplyr::summarise(ann_yield = sum(yield)) %>%
      dplyr::ungroup() %>%
      dplyr::summarise(med_yield_f_fmsy = median(ann_yield)) %>%
      .$med_yield_f_fmsy

    # make a sub function
    main_plt_df <- df_exp_spec_noise_rec_fs %>%
      dplyr::filter(reduce(map(
        frac_reserves, near, x = reserve_frac, tol = 1e-4
      ), `|`)) %>%
      dplyr::group_by(reserve_frac, flep_ratio, f_fmsy, year) %>%
      dplyr::summarize(annual_yield = sum(yield)) %>%
      dplyr::ungroup() %>%
      dplyr::filter(reduce(map(
        f_fmsys, near, x = f_fmsy, tol = 1e-4
      ), `|`))

    # make a sub function
    supp_plt_df <- main_plt_df %>%
      dplyr::mutate(below_thresh = if_else(annual_yield <= med_yield, 1, 0)) %>%
      dplyr::group_by(reserve_frac, f_fmsy) %>%
      dplyr::summarize(
        mean_yield = round(mean(annual_yield, na.rm = TRUE), 2),
        mean_yield_lab = paste0("Mean yield: ", mean_yield),
        sd_yield = round(sd(annual_yield, na.rm = TRUE), 2),
        sd_yield_lab = paste0("SD yield: ", sd_yield),
        cv_yield = round(sd(annual_yield, na.rm = TRUE)/mean(annual_yield, na.rm = TRUE), 2),
        cv_yield_lab = paste0("CV yield: ", cv_yield),
        yrs_below_thresh = paste("% YR below thresh: ", round(sum(below_thresh)/135, 2))
      )
    return(list(main_plt_df, supp_plt_df, med_yield))
  }

prep_ann_abund_for_plot <- function(df_exp_spec_noise_rec_fs,
                                    frac_reserves = c(0, 0.25, 0.50),
                                    f_fmsys = c(0.52, 1.00, 2.09)) {

  if (length(f_fmsys) < 1 | is.null(f_fmsys)) {
    stop("Please specify f_fmsy values to use")
  }

  if (length(frac_reserves) < 1 | is.null(frac_reserves)) {
    stop("Please specify frac_reserves values to use")
  }

  # make a sub function
    med_biomass <- df_exp_spec_noise_rec_fs %>%
      dplyr::filter(near(f_fmsy, 1), near(reserve_frac, 0))  %>%
      dplyr::group_by(
        experiment,
        noise,
        species,
        bh_alpha,
        rec_sd,
        reserve_frac,
        flep_ratio,
        sim_num,
        year
      ) %>%
      dplyr::summarise(ann_biomass = sum(biomass_at_age)) %>%
      dplyr::ungroup() %>%
      dplyr::summarise(med_biomass_f_fmsy = median(ann_biomass)) %>%
      .$med_biomass_f_fmsy

    # make a sub function
    main_plt_df <- df_exp_spec_noise_rec_fs %>%
      dplyr::filter(reduce(map(
        frac_reserves, near, x = reserve_frac, tol = 1e-4
      ), `|`)) %>%
      dplyr::group_by(reserve_frac, flep_ratio, f_fmsy, year) %>%
      dplyr::summarize(annual_biomass = sum(biomass_at_age)) %>%
      dplyr::ungroup() %>%
      dplyr::filter(reduce(map(
        f_fmsys, near, x = f_fmsy, tol = 1e-4
      ), `|`))

    # make a sub function
    supp_plt_df <- main_plt_df %>%
      dplyr::mutate(below_thresh = if_else(annual_biomass <= med_biomass, 1, 0)) %>%
      dplyr::group_by(reserve_frac, f_fmsy) %>%
      dplyr::summarize(
        mean_biomass = round(mean(annual_biomass, na.rm = TRUE), 2),
        mean_biomass_lab = paste0("Mean biomass: ", mean_biomass),
        sd_biomass = round(sd(annual_biomass, na.rm = TRUE), 2),
        sd_biomass_lab = paste0("SD biomass: ", sd_biomass),
        cv_biomass = round(sd(annual_biomass, na.rm = TRUE)/mean(annual_biomass, na.rm = TRUE), 2),
        cv_biomass_lab = paste0("CV yield: ", cv_biomass),
        yrs_below_thresh = paste("YR below thresh: ", sum(below_thresh))
      )
    return(list(main_plt_df, supp_plt_df, med_biomass))
  }

facet_yield_ts_plots <- function(main_plt_df,
                                 sub_plt_df,
                                 yield_thresh,
                                 text = TRUE,
                                 exp_deets_df,
                                 x_min = 600,
                                 x_max = 635,
                                 x_text_val = (x_max) - (x_max - x_min)/2) {

  plt_species <- unique(exp_deets_df$species)
  plt_dispersal <- unique(exp_deets_df$experiment)
  plt_noise <- unique(exp_deets_df$noise)
  plt_alpha <- round(unique(exp_deets_df$bh_alpha), 3)
  plt_sd <- unique(exp_deets_df$rec_sd)

  title_string <- paste0("Simulation results for: ", plt_species, 
                         " with ", plt_dispersal, " and ", plt_noise, " noise. \n", 
                         # "Pop dy parms: \n- BH alpha = ", plt_alpha, 
                         "\n- noise sd = ", plt_sd)

  quants_df <- main_plt_df %>%
    dplyr::group_by(reserve_frac, f_fmsy) %>%
    summarize(quant_80 = quantile(annual_yield, 0.8), 
              quant_20 = quantile(annual_yield, 0.2))

  ggplot(main_plt_df, aes(x = year, y = annual_yield)) +
    facet_grid(reserve_frac ~ f_fmsy,
               labeller = labeller(f_fmsy = label_both,
                                   reserve_frac = label_both)) +
    geom_ribbon(aes(
      ymin = yield_thresh,
      ymax = pmin(annual_yield, yield_thresh),
      fill = "Yield lower"
    )) +
    geom_ribbon(aes(
      ymin = annual_yield,
      ymax = pmin(annual_yield, yield_thresh),
      fill = "Yield higher"
    )) +
    scale_fill_manual(values = c("black", "white")) +
    {if (text) geom_text(
      data = sub_plt_df,
      x = x_text_val,
      y = 9500,
      size = 2.5,
      aes(label = mean_yield_lab)
    )} +
    {if (text) geom_text(
      data = sub_plt_df,
      x = x_text_val,
      y = 11500,
      size = 2.5,
      aes(label = sd_yield_lab)
    )} +
    {if (text) geom_text(
      data = sub_plt_df,
      x = x_text_val,
      y = 12500,
      size = 2.5,
      aes(label = yrs_below_thresh)
    )} +
    {if (text) geom_text(
      data = sub_plt_df,
      x = x_text_val,
      y = 10500,
      size = 2.5,
      aes(label = cv_yield_lab)
    )} +
    labs(fill = "Above/Below Yield threshold") +
    ggtitle(title_string) +
    xlab("Year") +
    ylab("Yield (metric tons)") +
    # ylim(0, 15000) +
    ylim(0, 12500) +
    xlim(x_min, x_max) +
    labs(colour = "Reserve\nfraction") +
    theme_grey() +
    geom_hline(data = quants_df, aes(yintercept = quant_80), colour = "orange", linewidth = 1.1, linetype = 1) +
    geom_hline(data = quants_df, aes(yintercept = quant_20), colour = "orange", linewidth = 1.1, linetype = 1) +
    theme(
      axis.line = element_line(colour = "black"),
      panel.background = element_rect(fill = "grey60"),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      legend.position="none"
    )
}

facet_biomass_ys_plots <- function(main_plt_df,
                                 sub_plt_df,
                                 biomass_thresh,
                                 exp_deets_df,
                                 x_text_val = 550) {

  plt_species <- unique(exp_deets_df$species)
  plt_dispersal <- unique(exp_deets_df$experiment)
  plt_noise <- unique(exp_deets_df$noise)
  plt_alpha <- round(unique(exp_deets_df$bh_alpha), 3)
  plt_sd <- unique(exp_deets_df$rec_sd)

  title_string <- paste0("Simulation results for: ", plt_species, 
                         " with ", plt_dispersal, " and ", plt_noise, " noise. \n", 
                         # "Pop dy parms: \n- BH alpha = ", plt_alpha, 
                         "\n- noise sd = ", plt_sd)

  quants_df <- main_plt_df %>%
    dplyr::group_by(reserve_frac, f_fmsy) %>%
    summarize(quant_80 = quantile(annual_biomass, 0.8),
              quant_20 = quantile(annual_biomass, 0.2))

  ggplot(main_plt_df, aes(x = year, y = annual_biomass)) +
    facet_grid(reserve_frac ~ f_fmsy,
               labeller = labeller(f_fmsy = label_both,
                                   reserve_frac = label_both)) +
    geom_ribbon(aes(
      ymin = biomass_thresh,
      ymax = pmin(annual_biomass, biomass_thresh),
      fill = "Yield lower"
    )) +
    geom_ribbon(aes(
      ymin = annual_biomass,
      ymax = pmin(annual_biomass, biomass_thresh),
      fill = "Yield higher"
    )) +
    scale_fill_manual(values = c("black", "white")) +
    # geom_text(
    #   data = sub_plt_df,
    #   x = x_text_val,
    #   y = 11000,
    #   aes(label = mean_biomass_lab)
    # ) +
    # geom_text(
    #   data = sub_plt_df,
    #   x = x_text_val,
    #   y = 12500,
    #   aes(label = sd_biomass_lab)
    # ) +
    # geom_text(
    #   data = sub_plt_df,
    #   x = x_text_val,
    #   y = 14000,
    #   aes(label = yrs_below_thresh)
    # ) +
    # geom_text(
    #   data = sub_plt_df,
    #   x = x_text_val,
    #   y = 9500,
    #   aes(label = cv_biomass_lab)
    # ) +
    labs(fill = "Above/Below Biomass threshold") +
    ggtitle(title_string) +
    xlab("Year") +
    ylab("Biomass (metric tons)") +
    ylim(0, NA) +
    labs(colour = "Reserve\nfraction") +
    theme_grey() +
    geom_hline(data = quants_df, aes(yintercept = quant_80), colour = "orange", linewidth = 1.1, linetype = 1) +
    geom_hline(data = quants_df, aes(yintercept = quant_20), colour = "orange", linewidth = 1.1, linetype = 1) +
    theme(
      axis.line = element_line(colour = "black"),
      panel.background = element_rect(fill = "grey60"),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.border = element_blank()
    )
}

# Recruits TS above/below thresh time series

# Recruit time series
prep_ann_recs_for_plot <- function(df_exp_spec_noise_rec_fs,
                                   fleps_2_fs,
                                   f_maxes_yield,
                                   frac_reserves = c(0, 0.25, 0.50),
                                   f_fmsys = c(0, 0.52, 1.00, 1,43, 2.09),
                                   sp_parms,
                                   spc) {
  if (length(f_fmsys) < 1 | is.null(f_fmsys)) {
    stop("Please specify f_fmsy values to use")
  }

  if (length(frac_reserves) < 1 | is.null(frac_reserves)) {
    stop("Please specify frac_reserves values to use")
  }

  t_c <- sp_parms[which(sp_parms$species == spc), ]$A_fish

  main_plt_df <- df_exp_spec_noise_rec_fs |>
    left_join(., y = fleps_2_fs, by = join_by(flep_ratio == flep_vals)) |>
    dplyr::mutate(f_fmsy = round(f_vals / f_maxes_yield, 2)) |>
    dplyr::filter(reduce(map(
      frac_reserves, near, x = reserve_frac, tol = 1e-4
    ), `|`),
    reduce(map(
      f_fmsys, near, x = f_fmsy, tol = 1e-4
    ), `|`))

  # make a sub function
  recruit_thresh <- main_plt_df %>%
    dplyr::filter(near(f_fmsy, 1), near(reserve_frac, 0)) %>%
    dplyr::summarize(med_recs_f_fmsy = median(recruits)) %>%
    .$med_recs_f_fmsy

  supp_plt_df <- main_plt_df %>%
  dplyr::filter(year > 500) %>%
  dplyr::mutate(below_thresh = if_else(recruits <= recruit_thresh, 1, 0)) %>%
  dplyr::group_by(reserve_frac, f_fmsy) |>
      dplyr::summarize(
        mean_recruits = round(mean(recruits, na.rm = TRUE), 2),
        sd_recruits = round(sd(recruits, na.rm = TRUE), 2),
        cv_recruits = round(sd_recruits/mean_recruits, 2),
        yrs_below_thresh = paste("YR below thresh: ", sum(below_thresh))
      ) |>
        dplyr::ungroup() |>
        dplyr::mutate(mean_recruits_lab = paste0("Mean recruits: ", format(mean_recruits, 
                                                             big.mark = ",",
                                                             scientific = FALSE)),
                      sd_recruits_lab = paste0("SD recruits: ", format(sd_recruits, 
                                                             big.mark = ",",
                                                             scientific = FALSE)),
                      cv_recruits_lab = paste0("CV recruits: ", format(cv_recruits, 
                                                             big.mark = ",",
                                                             scientific = FALSE)))
  return(list(main_plt_df, supp_plt_df, recruit_thresh))
}

facet_recs_ts_plots <- function(main_plt_df,
                                sub_plt_df,
                                yield_sub_plt,
                                recruit_thresh,
                                exp_deets_df,
                                x_text_val = 550) {
  ggplot(data = main_plt_df |> filter(year > 500),
       aes(x = year, y = recruits)) +
  geom_ribbon(aes(
      ymin = recruit_thresh,
      ymax = pmin(recruits, recruit_thresh),
      fill = "Recruits lower"
    )) +
    geom_ribbon(aes(
      ymin = recruits,
      ymax = pmin(recruits, recruit_thresh),
      fill = "Recruits higher"
    )) +
    scale_fill_manual(values = c("black", "white")) +
  facet_grid(reserve_frac ~ f_fmsy,
             labeller = labeller(f_fmsy = label_both,
                                 reserve_frac = label_both)) +
      geom_text(
      data = sub_plt_df,
      x = x_text_val,
      y = 4E6,
      aes(label = mean_recruits_lab),
      size = 3
    ) +
    geom_text(
      data = sub_plt_df,
      x = x_text_val,
      y = 4.5E6,
      aes(label = sd_recruits_lab),
      size = 3
    ) +
    geom_text(
      data = sub_plt_df,
      x = x_text_val,
      y = 5E6,
      aes(label = yrs_below_thresh),
      size = 3
    ) +
    geom_text(
      data = sub_plt_df,
      x = x_text_val,
      y = 3.5E6,
      aes(label = cv_recruits_lab),
      size = 3
    ) + 
    geom_text(
      data = yield_sub_plt,
      x = x_text_val,
      y = 5.5E6,
      aes(label = mean_yield_lab),
      size = 3
    ) +
    labs(fill = "Above/Below Recruit threshold") +
    ylim(0, 7e6) +
  theme_grey()  +
  theme(
    axis.line = element_line(colour = "black"),
    panel.background = element_rect(fill = "grey60"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank()
  ) +
  ylab("Recruits") +
  xlab("Year")

}

# Contour plot functions: yield

get_sp_disp_noise_yield_gcols <- function(sp_disp_noise_yield_prep) {
  sp_disp_noise_yield_prep_gcols <- sp_disp_noise_yield_prep %>%
    select(all_of(
      c(
        "reserve_frac",
        "flep_ratio",
        "f_vals",
        "f_fmsy",
        "year",
        "age",
        "yield"
      )
    ))

  return(sp_disp_noise_yield_prep_gcols)
}

get_sp_disp_noise_abund_gcols <- function(sp_disp_noise_abund_prep) {
  sp_disp_noise_abund_prep_gcols <- sp_disp_noise_abund_prep %>%
    select(all_of(
      c(
        "reserve_frac",
        "flep_ratio",
        "f_vals",
        "f_fmsy",
        "year",
        "age",
        "biomass_at_age"
      )
    ))

  return(sp_disp_noise_abund_prep_gcols)
}

calc_sp_disp_noise_gcols_ann_yield <- function(sp_disp_noise_yield_prep_gcols) {
  sp_disp_noise_yield_gcols_ann_yield <- sp_disp_noise_yield_prep_gcols %>%
  group_by(reserve_frac, f_vals, f_fmsy, year) %>%
  summarise(ann_yield = sum(yield)) %>%
  ungroup() 
  return(sp_disp_noise_yield_gcols_ann_yield)
}

calc_sp_disp_noise_gcols_ann_abund <- function(sp_disp_noise_abund_prep_gcols) {
  sp_disp_noise_abund_gcols_ann<- sp_disp_noise_abund_prep_gcols %>%
  group_by(reserve_frac, f_vals, f_fmsy, year) %>%
  summarise(ann_biomass = sum(biomass_at_age)) %>%
  ungroup() 
  return(sp_disp_noise_abund_gcols_ann)
}

calc_sp_disp_noise_yield_gcols_med_ann_yield <- function(sp_disp_noise_yield_prep_gcols) {
  sp_disp_noise_yield_gcols_med_ann_yield <- sp_disp_noise_yield_prep_gcols %>%
  group_by(reserve_frac, f_vals, f_fmsy, year) %>%
  summarise(ann_yield = sum(yield)) %>%
  ungroup() %>%
  group_by(reserve_frac, f_vals,  f_fmsy) %>%
  summarise(median_ann_yield = median(ann_yield)) %>%
  ungroup()
  return(sp_disp_noise_yield_gcols_med_ann_yield)
}

calc_sp_disp_noise_abund_gcols_med_ann_abund <- function(sp_disp_noise_abund_prep_gcols) {
  sp_disp_noise_abund_gcols_med_ann_abund <- sp_disp_noise_abund_prep_gcols %>%
  group_by(reserve_frac, f_vals, f_fmsy, year) %>%
  summarise(ann_biomass = sum(biomass_at_age)) %>%
  ungroup() %>%
  group_by(reserve_frac, f_vals,  f_fmsy) %>%
  summarise(median_ann_biomass = median(ann_biomass)) %>%
  ungroup()
  return(sp_disp_noise_abund_gcols_med_ann_abund)
}

get_f_maxes_med_ann_yield <- function(sp_disp_noise_yield_gcols_med_ann_yield) {
  f_max_median_ann_yield <- sp_disp_noise_yield_gcols_med_ann_yield %>%
  filter(median_ann_yield == max(median_ann_yield)) %>%
  .$f_vals

  try(if(length(f_max_median_ann_yield) == 0) stop("no F that maxes yield was found"))

  if (length(f_max_median_ann_yield) > 1) {

    return(f_max_median_ann_yield[1]) 
  }

  return(f_max_median_ann_yield)
}

calc_sp_disp_noise_yield_gcols_ann_yield_ffmsy <- function(sp_disp_noise_yield_gcols_ann_yield, 
                                                      f_max_median_ann_yield) {

  sp_disp_noise_yield_gcols_ann_yield_ffmsy <- sp_disp_noise_yield_gcols_ann_yield %>%
    mutate(f_fmsy = f_vals / f_max_median_ann_yield)

  return(sp_disp_noise_yield_gcols_ann_yield_ffmsy)
}

calc_sp_disp_noise_abund_gcols_ann_abund_ffmsy <- function(sp_disp_noise_abund_gcols_ann_abund, 
                                                      f_max_median_ann_yield) {

  sp_disp_noise_abund_gcols_ann_abund_ffmsy <- sp_disp_noise_abund_gcols_ann_abund %>%
    mutate(f_fmsy = f_vals / f_max_median_ann_yield)

  return(sp_disp_noise_abund_gcols_ann_abund_ffmsy)
}

calc_sp_disp_noise_yield_frac_below_med_max_yield <- function(sp_disp_noise_yield_gcols_ann_yield_ffmsy,
                                                              max_median_ann_yield) {

  # if (is.na(max_median_ann_yield)) {
  #   max_median_ann_yield <- sp_disp_noise_yield_gcols_ann_yield_ffmsy %>% 
  #   group_by(reserve_frac, f_vals, f_fmsy) %>%
  #   summarise(median_ann_yield = median(ann_yield)) %>%
  #   ungroup() %>%
  #   filter(median_ann_yield == max(median_ann_yield)) %>% 
  #   .$median_ann_yield
  # }

  sp_disp_noise_yield_frac_below_med_max_yield <-
      sp_disp_noise_yield_gcols_ann_yield_ffmsy %>%
      mutate(below_yield_thresh = if_else(ann_yield < max_median_ann_yield, 1, 0)) %>%
      group_by(reserve_frac, f_fmsy) %>%
      summarise(n_yrs_below = sum(below_yield_thresh)) %>%
      ungroup() %>%
      mutate(frac_below_med_yield_f_max = round(n_yrs_below / sim_len, 3))
    return(sp_disp_noise_yield_frac_below_med_max_yield)
}

calc_sp_disp_noise_abund_frac_below_med_max_abund <- function(sp_disp_noise_abund_gcols_ann_abund_ffmsy,
                                                              max_median_ann_abund) {

  # if (is.na(max_median_ann_abund)) {
  #   max_median_ann_abund <- sp_disp_noise_abund_gcols_ann_abund_ffmsy %>% 
  #   group_by(reserve_frac, f_vals, f_fmsy) %>%
  #   summarise(median_ann_biomass = median(ann_biomass)) %>%
  #   ungroup() %>%
  #   filter(median_ann_biomass == max(median_ann_biomass)) %>% 
  #   .$median_ann_biomass
  # }

  sp_disp_noise_abund_frac_below_med_max_abund <-
      sp_disp_noise_abund_gcols_ann_abund_ffmsy %>%
      mutate(below_thresh_ann_yield = if_else(ann_biomass < max_median_ann_abund, 1, 0)) %>%
      group_by(reserve_frac, f_fmsy) %>%
      summarise(n_yrs_below = sum(below_thresh_ann_yield)) %>%
      ungroup() %>%
      mutate(frac_below_med_abund_f_max = round(n_yrs_below / sim_len, 3))
    return(sp_disp_noise_abund_frac_below_med_max_abund)
}

make_contour_plt_sp_disp_noise_frac_below_med_max_yield <-
  function(sp_disp_noise_yield_frac_below_med_max_yield,
           species_name,
           dispersal,
           noise_type,
           max_f_fmsy,
           max_reserve_frac) {
    sp_disp_noise_yield_frac_below_med_max_yield_plt <-
      sp_disp_noise_yield_frac_below_med_max_yield %>%
      filter(reserve_frac <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
      ggplot(data = .,
             aes(x = reserve_frac, y = f_fmsy, z = frac_below_med_yield_f_max)) +
      geom_contour_filled(bins = 12) +
      ggtitle(paste0(
        species_name,
        " ",
        dispersal,
        " ",
        noise_type,
        ":\nTime below median max yield"
      )) +
      xlab("Reserve fraction") +
      ylab("F/Fmsy") +
      scale_fill_viridis_d(option = "D", direction = -1) +
      geom_segment(aes(
        x = 0,
        xend = max_reserve_frac,
        y = 1,
        yend = 1
      ), colour = "black",
      linetype = 2) +
      scale_x_continuous(expand = expansion(mult = 0, add = 0)) +
      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
      theme_bw()

    return(sp_disp_noise_yield_frac_below_med_max_yield_plt)
  }

make_contour_plt_sp_disp_noise_frac_below_med_max_abund <-
  function(sp_disp_noise_frac_below_med_max_abund,
           species_name,
           dispersal,
           noise_type,
           max_f_fmsy,
           max_reserve_frac) {
    sp_disp_noise_frac_below_med_max_abund_plt <-
      sp_disp_noise_frac_below_med_max_abund %>%
      filter(reserve_frac <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
      ggplot(data = .,
             aes(x = reserve_frac, y = f_fmsy, z = frac_below_med_abund_f_max)) +
      geom_contour_filled(bins = 12) +
      ggtitle(
        paste0(
          species_name,
          " ",
          dispersal,
          " ",
          noise_type,
          ":\nTime below median max biomass"
        )
      ) +
      xlab("Reserve fraction") +
      ylab("F/Fmsy") +
      scale_fill_viridis_d(option = "D", direction = -1) +
      geom_segment(
        aes(
          x = 0,
          xend = max_reserve_frac,
          y = 1,
          yend = 1
        ),
        colour = "black",
        linetype = 2
      ) +
      scale_x_continuous(expand = expansion(mult = 0, add = 0)) +
      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
      theme_bw()

    return(sp_disp_noise_frac_below_med_max_abund_plt)
}

# Contour plot functions: recruits

calc_sp_disp_noise_recs_ffmsy <- function(sp_disp_noise_recs, 
                                          fleps_2_fs,
                                          f_maxes_med_ann_yield) {
  sp_disp_noise_recs_ffmsy <- sp_disp_noise_recs %>%
    mutate(flep_ratio_ch = as.character(flep_ratio)) %>%
    left_join(., y = fleps_2_fs, by = join_by(flep_ratio_ch == flep_vals_ch)) %>%
    dplyr::mutate(f_fmsy = round(f_vals / f_maxes_med_ann_yield, 2))
  return(sp_disp_noise_recs_ffmsy)
}

calc_recruit_thresh <- function(sp_disp_noise_recs_ffmsy) {
  recruit_thresh <- sp_disp_noise_recs_ffmsy %>%
  dplyr::filter(near(f_fmsy, 1), near(reserve_frac, 0)) %>%
  dplyr::summarize(med_recs_f_fmsy = median(recruits)) %>%
  .$med_recs_f_fmsy
  return(recruit_thresh)
}

calc_time_below_rec_thresh <- function(sp_disp_noise_recs_ffmsy, 
                                       recruit_thresh) {
  sp_disp_noise_recs_ffmsy %>%
  arrange(reserve_frac, f_fmsy, year) %>%
  mutate(below_threshold = recruits <= recruit_thresh) %>%
  group_by(reserve_frac, f_fmsy) %>%
  summarize(num_below_threshold = sum(below_threshold), 
            frac_below_threshold = num_below_threshold/sim_len)
}

make_contour_sp_disp_noise_frac_below_rec_thresh <-
  function(sp_disp_noise_recs_below_thresh,
           species_name,
           dispersal,
           noise_type,
           max_f_fmsy = 2.5 ,
           max_reserve_frac = 0.5,
           n_bins = 12) {

    recs_below_threshold_plt <- sp_disp_noise_recs_below_thresh %>%
      filter(reserve_frac <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
      ggplot(data = .,
             aes(x = reserve_frac, y = f_fmsy, z = frac_below_threshold)) +
      geom_contour_filled(bins = n_bins) +
      ggtitle(paste0(
        species_name,
        " ",
        dispersal,
        " ",
        noise_type,
        ":\nTime below threshold"
      )) +
      xlab("Reserve fraction") +
      ylab("F/Fmsy") +
      scale_fill_viridis_d(option = "D", direction = -1) +
      geom_segment(aes(
        x = 0,
        xend = max_reserve_frac,
        y = 1,
        yend = 1
      ),
      colour = "black",
      linetype = 2) +
      scale_x_continuous(expand = expansion(mult = 0, add = 0)) +
      scale_y_continuous(expand = expansion(mult = 0, add = 0))

    return(recs_below_threshold_plt)

  }

```

```{r}
#| label: recs-abund-yield
#| echo: FALSE

recs_spec_disp_noise <- qry_results_table_agg(
  ddb_table = exp, #"larval_pool_blue_rockfish_mei_135_75",
  metric = "recruits",
  burn_in = burn_in_parm,
  sim_len = sim_len_parm,
  reserve_fracs = NULL,
  flep_ratios = NULL) %>%
  mutate(flep_ratio_ch = as.character(flep_ratio))

waa_df <- tibble(age = 1:length(waa_g),
                 "waa" = waa_g)

abund_spec_disp_noise <- qry_results_table_agg(
  ddb_table = exp, #"larval_pool_blue_rockfish_mei_135_75",
  metric = "abundance",
  burn_in = burn_in_parm,
  sim_len = sim_len_parm,
  reserve_fracs = NULL,
  flep_ratios = NULL) %>%
  tibble() %>%
  left_join(x = ., y = waa_df, by = "age") %>%
  mutate(biomass_at_age = (abundance * waa) / 1e6,
         flep_ratio_ch = as.character(flep_ratio)) %>%
  select(-waa, -abundance)

yield_spec_disp_noise <- qry_results_table_agg(
  ddb_table = exp, #"larval_pool_blue_rockfish_mei_135_75",
  metric = "yield",
  burn_in = burn_in_parm,
  sim_len = sim_len_parm,
  reserve_fracs = NULL,
  flep_ratios = NULL) %>% 
  mutate(yield = yield / 1e6, 
         flep_ratio_ch = as.character(flep_ratio))

```

## Recruits

#### Time series plots

```{r}
#| label: recruit-time-series-plots
#| echo: FALSE
#| fig-width: 15
#| fig-height: 8
#| fig-column: screen

F_max_yield <-
  get_f_maxes_yield(yield_disp_sp_noise = yield_spec_disp_noise,
                    fleps_2_fs = spec_fleps_2_fs)

# yield_brf_lp_white_135_75_prep

yield_spec_disp_noise_prep <- make_df_yield_exp_spec_noise_rec_fs(
  df_exp_spec_noise_rec = yield_spec_disp_noise,
  fleps_2_fs = spec_fleps_2_fs,
  f_maxes_yield = F_max_yield
)

yield_sub_plt_df <- prep_ann_yield_for_plot(
  df_exp_spec_noise_rec = yield_spec_disp_noise_prep,
  frac_reserves = c(0, 0.25, 0.50),
  f_fmsys = c(0, 0.52, 1.00, 1.43, 2.09)
)[[2]]

recs_spec_disp_noise_plt <-
  prep_ann_recs_for_plot(
    df_exp_spec_noise_rec_fs = recs_spec_disp_noise,
    fleps_2_fs = spec_fleps_2_fs,
    f_maxes_yield = F_max_yield,
    frac_reserves = c(0, 0.25, 0.50),
    f_fmsys = c(0, 0.52, 1.00, 1.43, 2.09),
    sp_parms = species_parms,
    spc = nice_species
  )

spec_disp_noise_135_075_alpha_sd <-
  get_exp_details(df_after_qry_results_table_agg = recs_spec_disp_noise)

recs_ts_plt <- facet_recs_ts_plots(
  main_plt_df = recs_spec_disp_noise_plt[[1]],
  sub_plt_df = recs_spec_disp_noise_plt[[2]],
  yield_sub_plt = yield_sub_plt_df,
  recruit_thresh = recs_spec_disp_noise_plt[[3]],
  exp_deets_df = spec_disp_noise_135_075_alpha_sd,
  x_text_val = 550
)

print(recs_ts_plt)

postscript(file = file.path(out_path, paste0(exp, "-recs-ts-plt.eps")), 
           width = 8,
           heigh = 6)
print(recs_ts_plt)
invisible(dev.off())

png(
  file = file.path(out_path, paste0(exp, "-recs-ts-plt.png")),
  width = 8,
  heigh = 6,
  units = "in", res = 600
)
print(recs_ts_plt)
invisible(dev.off())

```

#### Contour plots

```{r}
#| label: recruit-contour-plots
#| echo: FALSE
#| fig-width: 15
#| fig-height: 8
#| fig-column: screen

# yield_spec_disp_noise_prep
yield_spec_disp_noise_prep_gcols <- get_sp_disp_noise_yield_gcols(sp_disp_noise_yield_prep = yield_spec_disp_noise_prep)

yield_spec_disp_noise_gcols_ann <- 
calc_sp_disp_noise_gcols_ann_yield(sp_disp_noise_yield_prep_gcols = yield_spec_disp_noise_prep_gcols)

yield_spec_disp_noise_gcols_med_ann <- calc_sp_disp_noise_yield_gcols_med_ann_yield(sp_disp_noise_yield_prep_gcols = yield_spec_disp_noise_prep_gcols)

# spec_disp_noise_f_maxes_med_ann_yield <- get_f_maxes_med_ann_yield(sp_disp_noise_yield_gcols_med_ann_yield = yield_spec_disp_noise_gcols_med_ann)

recs_spec_disp_noise_ffmsy <-
  calc_sp_disp_noise_recs_ffmsy(sp_disp_noise_recs = recs_spec_disp_noise,
                                fleps_2_fs = spec_fleps_2_fs,
                                f_maxes_med_ann_yield = F_max_yield)

recs_spec_disp_rec_thresh <- calc_recruit_thresh(sp_disp_noise_recs_ffmsy = recs_spec_disp_noise_ffmsy)

recs_spec_disp_noise_below_thresh <-
  calc_time_below_rec_thresh(sp_disp_noise_recs_ffmsy = recs_spec_disp_noise_ffmsy,
                             recruit_thresh = recs_spec_disp_rec_thresh)

rec_contour_plt <- make_contour_sp_disp_noise_frac_below_rec_thresh(
  sp_disp_noise_recs_below_thresh = recs_spec_disp_noise_below_thresh,
  species_name = nice_species,
  dispersal = nice_dispersal,
  noise_type = nice_noise,
  max_f_fmsy = 2.5,
  max_reserve_frac = 0.5,
  n_bins = 12
)

print(rec_contour_plt)

postscript(file = file.path(out_path, paste0(exp, "-recs-contour-plt.eps")), 
           width = 8,
           heigh = 6)
print(rec_contour_plt)
invisible(dev.off())

png(
  file = file.path(out_path, paste0(exp, "-recs-contour-plt.png")),
  width = 8,
  heigh = 6,
  units = "in", res = 600
)
print(rec_contour_plt)
invisible(dev.off())

```

## Abundance

#### Time series plots

```{r}
#| label: abundance-time-series-plots
#| echo: FALSE
#| fig-width: 15
#| fig-height: 8
#| fig-column: screen
# Needs
# 1. abund_spec_disp_noise
# 2. (brf_)F_max_yield(_75sd)

# abund_spec_disp_noise
# F_max_yield

abund_spec_disp_noise_alpha_sd <- get_exp_details(df_after_qry_results_table_agg= abund_spec_disp_noise)

abund_spec_disp_noise_prep <- make_df_exp_spec_noise_rec_fs(
  df_exp_spec_noise_rec = abund_spec_disp_noise,
  fleps_2_fs = spec_fleps_2_fs,
  f_maxes_yield = F_max_yield
)

abund_spec_disp_noise_plt <-
  prep_ann_abund_for_plot(
    df_exp_spec_noise_rec = abund_spec_disp_noise_prep,
    frac_reserves = c(0, 0.25, 0.50),
    f_fmsys = c(0.52, 1.00, 1.43, 2.09)
  )

abund_ts_plt <- facet_biomass_ys_plots(main_plt_df = abund_spec_disp_noise_plt[[1]],
                     sub_plt_df = abund_spec_disp_noise_plt[[2]],
                     biomass_thresh = abund_spec_disp_noise_plt[[3]],
                     exp_deets_df = abund_spec_disp_noise_alpha_sd,
                     x_text_val = x_text_position_parm)

print(abund_ts_plt)

postscript(file = file.path(out_path, paste0(exp, "-abund-ts-plt.eps")), 
           width = 8,
           heigh = 6)
print(abund_ts_plt)
invisible(dev.off())

png(
  file = file.path(out_path, paste0(exp, "-abund-ts-plt.png")),
  width = 8,
  heigh = 6,
  units = "in", res = 600
)
print(abund_ts_plt)
invisible(dev.off())

```

#### Contour plots

```{r}
#| label: abundance-contour-plots
#| echo: FALSE
#| fig-width: 15
#| fig-height: 8
#| fig-column: screen

abund_spec_disp_noise_prep_gcols <- get_sp_disp_noise_abund_gcols(sp_disp_noise_abund_prep = abund_spec_disp_noise_prep)

abund_spec_disp_noise_prep_gcols_ann <- 
calc_sp_disp_noise_gcols_ann_abund(sp_disp_noise_abund_prep_gcols = abund_spec_disp_noise_prep_gcols)

abund_spec_disp_noise_prep_gcols_med_ann <- calc_sp_disp_noise_abund_gcols_med_ann_abund(sp_disp_noise_abund_prep_gcols = abund_spec_disp_noise_prep_gcols)

spec_disp_noise_ann_abund_ffmsy <- calc_sp_disp_noise_abund_gcols_ann_abund_ffmsy(
  sp_disp_noise_abund_gcols_ann_abund = abund_spec_disp_noise_prep_gcols_med_ann,
  f_max_median_ann_yield = F_max_yield
)

max_median_ann_abund_value <- spec_disp_noise_ann_abund_ffmsy %>% filter(near(f_fmsy, 1)) %>% .$median_ann_biomass

spec_disp_noise_prep_frac_below_med_max_abund <- calc_sp_disp_noise_abund_frac_below_med_max_abund(sp_disp_noise_abund_gcols_ann_abund_ffmsy = abund_spec_disp_noise_prep_gcols_ann, max_median_ann_abund = max_median_ann_abund_value)

spec_disp_noise_prep_abund_contour_plt <- make_contour_plt_sp_disp_noise_frac_below_med_max_abund(
  sp_disp_noise_frac_below_med_max_abund = spec_disp_noise_prep_frac_below_med_max_abund,
  species_name = nice_species,
  dispersal = nice_dispersal,
  noise_type = nice_noise,
  max_f_fmsy = 2.5,
  max_reserve_frac = 0.5
)

print(spec_disp_noise_prep_abund_contour_plt)

postscript(file = file.path(out_path, paste0(exp, "-abund-contour-plt.eps")), 
           width = 8,
           heigh = 6)
print(spec_disp_noise_prep_abund_contour_plt)
invisible(dev.off())

png(
  file = file.path(out_path, paste0(exp, "-abund-contour-plt.png")),
  width = 8,
  heigh = 6,
  units = "in", res = 600
)
print(spec_disp_noise_prep_abund_contour_plt)
invisible(dev.off())

```

## Yield

#### Time series

```{r}
#| label: yield-time-series-plots
#| echo: FALSE
#| fig-width: 15
#| fig-height: 8
#| fig-column: screen

# Data input needs:
# 1. yield_spec_disp_noise
# 2. F_max_yield

# F_max_yield <-
#   get_f_maxes_yield(yield_disp_sp_noise = yield_spec_disp_noise,
#                     fleps_2_fs = spec_fleps_2_fs)

spec_disp_noise_alpha_sd <- get_exp_details(df_after_qry_results_table_agg= yield_spec_disp_noise)

yield_spec_disp_noise_prep <- make_df_exp_spec_noise_rec_fs(
  df_exp_spec_noise_rec = yield_spec_disp_noise,
  fleps_2_fs = spec_fleps_2_fs,
  f_maxes_yield = F_max_yield
)

yield_spec_disp_noise_plt <-
  prep_ann_yield_for_plot(
    df_exp_spec_noise_rec = yield_spec_disp_noise_prep,
    frac_reserves = c(0, 0.25, 0.50),
    f_fmsys = c(0.52, 1.00, 1.43, 2.09)
  )

yield_ts_plots <- facet_yield_ts_plots(main_plt_df = yield_spec_disp_noise_plt[[1]],
                     sub_plt_df = yield_spec_disp_noise_plt[[2]],
                     yield_thresh = yield_spec_disp_noise_plt[[3]],
                     exp_deets_df = spec_disp_noise_alpha_sd,
                     x_min = 600,
                     x_max = 635)

print(yield_ts_plots)

postscript(file = file.path(out_path, paste0(exp, "-yield-ts-plt.eps")), 
           width = 8,
           heigh = 6)
print(yield_ts_plots)
invisible(dev.off())

png(
  file = file.path(out_path, paste0(exp, "-yield-ts-plt.png")),
  width = 8,
  heigh = 6,
  units = "in", res = 600
)
print(yield_ts_plots)
invisible(dev.off())

# No text version
yield_ts_plots <- facet_yield_ts_plots(main_plt_df = yield_spec_disp_noise_plt[[1]],
                     sub_plt_df = yield_spec_disp_noise_plt[[2]],
                     yield_thresh = yield_spec_disp_noise_plt[[3]],
                     exp_deets_df = spec_disp_noise_alpha_sd,
                     text = FALSE,
                     x_min = 600,
                     x_max = 635)

postscript(file = file.path(out_path, paste0(exp, "-yield-ts-plt-no-text.eps")), 
           width = 8,
           heigh = 6)
print(yield_ts_plots)
invisible(dev.off())

png(
  file = file.path(out_path, paste0(exp, "-yield-ts-plt-no-text.png")),
  width = 8,
  heigh = 6,
  units = "in", res = 600
)
print(yield_ts_plots)
invisible(dev.off())

```

#### Contour

```{r}
#| label: yield-contour-plots
#| echo: FALSE
#| fig-width: 15
#| fig-height: 8
#| fig-column: screen

yield_spec_disp_noise_prep_gcols <- get_sp_disp_noise_yield_gcols(sp_disp_noise_yield_prep = yield_spec_disp_noise_prep)

yield_spec_disp_noise_prep_gcols_ann <- 
calc_sp_disp_noise_gcols_ann_yield(sp_disp_noise_yield_prep_gcols = yield_spec_disp_noise_prep_gcols)

yield_spec_disp_noise_prep_gcols_med_ann <- calc_sp_disp_noise_yield_gcols_med_ann_yield(sp_disp_noise_yield_prep_gcols = yield_spec_disp_noise_prep_gcols)

spec_disp_noise_ann_yield_ffmsy <- calc_sp_disp_noise_yield_gcols_ann_yield_ffmsy(
  sp_disp_noise_yield_gcols_ann_yield = yield_spec_disp_noise_prep_gcols_med_ann,
  f_max_median_ann_yield = F_max_yield)

spec_disp_noise_prep_frac_below_med_max_yield <- calc_sp_disp_noise_yield_frac_below_med_max_yield(sp_disp_noise_yield_gcols_ann_yield_ffmsy = yield_spec_disp_noise_prep_gcols_ann, max_median_ann_yield = spec_disp_noise_ann_yield_ffmsy %>% filter(near(f_vals, F_max_yield, 0.001), near(reserve_frac, 0, 0.001)) %>% .$median_ann_yield)

spec_disp_noise_prep_yield_contour_plt <- make_contour_plt_sp_disp_noise_frac_below_med_max_yield(
  sp_disp_noise_yield_frac_below_med_max_yield = spec_disp_noise_prep_frac_below_med_max_yield,
  species_name = nice_species,
  dispersal = nice_dispersal,
  noise_type = nice_noise,
  max_f_fmsy = 2.5,
  max_reserve_frac = 0.5
)

print(spec_disp_noise_prep_yield_contour_plt)

postscript(file = file.path(out_path, paste0(exp, "-yield-contour-plt.eps")), 
           width = 8,
           heigh = 6)
print(spec_disp_noise_prep_yield_contour_plt)
invisible(dev.off())

png(
  file = file.path(out_path, paste0(exp, "-yield-contour-plt.png")),
  width = 8,
  heigh = 6,
  units = "in", res = 600
)
print(spec_disp_noise_prep_yield_contour_plt)
invisible(dev.off())

```

## Lagged-recruits ($t_c$) and yield

#### Time series

```{r}
#| label: lagged-recs-yield-ts-plots
#| echo: FALSE
#| fig-width: 15
#| fig-height: 8
#| fig-column: screen

# yield_spec_disp_noise_prep_gcols
# recs_spec_disp_noise_ffmsy

frac_reserves <- c(0, 0.25, 0.50)
f_fmsys <- c(0.52, 1.00, 2.09)

t_c <- species_parms[which(species_parms$species == nice_species),]$A_fish

recs_spec_disp_noise_ffmsy_plt <- recs_spec_disp_noise_ffmsy %>%
  dplyr::filter(reduce(map(
    frac_reserves, near, x = reserve_frac, tol = 1e-4
  ), `|`),
  reduce(map(
    f_fmsys, near, x = f_fmsy, tol = 1e-4
  ), `|`)) %>%
  mutate(lagged_year = year + t_c)

yield_spec_disp_noise_prep_plt <- yield_spec_disp_noise_prep_gcols %>%
  dplyr::group_by(reserve_frac, flep_ratio, f_fmsy, year) %>%
  dplyr::summarize(annual_yield = sum(yield)) %>%
  dplyr::ungroup() %>%
  dplyr::filter(reduce(map(
    frac_reserves, near, x = reserve_frac, tol = 1e-4
  ), `|`),
  reduce(map(
    f_fmsys, near, x = f_fmsy, tol = 1e-4
  ), `|`))

plt_start_yr <- 600
plt_end_yr <- 635

scaled_yield_plt <- yield_spec_disp_noise_prep_plt %>%
  group_by(reserve_frac, f_fmsy) %>%
  mutate(scaled_yield = scale(annual_yield)[,1]) %>%
  ungroup()

scaled_recs_plt <- recs_spec_disp_noise_ffmsy_plt %>% 
  group_by(reserve_frac, f_fmsy) %>%
  mutate(scaled_recruits = scale(recruits)[,1]) %>%
  ungroup()

scaled_yield_plt_4corr <- scaled_yield_plt %>%
  mutate(reserve_frac = as.character(reserve_frac), 
         f_fmsy = as.character(f_fmsy)) %>%
  select(reserve_frac, f_fmsy, year, scaled_yield)

scaled_recs_plt_4corr <- scaled_recs_plt %>%
  mutate(reserve_frac = as.character(reserve_frac), 
         f_fmsy = as.character(f_fmsy))  %>%
  select(reserve_frac, f_fmsy, lagged_year, scaled_recruits)

corr_vals <- scaled_yield_plt_4corr %>%
  left_join(scaled_recs_plt_4corr,
            by = c("reserve_frac" = "reserve_frac",
                   "f_fmsy" = "f_fmsy",
                   "year" = "lagged_year")) %>%
  filter(.,complete.cases(reserve_frac, f_fmsy, year, scaled_yield, scaled_recruits)) %>%
  group_by(reserve_frac, f_fmsy) %>%
  summarise(corr = cor(scaled_yield, scaled_recruits))

lagged_recs_yield_plt <- ggplot(scaled_yield_plt %>% 
  filter(year > plt_start_yr, 
         year <= plt_end_yr), 
       aes(x = year, y = scaled_yield)) + 
  facet_grid(reserve_frac ~ f_fmsy,
               labeller = labeller(f_fmsy = label_both,
                                   reserve_frac = label_both)) +
  geom_line() +
  geom_line(data = scaled_recs_plt %>% filter(lagged_year > plt_start_yr, 
         lagged_year <= plt_end_yr), aes(x = lagged_year, y = scaled_recruits), 
            colour = "blue") +
  geom_text(
      data = corr_vals,
      x = 1.01 * plt_start_yr ,
      y = 3,
      aes(label = paste0("Corr: ", round(corr, 3)))
  ) +
  ylab("Scaled yield (black) and lagged + scaled recruits (blue)") +
  xlab("Year") +
  theme_bw()

print(lagged_recs_yield_plt)

postscript(file = file.path(out_path, paste0(exp, "-lagged-recs-yield-ts-plt.eps")), 
           width = 8,
           heigh = 6)
print(lagged_recs_yield_plt)
invisible(dev.off())

png(
  file = file.path(out_path, paste0(exp, "-lagged-recs-yield-ts-plt.png")),
  width = 8,
  heigh = 6,
  units = "in", res = 600
)
print(lagged_recs_yield_plt)
invisible(dev.off())

```

### 2023-10-28 R/functions.R

@@ -1,0 +1,2569 @@
+#' functions. R
+
+
+#'
+#' @title load life history and fishery parameters for California 'fish' species
+#' @description loads a data.frame from `data/species_parameters.csv` to be
+#' used by `get_species_parms` that containslife history for each species
+#' investigated, including: natural mortality (M); von Bertalannfy length-at-age parameters --
+#' asymptotic maximum age (L_inf), growth rate (k), and time when average
+#' length is 0 (t_0); maximum age (A_max); age of maturity (A_mat); age when
+#' vulnerable to fishery (A_fish); and length-weight parameters (weight =
+#' biom_const * length ^biom_exp)
+#'
+#' @return returns a data.frame with life history parameters for 18 species
+#' used to investigate the influence of MPAs on resilience
+#'
+#' @param dts the time series to mimic with respect to frequency content
+#' @param n_reps the number of mimic time series to create
+#' @param scale_sd standard deviation of the resulting time series, default value 1
+#' @param scale_mean mean  of the resulting time series, default value 0
+#' @param r_seed specify random seed for reproducibility
+#'
+#' @examples
+#'
+#' sp_parms <- load_species_parms() # add how to use in targets workflow
+#'
+
+load_species_parms <-
+  function(fp = file.path("data", "species_parameters.csv")) {
+    spec_parms_fp <- fp
+    spec_parms_df <- readr::read_csv(file = spec_parms_fp)
+    return(spec_parms_df)
+  }
+
+#'
+#' @title get life history and fishery parameters for each California 'fish' species
+#'
+#' @description a list of life history parameters for each species investigated,
+#' including: natural mortality (M); von Bertalannfy length-at-age parameters
+#' -- asymptotic maximum age (L_inf), growth rate (k), and time when average
+#' length is 0 (t_0); maximum age (A_max); age of maturity (A_mat); age when
+#' vulnerable to fishery (A_fish); and length-weight parameters (weight =
+#' biom_const * length ^biom_exp)
+#'
+#' @return returns a list of life history parameters
+#'
+#' @param df_parms the time series to mimic with respect to frequency content
+#' @param species_name the number of mimic time series to create
+#'
+#' @examples
+#'
+#' spec_parms <- load_species_parms()
[…]

### 2023-10-28 R/test_functions.R

@@ -1,0 +1,112 @@
+run_sims_sm_write <- function(dt,
+                     expmts,
+                     spec_name,
+                     alpha_bh,
+                     beta_bh,
+                     recr_sd,
+                     fleps,
+                     frac_reserves,
+                     noise_vec,
+                     noise_dat,
+                     n_years,
+                     num_sims,
+                     num_patches,
+                     les_mats,
+                     conn_mats,
+                     in_out_fracs,
+                     sim_results,
+                     sim_spec_dervars,
+                     f_vals,
+                     spec_flep_f_ind,
+                     sim_spec_pars) {
+
+  con <-
+    dbConnect(duckdb::duckdb(),
+              dbdir = "data/sim_out.duckdb",
+              read_only = FALSE)
+  
+  for (i in 1:length(expmts)) {
+    for (j in 1:length(spec_name)) {
+      for (p in noise_vec) {
+        for (m in 1:length(recr_sd)) {
+          for (n in 1:length(fleps)) {
+            for (o in 1:length(frac_reserves)) {
+              for (q in 1:num_sims) {
+                
+                # print(paste0("q -- sim num: ", q))
+                
+                dt_one <- dt[i = .(
+                  expmts[i],
+                  spec_name[j],
+                  alpha_bh[j],
+                  recr_sd[m],
+                  frac_reserves[o],
+                  fleps[n],
+                  p,
+                  q
+                ), ]
+                
+                out <- run_patch_sims2(
+                  t_steps = n_years,
+                  num_patches = num_patches,
+                  les_mat = les_mats[[j]][[n]],
+                  con_mat = conn_mats[[o]],
+                  frac_in_out = in_out_fracs[[o]],
+                  N = sim_results[[j]][[n]],
+                  # this needs the values from a unfished_N1 for each species
+                  selectivity = as.integer(sim_spec_dervars[[j]][["F_select"]]),
+                  fishing_mortality = c(0, f_vals[spec_flep_f_ind[[j]][[n]]]),
+                  natural_mortality = sim_spec_pars[[j]][["M"]],
+                  weight_at_age = sim_spec_pars[[j]][["biom_const"]] * sim_spec_dervars[[j]][["length_at_age"]] ^
+                    sim_spec_pars[[j]][["biom_exp"]],
+                  alpha = alpha_bh[[j]],
+                  beta = beta_bh,
+                  noise_series = noise_dat
+                )
+                
+                out_Ns <-
+                  setnames(
[…]

### 2023-10-28 _targets.R

@@ -1,0 +1,511 @@
+# add unit/data tests (via testthat and assertr)
+# add version control?
+
+
+library(targets)
+library(tarchetypes)
+source(file.path("R", "functions.R"))
+source(file.path("R", "test_functions.R"))
+options(tidyverse.quiet = TRUE)
+tar_option_set(
+  packages = c(
+    "tidyverse",
+    "data.table",
+    "duckdb",
+    "colorspace",
+    "fst",
+    "qs",
+    "metR",
+    "isoband",
+    "signal",
+    "imager"
+  )
+)
+
+
+r_seed <- 11
+tar_seed(default = r_seed)
+## TODO: check for duck.db files and delete before running
+list(
+  tar_target(exp_names_nd,
+             "no_dispersal"),
+  tar_target(exp_names_lp,
+             "larval_pool"),
+  tar_target(
+    species_parms_csv,
+    file.path("data", "species_parameters.csv"),
+    format = "file"
+  ),
+  tar_target(species_parms,
+             load_species_parms(fp = species_parms_csv)),
+  tar_target(
+    species_names,
+    c(
+      "Blue rockfish",
+      "Cabezon",
+      # "Kelp bass",
+      # "Pacific cod",
+      "China rockfish"
+    )
+  ),
+  # get parms for selected species
+  tar_target(
+    sim_species_parms,
+    list_species_parms(parm_df = species_parms,
+                       sp_names = species_names)
+  ),
+  # Get age from parms file
+  tar_target(
+    ages,
+    species_names %>%
+      purrr::set_names() %>%
+      purrr::map(., ~ 1:sim_species_parms[[.x]]$A_max)
+  ),
+  # Fishing mortality - many so that Fs for given FLEPs can be computed
+  tar_target(fishing_mortality_values,
+             seq(0, 2, by = 0.0025)),
+  # Make derived parms for selected species
+  # 'Derived' because they are calculated from the species parameters data
+  tar_target(num_patches,
+             2),
+  # population dynamics and simulation parameters
+  # Simulation length burn_in and actual sim_len:
+  tar_target(burn_in,
+             500),
+  tar_target(sim_len,
+             512),
+  tar_target(sim_len_135,
+             135),
+  tar_target(n_years,
+             burn_in + sim_len),
+  tar_target(n_years_135,
[…]

### 2023-10-28 report-generator.R

@@ -1,0 +1,39 @@
+library(quarto)
+library(DBI)
+library(duckdb)
+library(tidyverse)
+
+if (exists(x = "con")) dbDisconnect(con, shutdown=TRUE)
+con <- DBI::dbConnect(duckdb::duckdb(),
+                      dbdir = "data/sim_out.duckdb",
+                      read_only = FALSE) # change to TRUE???
+
+avail_tables <- DBI::dbListTables(con)
+
+exp_tabs <- avail_tables[!str_detect(avail_tables, "enso_75|white_75|mei_135_25|white_135_25")]
+
+DBI::dbDisconnect(conn = con, shutdown = TRUE)
+
+exp_tabs <- exp_tabs[str_detect(exp_tabs, "blue_rockfish")]
+
+run_html <- function(experiment) {
+  quarto::quarto_render(
+    "recs-abund-yield-parameters.qmd",
+    output_format = "html",
+    execute_params = list(experiment = experiment),
+    output_file = glue::glue("ts-contour-plots-{experiment}.html")
+  )
+}
+
+purrr::map(exp_tabs, run_html)
+
+# 
+con <- DBI::dbConnect(duckdb::duckdb(),
+                      dbdir = "data/sim_out.duckdb",
+                      read_only = FALSE) # change to TRUE???
+nd_qry <- "select * from 'no_dispersal_blue_rockfish_mei_135_75' limit 2000"
+lp_qry <- "select * from 'larval_pool_blue_rockfish_mei_135_75' limit 2000"
+nd_df <- dbGetQuery(con, nd_qry)
+lp_df <- dbGetQuery(con, lp_qry)
+all.equal(nd_df, lp_df)
+DBI::dbDisconnect(con, shutdown = TRUE)

### 2023-10-28 R/test_functions.R
add test functions to reduce data written to duckdb and fine-tune the chunksize of DB writes

@@ -1,29 +1,48 @@
-run_sims_sm_write <- function(dt,
-                     expmts,
-                     spec_name,
-                     alpha_bh,
-                     beta_bh,
-                     recr_sd,
-                     fleps,
-                     frac_reserves,
-                     noise_vec,
-                     noise_dat,
-                     n_years,
-                     num_sims,
-                     num_patches,
-                     les_mats,
-                     conn_mats,
-                     in_out_fracs,
-                     sim_results,
-                     sim_spec_dervars,
-                     f_vals,
-                     spec_flep_f_ind,
-                     sim_spec_pars) {
+# 
+# sim_num = num_sims_dt
+# reserve_frac = reserve_fracs_dt
+# flep_ratio = flep_ratios_dt
+# year = year_vals_dt
+# age = age_vals_dt
+# patch_num = patch_num_dt
+# number = NA_real_
+# yield = NA_real_
 
+
+run_sims_sm_write <- function(dt,
+                              expmts,
+                              spec_name,
+                              alpha_bh,
+                              beta_bh,
+                              recr_sd,
+                              num_sims,
+                              frac_reserves,
+                              fleps,
+                              n_years,
+                              noise_vec,
+                              noise_dat,
+                              num_patches,
+                              les_mats,
+                              conn_mats,
+                              in_out_fracs,
+                              sim_results,
+                              sim_spec_dervars,
+                              f_vals,
+                              spec_flep_f_ind,
+                              sim_spec_pars) {
+  
   con <-
     dbConnect(duckdb::duckdb(),
               dbdir = "data/sim_out.duckdb",
               read_only = FALSE)
+  
+  for (i in 1:num_sims) {
+    for (j in 1:length(frac_reserves)) {
+      for (k in 1:length(fleps)) {
+        dt_one <- dt[i = sim_num == q & near(reserve_frac, frac_reserves[j]) & near(flep_ratio, fleps[n]),]
+      }
+    }
+  }
   
   for (i in 1:length(expmts)) {
     for (j in 1:length(spec_name)) {
@@ -70,7 +89,11 @@ run_sims_sm_write <- function(dt,
                     old = c("V1", "V2", "V3", "value"),
                     new = c("age", "year", "patch_num", "number")
                   )
[…]

### 2023-10-28 R/functions.R
clean up commented code for previous pop sims calcs. age struc sim func init Y[,1,] and max_age to dim(N)[1]

@@ -1588,16 +1588,13 @@ run_patch_sims2 <- function(t_steps,
   Z <- natural_mortality + fishing_mortality
   E <- matrix(0, nrow = num_patches, ncol = t_steps) # eggs
   R <- E
-  # Y <- array(data = NA, dim = dim(N)) #- c(1, 0, 0))
-  Y <- array(data = 0, dim = dim(N)) #- c(1, 0, 0))
-  Y[1, ,] <- 0
-  max_age <- nrow(N)
+  Y <- array(data = 0, dim = dim(N)) 
+  Y[, 1,] <- 0 # Y[1, ,] <- 0
+  max_age <- dim(N)[1] #nrow(N)
   # loop over time
   for (t in 2:t_steps) {
     # loop over patches
     for (n in 1:num_patches) {
-      # catch_at_age <-
-      #   (1 - exp(-((fishing_mortality[n] * selectivity) + natural_mortality))) * (fishing_mortality[n] * selectivity / (natural_mortality + fishing_mortality[n] * selectivity))
       N[, t, n] <-
         les_mat[, , n] %*% N[, t - 1, n] # advance the population
       N_deaths <- N[1:(max_age - 1), t - 1, n] - N[2:(max_age), t, n]
@@ -1605,11 +1602,8 @@ run_patch_sims2 <- function(t_steps,
         N_deaths * (
           fishing_mortality[n] * selectivity / (natural_mortality + fishing_mortality[n] * selectivity)
         )
-      # N_caught <- N[1:(length(weight_at_age) - 1), t, n] * catch_at_age
       Y[2:max_age, t, n] <-
         N_harvest * weight_at_age[-1] #[-(length(weight_at_age))]
-      # Y[, t, n] <-
-      #   N[1:(length(weight_at_age) - 1), t, n] * catch_at_age * weight_at_age[-(length(weight_at_age))]
       E[n, t] <- N[1, t, n] # pull out the eggs produced
     }
     # do larval pool dispersal
@@ -1632,8 +1626,6 @@ run_patch_sims2 <- function(t_steps,
   }
   out <- list(
     Ns = N,
-    # Recs = R,
-    # Eggs = E,
     Y = Y
   )
   return(out)

### 2023-10-28 R/test_functions.R

@@ -52,8 +52,6 @@ run_sims_sm_write <- function(dt,
             for (o in 1:length(frac_reserves)) {
               for (q in 1:num_sims) {
                 
-                # print(paste0("q -- sim num: ", q))
-                
                 dt_one <- dt[i = .(
                   expmts[i],
                   spec_name[j],
@@ -91,7 +89,6 @@ run_sims_sm_write <- function(dt,
                   )
                 setcolorder(out_Ns, c("year", "age", "patch_num"))
                 setkeyv(out_Ns, c("year", "age", "patch_num"))
-                # setkeyv(out_Ns, c("age", "year", "patch_num"))
                 
                 stopifnot(max(out_Ns[patch_num]) = num_patches)
                 
@@ -103,7 +100,6 @@ run_sims_sm_write <- function(dt,
                   )
                 setcolorder(out_Y, c("year", "age", "patch_num"))
                 setkeyv(out_Y, c("year", "age", "patch_num"))
-                # setkeyv(out_Y, c("year", "age", "patch_num"))
                 
                 stopifnot(max(out_Y[patch_num]) = num_patches)
                 

### 2023-10-28 R/functions.R
Z not used in run_patch_sims2

@@ -1585,7 +1585,7 @@ run_patch_sims2 <- function(t_steps,
                             alpha,
                             beta,
                             noise_series) {
-  Z <- natural_mortality + fishing_mortality
+  
   E <- matrix(0, nrow = num_patches, ncol = t_steps) # eggs
   R <- E
   Y <- array(data = 0, dim = dim(N)) 

### 2023-10-29 R/functions.R
write to DB after each of num_sim runs to reduce DB read/write attemps from ~2800 of 10 MB to 5 of ~6 GB and track performance. First time to run tar_make in background (`tar_make(callr_function = callr::r_bg)`)

@@ -1219,20 +1219,20 @@ set_sim_results_arrays <- function(sp_names,
 make_sim_dt2 <- function(sim_nums,
                          reserve_fracs_vals,
                          flep_ratios_vals,
-                         sim_years,
-                         max_age,
+                         # sim_years,
+                         # max_age,
                          check=FALSE) {
   
   # Steps to pre-populate data.table before simulation runs.
   
   sim_nums_vals <- 1:sim_nums
-  year_vals <- 1:sim_years
-  patch_vals <- 1:2
-  age_vals <- 1:max_age
+  # year_vals <- 1:sim_years
+  # patch_vals <- 1:2
+  # age_vals <- 1:max_age
   
   num_sims_dt <- rep(
     sim_nums_vals,
-    each = length(reserve_fracs_vals) * length(flep_ratios_vals) *  length(year_vals) * max(patch_vals) * length(age_vals)
+    each = length(reserve_fracs_vals) * length(flep_ratios_vals) # *  length(year_vals) * max(patch_vals) * length(age_vals)
   )
   
   flep_ratios_dt <- rep(
@@ -1247,22 +1247,22 @@ make_sim_dt2 <- function(sim_nums,
     times = sim_nums * length(flep_ratios_vals) 
   )
   
-  year_vals_dt <- rep(
-    year_vals,
-    each = length(patch_vals) * length(age_vals),
-    times =  sim_nums * length(reserve_fracs_vals) * length(flep_ratios_vals) 
-  )
-  
-  age_vals_dt <- rep(
-    age_vals,
-    each = length(patch_vals),
-    times = sim_nums * length(reserve_fracs_vals) * length(flep_ratios_vals) *  length(year_vals) 
-  )
-  
-  patch_num_dt <- rep(
-    patch_vals,
-    times = sim_nums * length(reserve_fracs_vals) * length(flep_ratios_vals) *  length(year_vals) * length(age_vals)
-  )
+  # year_vals_dt <- rep(
+  #   year_vals,
+  #   each = length(patch_vals) * length(age_vals),
+  #   times =  sim_nums * length(reserve_fracs_vals) * length(flep_ratios_vals) 
+  # )
+  # 
+  # age_vals_dt <- rep(
+  #   age_vals,
+  #   each = length(patch_vals),
+  #   times = sim_nums * length(reserve_fracs_vals) * length(flep_ratios_vals) *  length(year_vals) 
+  # )
+  # 
[…]

### 2023-10-29 R/test_functions.R

@@ -9,8 +9,7 @@
 # yield = NA_real_
 
 
-run_sims_sm_write <- function(dt,
-                              expmts,
+run_sims_sm_write <- function(expmts,
                               spec_name,
                               alpha_bh,
                               beta_bh,
@@ -36,43 +35,63 @@ run_sims_sm_write <- function(dt,
               dbdir = "data/sim_out.duckdb",
               read_only = FALSE)
   
-  for (i in 1:num_sims) {
-    for (j in 1:length(frac_reserves)) {
-      for (k in 1:length(fleps)) {
-        dt_one <- dt[i = sim_num == q & near(reserve_frac, frac_reserves[j]) & near(flep_ratio, fleps[n]),]
-      }
-    }
-  }
+  # for (i in 1:num_sims) {
+  #   for (j in 1:length(frac_reserves)) {
+  #     for (k in 1:length(fleps)) {
+  #       dt_one <- dt[i = sim_num == q & near(reserve_frac, frac_reserves[j]) & near(flep_ratio, fleps[n]),]
+  #       out <- run_patch_sims2(
+  #         t_steps = n_years,
+  #         num_patches = num_patches,
+  #         les_mat = les_mats[[j]][[n]],
+  #         con_mat = conn_mats[[o]],
+  #         frac_in_out = in_out_fracs[[o]],
+  #         N = sim_results[[j]][[n]],
+  #         # this needs the values from a unfished_N1 for each species
+  #         selectivity = as.integer(sim_spec_dervars[[j]][["F_select"]]),
+  #         fishing_mortality = c(0, f_vals[spec_flep_f_ind[[j]][[n]]]),
+  #         natural_mortality = sim_spec_pars[[j]][["M"]],
+  #         weight_at_age = sim_spec_pars[[j]][["biom_const"]] * sim_spec_dervars[[j]][["length_at_age"]] ^
+  #           sim_spec_pars[[j]][["biom_exp"]],
+  #         alpha = alpha_bh[[j]],
+  #         beta = beta_bh,
+  #         noise_series = noise_dat
+  #       )
+  #     }
+  #   }
+  # }
   
   for (i in 1:length(expmts)) {
     for (j in 1:length(spec_name)) {
-      for (p in noise_vec) {
-        for (m in 1:length(recr_sd)) {
-          for (n in 1:length(fleps)) {
-            for (o in 1:length(frac_reserves)) {
-              for (q in 1:num_sims) {
+      for (k in noise_vec) {
[…]

### 2023-10-29 _targets.R

@@ -23,6 +23,13 @@ tar_option_set(
 )
 
 
+# "Blue rockfish",
+# "Cabezon",
+# "Kelp bass",
+# "Pacific cod",
+# "China rockfish"
+
+
 r_seed <- 11
 tar_seed(default = r_seed)
 ## TODO: check for duck.db files and delete before running
@@ -43,8 +50,6 @@ list(
     c(
       "Blue rockfish",
       "Cabezon",
-      # "Kelp bass",
-      # "Pacific cod",
       "China rockfish"
     )
   ),
@@ -93,8 +98,10 @@ list(
   # Lower FLEPs correspond to populations that have experienced higher exploitation
   # 0.3 is close to population collapse, so 0.4 is close enough to get cohort resonance
   tar_target(flep_ratios,
+             # c(seq(0.2, 0.8, by = 0.2), 0.998)),
              c(seq(0.2, 0.975, by = 0.025), 0.998)),
   tar_target(reserve_fracs,
+             # seq(0, 0.8, by = 0.2)),
              seq(0, 0.8, by = 0.05)),
   # EPR (FLEP) can't go below this proportion of the unfished value
   # Note that the eq. recruitment is the point where line with 1/FLEP intersects SR curve
@@ -212,7 +219,7 @@ list(
       sim_arrays = sim_results_arrays_empty,
       fleps = flep_ratios,
       sim_sp_derived_vars = sim_species_derived_vars,
-      n_years = n_years,
+      n_years = n_years_135,
       n_patch = num_patches
     )
   ),
@@ -259,10 +266,10 @@ list(
   tar_target(white_noise,
              rnorm(n_years, 0, sd_recruitment)),
   tar_target(white_noise_135,
-             rnorm(635, 0, sd_recruitment)),
+             rnorm(n_years_135, 0, sd_recruitment)),
   tar_target(
     pre_enso_noise,
-    make_sim_enso(sim_enso_len = 1012, n_enso_sims = 100)
+    make_sim_enso(sim_enso_len = n_years, n_enso_sims = 100)
   ),
   tar_target(enso_noise,
              sd_recruitment * pre_enso_noise),
@@ -272,7 +279,7 @@ list(
     enso_noise_135,
     make_sim_ann_mei_ext(
       mei = enso_dat_135$mei,
-      sim_enso_len = 635,
[…]

### 2023-11-04 ms_figures_supp_figs.qmd
initial steps/prep results of simulations to create figs for manuscript.

---
title: "Recruits, abundance, and yield time series and contours"
author: "Botsford, Hastings, White, and Kilduff"
execute: 
  warning: false
format:
  html: 
    page-layout: full
    embed-resources: true
    anchor-sections: true
    fig-width: 7
    fig-height: 5
  pdf:
    fig-width: 7
    fig-height: 5
  docx:
    fig-width: 7
    fig-height: 5
editor: visual
params:
  experiment: "larval_pool_blue_rockfish_mei_135_75"
---

## Config and set up

```{r}
#| label: Good label name
#| echo: false
#| 
# c("larval_pool_blue_rockfish_mei_135_75",
# "larval_pool_blue_rockfish_white_135_75",
# "larval_pool_cabezon_mei_135_75",
# "larval_pool_cabezon_white_135_75",
# "larval_pool_china_rockfish_mei_135_75",
# "larval_pool_china_rockfish_white_135_75",
# "no_dispersal_blue_rockfish_mei_135_75",
# "no_dispersal_blue_rockfish_white_135_75",
# "no_dispersal_cabezon_mei_135_75",
# "no_dispersal_cabezon_white_135_75",
# "no_dispersal_china_rockfish_mei_135_75",
# "no_dispersal_china_rockfish_white_135_75")

main_figs_path <- file.path("output", "main_figs")
supp_figs_path <- file.path("output", "supp_figs")

if (!dir.exists(main_figs_path)) {
  dir.create(main_figs_path, recursive = TRUE) 
}

if (!dir.exists(supp_figs_path)) {
  dir.create(supp_figs_path, recursive = TRUE) 
}

con <- DBI::dbConnect(duckdb::duckdb(),
                      dbdir = "data/sim_out.duckdb",
                      read_only = FALSE)
```

```{r}
#| label: load-packages-data
#| echo: false

library(targets)
suppressMessages(library(tidyverse))
library(duckdb)
options(dplyr.summarise.inform = FALSE)
# Load relevant data from target objexts
tar_load(sim_nums)
tar_load(sim_len)
tar_load(species_flep_fished_ind)
tar_load(fishing_mortality_values)
tar_load(species_parms)
tar_load(sim_species_parms)
tar_load(sim_species_derived_vars)

# Load project functions
source("R/functions.R")

# constants
burn_in_parm <- 500
sim_len_parm <- 135

x_text_position_parm <- 550

waa_g <- sim_species_parms[[nice_species]][["biom_const"]] * sim_species_derived_vars[[nice_species]][["length_at_age"]] ^
                    sim_species_parms[[nice_species]][["biom_exp"]]

# use functions to create useful data structures
# FLEP to F reference tables by species
spec_fleps_2_fs <-
  get_fs_from_fleps(species = nice_species,
                    flep_inds = species_flep_fished_ind,
                    f_vals =  fishing_mortality_values)

```

## Main figures

### Figure 3

Contour plots showing the buffering effects of harvest rate and marine reserves on the abundance of a fished population, when there is no larval dispersal between the fished and reserve habitat patches.

Species: Blue rockfish

Dispersal: No Dispersal

Environmental noise: ENSO (MEI)

```{r}
#| label: figure_3

set.seed(11)
num_sims_2_avg <- 5
sims_2_use <- sort(sample(1:sim_nums, size = num_sims_2_avg, replace = FALSE))

table_name <- "no_dispersal_blue_rockfish_mei_135_75"

qry <- paste0("SELECT  sim_num, reserve_frac, flep_ratio, year, age, 
              sum(number) as abundance,
              sum(yield) as yield,
              FROM '", table_name, 
              "' WHERE sim_num IN (", toString(sims_2_use), ") AND year > 500 
              GROUP BY sim_num, reserve_frac, flep_ratio, year, age
              ORDER BY sim_num, reserve_frac, flep_ratio, year, age
              ")

out <- dbGetQuery(conn = con, qry)

out_2 <- out %>%
  group_by(sim_num, reserve_frac, flep_ratio) %>%
  summarize(abundance = mean(abundance, na.rm = TRUE),
            yield = mean(yield, na.rm=TRUE)) %>%
  ungroup()

ggplot(out_2, aes(x = as.numeric(reserve_frac), 
                y = as.numeric(flep_ratio),
                z = abundance)) +
  facet_grid(sim_num ~ .) +
  geom_contour_filled()

out_3 <- out_2 %>%
  group_by(reserve_frac, flep_ratio) %>%
  summarize(abundance = mean(abundance, na.rm = TRUE),
            yield = mean(yield, na.rm = TRUE)) %>%
  ungroup()

ggplot(out_3, aes(x = as.numeric(reserve_frac), 
                y = as.numeric(flep_ratio),
                z = abundance)) +
  geom_contour_filled()

# qry <- "SELECT reserve_frac, flep_ratio, sum(number) as total_nums, sum(yield) as total_yield from '", table_name, "'where year > 500 group by reserve_frac, flep_ratio order by reserve_frac asc, flep_ratio asc"

```

### Figure 4

Contour plots showing the buffering effects of harvest rate and marine reserves on the abundance of a fished population, when the fished and reserve patches share a larval pool.

Species: Blue rockfish

Dispersal: Larval pool

Environmental noise: ENSO (MEI)

```{r}
#| label: figure_4
```

### Figure 5

Representative timeseries of total population biomass under different combinations of fishing rate and marine reserve protection.

Species: Blue rockfish

Dispersal: Larval pool

Environmental noise: ENSO (MEI)

```{r}
#| label: figure_5

```

### Figure 6

Representative timeseries of fishery yield under different combinations of fishing rate and marine reserve protection.

Species: Blue rockfish

Dispersal: Larval pool

Environmental noise: ENSO (MEI)

```{r}
#| label: figure_6

```

### Figure 7

Representative timeseries of fishery yield (black curves) in the same harvest and marine reserve scenarios depicted in Fig. 5.

Species: Blue rockfish

Dispersal: Larval pool

Environmental noise: ENSO (MEI)

```{r}
#| label: figure_7

```

### 2023-11-04 recs-abund-yield-parameters.qmd
initial steps/prep results of simulations to create figs for manuscript.

@@
 nice_species <- pretty_species[stringr::str_detect(exp, valid_species)]
-nice_noise <- pretty_noise[stringr::str_detect(exp, valid_noise)]
+nice_noise <- pretty_noise[stringr::str_detect(exp, valid_noise)]o
 
@@
 
-### Experiment: `r params$experimenft`
+### Experiment: `r params$experiment`
 

### 2023-11-04 R/test_functions.R

@@ -35,40 +35,21 @@ run_sims_sm_write <- function(expmts,
               dbdir = "data/sim_out.duckdb",
               read_only = FALSE)
   
-  # for (i in 1:num_sims) {
-  #   for (j in 1:length(frac_reserves)) {
-  #     for (k in 1:length(fleps)) {
-  #       dt_one <- dt[i = sim_num == q & near(reserve_frac, frac_reserves[j]) & near(flep_ratio, fleps[n]),]
-  #       out <- run_patch_sims2(
-  #         t_steps = n_years,
-  #         num_patches = num_patches,
-  #         les_mat = les_mats[[j]][[n]],
-  #         con_mat = conn_mats[[o]],
-  #         frac_in_out = in_out_fracs[[o]],
-  #         N = sim_results[[j]][[n]],
-  #         # this needs the values from a unfished_N1 for each species
-  #         selectivity = as.integer(sim_spec_dervars[[j]][["F_select"]]),
-  #         fishing_mortality = c(0, f_vals[spec_flep_f_ind[[j]][[n]]]),
-  #         natural_mortality = sim_spec_pars[[j]][["M"]],
-  #         weight_at_age = sim_spec_pars[[j]][["biom_const"]] * sim_spec_dervars[[j]][["length_at_age"]] ^
-  #           sim_spec_pars[[j]][["biom_exp"]],
-  #         alpha = alpha_bh[[j]],
-  #         beta = beta_bh,
-  #         noise_series = noise_dat
-  #       )
-  #     }
-  #   }
-  # }
-  
   for (i in 1:length(expmts)) {
     for (j in 1:length(spec_name)) {
       for (k in noise_vec) {
         for (l in 1:length(recr_sd)) {
           for (m in 1:num_sims) {
+            print(paste0("num_sims: ", m))
             for (n in 1:length(frac_reserves)) {
+              # print(paste0("frac_res: ", frac_reserves[n]))
               for (o in 1:length(fleps)) {
-              
-                dt_one <- data.table(sim_num = num_sims[m], reserve_frac=frac_reserves[n], flep_ratio=fleps[o], number = list(), yield = list())
+                # print(paste0("fleps: ", fleps[o]))
+                dt_one <- data.table(sim_num = m, 
+                                     reserve_frac=as.character(frac_reserves[n]), 
+                                     flep_ratio=as.character(fleps[o]), 
+                                     number = list(), 
+                                     yield = list())
                 
[…]

### 2023-11-04 _targets.R

@@ -91,7 +91,7 @@ list(
              1:n_years_135),
   # Run how many replicate simulations?
   tar_target(sim_nums,
-             5),
+             25),
   tar_target(sd_recruitment,
              0.75),
   # Fraction of lifetime egg production (FLEP)

### 2023-11-04 report-generator.R

@@ -28,12 +28,12 @@ run_html <- function(experiment) {
 purrr::map(exp_tabs, run_html)
 
 # 
-con <- DBI::dbConnect(duckdb::duckdb(),
-                      dbdir = "data/sim_out.duckdb",
-                      read_only = FALSE) # change to TRUE???
-nd_qry <- "select * from 'no_dispersal_blue_rockfish_mei_135_75' limit 2000"
-lp_qry <- "select * from 'larval_pool_blue_rockfish_mei_135_75' limit 2000"
-nd_df <- dbGetQuery(con, nd_qry)
-lp_df <- dbGetQuery(con, lp_qry)
-all.equal(nd_df, lp_df)
-DBI::dbDisconnect(con, shutdown = TRUE)
+# con <- DBI::dbConnect(duckdb::duckdb(),
+#                       dbdir = "data/sim_out.duckdb",
+#                       read_only = FALSE) # change to TRUE???
+# nd_qry <- "select * from 'no_dispersal_blue_rockfish_mei_135_75' limit 2000"
+# lp_qry <- "select * from 'larval_pool_blue_rockfish_mei_135_75' limit 2000"
+# nd_df <- dbGetQuery(con, nd_qry)
+# lp_df <- dbGetQuery(con, lp_qry)
+# all.equal(nd_df, lp_df)
+# DBI::dbDisconnect(con, shutdown = TRUE)

### 2023-11-04 test_duckdb_connect.R

@@ -1,0 +1,44 @@
+# Install and load packages
+# Uncomment next 5 lines first time the project is run
+# install.packages(c("DBI", "ggplot2"))
+library(remotes)
+# ## duckdb note: newer package versions cannot read databases written with older versions
+# ## until the duckdb (R package) version reaches 1.0
+install_version("duckdb", version = "0.7.0", repos = "https://cloud.r-project.org/")
+
+library(DBI)
+library(duckdb)
+library(ggplot2)
+
+# connect to the database
+con <- DBI::dbConnect(duckdb::duckdb(),
+                      dbdir = "data/sim_out.duckdb",
+                      read_only = FALSE)
+# list the names of tables in the database
+tables <- dbListTables(con)
+
+# query one of the tables # larval_pool_blue_rockfish_mei_135_75
+for (i in 1:length(tables)) {
+  out <- dbGetQuery(conn = con, paste0("SELECT reserve_frac, flep_ratio, sum(number) as total_nums, sum(yield) as total_yield 
+                               from '", tables[i], "' 
+                               where year > 500
+                               group by reserve_frac, flep_ratio
+                               order by reserve_frac asc, flep_ratio asc"))
+  
+  print(tail(out))
+  
+}
+
+# make some quick plots that are kind of like the real plots for the last table of the loop
+ggplot(out, aes(x = as.numeric(reserve_frac), 
+                y = as.numeric(flep_ratio),
+                z = total_nums)) +
+  geom_contour_filled()
+
+ggplot(out, aes(x = as.numeric(reserve_frac), 
+                y = as.numeric(flep_ratio),
+                z = total_yield)) +
+  geom_contour_filled()
+
+# close the connection
+DBI::dbDisconnect(con, shutdown = TRUE)

### 2023-11-07 ms_figures_supp_figs.qmd
refactor and revise plot functions for main figures, data prep steps interim commit

@@
 
-waa_g <- sim_species_parms[[nice_species]][["biom_const"]] * sim_species_derived_vars[[nice_species]][["length_at_age"]] ^
-                    sim_species_parms[[nice_species]][["biom_exp"]]
-
-# use functions to create useful data structures
-# FLEP to F reference tables by species
-spec_fleps_2_fs <-
-  get_fs_from_fleps(species = nice_species,
-                    flep_inds = species_flep_fished_ind,
-                    f_vals =  fishing_mortality_values)
+# waa_g <- sim_species_parms[[nice_species]][["biom_const"]] * sim_species_derived_vars[[nice_species]][["length_at_age"]] ^
+#                     sim_species_parms[[nice_species]][["biom_exp"]]
+# 
+# 
+# # use functions to create useful data structures
+# # FLEP to F reference tables by species
+# spec_fleps_2_fs <-
+#   get_fs_from_fleps(species = nice_species,
+#                     flep_inds = species_flep_fished_ind,
+#                     f_vals =  fishing_mortality_values) 
+#
 
@@
 
+## Species parms
+
+brf_waa_g <- sim_species_parms[["Blue rockfish"]][["biom_const"]] * sim_species_derived_vars[["Blue rockfish"]][["length_at_age"]] ^
+                    sim_species_parms[["Blue rockfish"]][["biom_exp"]]
+
+brf_waa_g_df <- data.frame(age = 1: sim_species_parms[["Blue rockfish"]]$A_max,
+                           waa_g = brf_waa_g)
+
+# use functions to create useful data structures
+# FLEP to F reference tables by species
+spec_fleps_2_fs <-
+  get_fs_from_fleps(species = "Blue rockfish",
+                    flep_inds = species_flep_fished_ind,
+                    f_vals =  fishing_mortality_values)
+
+## Qry 
 set.seed(11)
@@
 
-table_name <- "no_dispersal_blue_rockfish_mei_135_75"
+table_name <- "no_dispersal_blue_rockfish_white_135_75"
 
@@
 
-out_2 <- out %>%
-  group_by(sim_num, reserve_frac, flep_ratio) %>%
+get_f_maxes_yield <- function(out_df,
+                              fleps_2_fs) {
+  # Find the fishing mortality level that maximizes yield
+  # with no reserves
+  F_maxes_yield <- out %>%
+    dplyr::filter(reserve_frac == "0") %>%
+    dplyr::left_join(., y = fleps_2_fs, by = join_by(flep_ratio == flep_vals_ch)) %>%
+    dplyr::group_by(f_vals, flep_ratio, year) %>%
+    dplyr::summarise(yield = sum(yield),
+                     abundance = sum(abundance)) %>%
+    dplyr::ungroup() %>%
+    dplyr::group_by(f_vals, flep_ratio) %>%
+    dplyr::summarize(yield = mean(yield, na.rm = TRUE),
+                     abundance = mean(abundance, na.rm = TRUE)) %>%
+    ungroup() %>%
+    dplyr::filter(yield == max(yield)) %>%
+    .$f_vals
+
+  return(F_maxes_yield)
+}
+
+df_add_fs_out <- function(out,
+                          spec_fleps_2_fs,
+                          F_maxes_yield) {
+out_fs <- out %>%
+  mutate(flep_ratio_ch = as.character(flep_ratio)) %>%
+  dplyr::left_join(., y = spec_fleps_2_fs, by = join_by(flep_ratio == flep_vals_ch)) %>%
+  dplyr::mutate(f_fmsy = round(f_vals / F_maxes_yield, 2)) %>%
+  dplyr::left_join(., y = brf_waa_g_df, join_by(age == age)) %>%
+  dplyr::mutate(biomass_at_age = (abundance * waa_g) / 1E6)
+
+}
+
+get_median_yield <- function(df_out_fs) {
+  # returns the mean of median yield at at F = F_msy 
+  # for a coastline with no reserves across sims
+
+  stopifnot(colnames(df_out_fs) == c("sim_num", "reserve_frac", "flep_ratio",
+                                     "year", "age", "abundance", "yield", 
+                                     "flep_ratio_ch", "flep_vals", "f_vals", 
+                                     "f_fmsy", "waa_g", "biomass_at_age"))
+
+  sim_num_2_use <- min(df_out_fs$sim_num)
+  med_yield <- df_out_fs %>%
+    dplyr::filter(near(f_fmsy, 1), near(as.numeric(reserve_frac), 0))  %>%
+    dplyr::group_by(sim_num,
+                    reserve_frac,
+                    f_fmsy,
+                    year) %>%
+    dplyr::summarise(ann_yield = sum(yield)) %>%
+    dplyr::ungroup() %>%
+    dplyr::group_by(sim_num) %>%
+    dplyr::summarise(med_ann_yield = median(ann_yield)) %>%
+    dplyr::ungroup() %>%
+    dplyr::summarise(avg_med_yield_f_fmsy = mean(med_ann_yield)) %>%
+    .$avg_med_yield_f_fmsy
+  return(med_yield)
+}
+
+get_median_biomass <- function(df_out_fs) {
+  # returns the mean of median abundance at at F = F_msy 
+  # for a coastline with no reserves across sims
+  stopifnot(colnames(df_out_fs) == c("sim_num", "reserve_frac", "flep_ratio",
+                                     "year", "age", "abundance", "yield", 
+                                     "flep_ratio_ch", "flep_vals", "f_vals", 
+                                     "f_fmsy", "waa_g", "biomass_at_age"))
+  med_biomass <- df_out_fs %>%
+    dplyr::filter(near(f_fmsy, 1), near(as.numeric(reserve_frac), 0))  %>%
+    dplyr::group_by(sim_num,
+                    reserve_frac,
+                    flep_ratio,
+                    year) %>%
+    dplyr::summarise(ann_biomass = sum(biomass_at_age)) %>%
+    dplyr::ungroup() %>%
+     dplyr::group_by(sim_num) %>%
+    dplyr::summarise(med_ann_biomass = median(ann_biomass)) %>%
+    dplyr::summarise(avg_med_biomass_f_fmsy = mean(med_ann_biomass)) %>%
+    .$avg_med_biomass_f_fmsy
+  return(med_biomass)
+}
+
+df_yld_bm_stats_by_sim_f_frac_year <- function(df_out_fs,
+                                      sims_num_2_use) {
+  stopifnot(colnames(df_out_fs) == c("sim_num", "reserve_frac", "flep_ratio",
+                                     "year", "age", "abundance", "yield", 
+                                     "flep_ratio_ch", "flep_vals", "f_vals", 
+                                     "f_fmsy", "waa_g", "biomass_at_age"))
+  # make a sub function
+  out_df <- df_out_fs %>%
+    dplyr::filter(near(sim_num, sim_num_2_use)) %>%
+    dplyr::filter(reduce(map(
+      frac_reserves,
+      near,
+      x = as.numeric(reserve_frac),
+      tol = 1e-4
+    ), `|`)) %>%
+    dplyr::group_by(sim_num, reserve_frac, f_fmsy, year) %>%
+    dplyr::summarize(annual_yield = sum(yield),
+                     annual_biomass = sum(biomass_at_age)) %>%
+    dplyr::ungroup() %>%
+    dplyr::filter(reduce(map(
+      f_fmsys, near, x = f_fmsy, tol = 1e-4
+    ), `|`))
+  return(out_df)
+}
+
+# df_exp_spec_noise_rec_fs
+prep_ann_yield_abund_for_plot <- function(df_out_fs,
+                                          frac_reserves = c(0, 0.25, 0.50),
+                                          f_fmsys = c(0, 0.52, 1.00, 2.09)) {
+
+  sim_num_2_use <- min(df_out_fs$sim_num)
+  if (length(f_fmsys) < 1 | is.null(f_fmsys)) {
+    stop("Please specify f_fmsy values to use")
+  }
+
+  if (length(frac_reserves) < 1 | is.null(frac_reserves)) {
+    stop("Please specify frac_reserves values to use")
+  }
+
+    # make a sub function
+    supp_plt_df <- main_plt_df %>%
+      dplyr::mutate(below_thresh_yld = if_else(annual_yield <= med_yield, 1, 0),
+                    below_thresh_bm = if_else(annual_biomass <= med_biomass, 1, 0)) %>%
+      dplyr::group_by(sim_num, reserve_frac, f_fmsy) %>%
+      dplyr::summarise(
+        mean_yield = round(mean(annual_yield, na.rm = TRUE), 2),
+        mean_biomass = round(mean(annual_biomass, na.rm = TRUE), 2),
+        sd_yield = round(sd(annual_yield, na.rm = TRUE), 2),
+        sd_biomass = round(sd(annual_biomass, na.rm = TRUE), 2),
+        cv_yield = round(sd(annual_yield, na.rm = TRUE)/mean(annual_yield, na.rm = TRUE), 2),
+        cv_biomass = round(sd(annual_biomass, na.rm = TRUE)/mean(annual_biomass, na.rm = TRUE), 2),
+        yrs_below_yield_thresh = round(sum(below_thresh_yld)/135, 2),
+        yrs_below_biomass_thresh = round(sum(below_thresh_bm)/135, 2)
+      ) %>%
+      dplyr::ungroup() %>%
+      dplyr::group_by(reserve_frac, f_fmsy) %>%
+      dplyr::summarize(
+        mean_yield = round(mean(mean_yield, na.rm = TRUE), 2),
+        mean_yield_lab = paste0("Mean yield: ", mean_yield),
+        mean_biomass = round(mean(mean_biomass, na.rm = TRUE), 2),
+        mean_biomass_lab = paste0("Mean biomass: ", mean_yield),
+        sd_yield = round(sd(annual_yield, na.rm = TRUE), 2),
+        sd_yield_lab = paste0("SD yield: ", sd_yield),
+        sd_abundance = round(sd(annual_abundance, na.rm = TRUE), 2),
+        sd_abundance_lab = paste0("SD biomass: ", sd_yield),
+        cv_yield = round(sd(annual_yield, na.rm = TRUE)/mean(annual_yield, na.rm = TRUE), 2),
+        cv_yield_lab = paste0("CV yield: ", cv_yield),
+        cv_biomass = round(sd(mean_abundance, na.rm = TRUE)/mean(mean_abundance, na.rm = TRUE), 2),
+        cv_biomass_lab = paste0("CV biomass: ", cv_biomass),
+        yrs_below_yield_thresh = paste("% YR below yield thresh: ", round(sum(below_thresh_yld)/135, 2)),
+        yrs_below_biomass_thresh = paste("% YR below biomass thresh: ", round(sum(below_thresh_bm)/135, 2))
+      ) %>%
+      ungroup()
+    return(list(main_plt_df, supp_plt_df, med_yield))
+  }
+
+F_brf_maxes_yield <- get_f_maxes_yield(out_df = out,
+                              fleps_2_fs = spec_fleps_2_fs)
+F_brf_maxes_yield
+out_fs
+
+med_yield <- get_median_yield(df_out_fs = df_out_fs) 
+med_yield
+med_biomass <- get_median_biomass(df_out_fs = df_out_fs)
+med_biomass
+out <- df_yld_bm_stats_by_sim_f_frac_year(df_out_fs = df_out_fs,
+                                      sims_num_2_use = sims_2_use)
+out
+test_plot_df <- prep_ann_yield_abund_for_plot(
+  df_out_fs = out_fs,
+  frac_reserves = c(0, 0.25, 0.50),
+  f_fmsys = c(0, 0.52, 1.00, 2.09)
+)
+
+out_2 <- out_fs %>%
+  group_by(sim_num, reserve_frac, f_fmsy) %>%
   summarize(abundance = mean(abundance, na.rm = TRUE),
@@
 
+out_3 <- out_2 %>%
+  group_by(reserve_frac, f_fmsy) %>%
+  summarize(abundance = mean(abundance, na.rm = TRUE),
+            yield = mean(yield, na.rm = TRUE)) %>%
+  ungroup()
+
 ggplot(out_2, aes(x = as.numeric(reserve_frac), 
-                y = as.numeric(flep_ratio),
+                y = as.numeric(f_fmsy),
                 z = abundance)) +
@@
 
-out_3 <- out_2 %>%
-  group_by(reserve_frac, flep_ratio) %>%
-  summarize(abundance = mean(abundance, na.rm = TRUE),
-            yield = mean(yield, na.rm = TRUE)) %>%
-  ungroup()
-
 ggplot(out_3, aes(x = as.numeric(reserve_frac), 
-                y = as.numeric(flep_ratio),
+                y = as.numeric(f_fmsy),
                 z = abundance)) +

### 2023-11-07 _targets.R

@@ -255,6 +255,7 @@ list(
     larvpool_disp_conn_mat %>% purrr::map(., ~ matrix(.x[, 1], nrow = 2))
   ),
   # Environmental noise
+  # need to make n_sims number of noise signals for enso and white
   tar_target(noises_white,
              "white"),
   tar_target(noises_white_135,

### 2023-12-18 ms_figures_supp_figs.qmd
final working code, flag used functions, update gitignore file

--- 2023-11-04 ms_figures_supp_figs.qmd
@@
 ---
-title: "Recruits, abundance, and yield time series and contours"
+title: "Figures and supplemental figures for ecological resilience ms"
 author: "Botsford, Hastings, White, and Kilduff"
@@
 editor: visual
-params:
-  experiment: "larval_pool_blue_rockfish_mei_135_75"
 ---
+
+List of DuckDB tables
+
+-   "larval_pool_blue_rockfish_mei_135_75"
+-   "larval_pool_blue_rockfish_white_135_75"
+-   "larval_pool_cabezon_mei_135_75"
+-   "larval_pool_cabezon_white_135_75"
+-   "larval_pool_china_rockfish_mei_135_75"
+-   "larval_pool_china_rockfish_white_135_75"
+-   "no_dispersal_blue_rockfish_mei_135_75"
+-   "no_dispersal_blue_rockfish_white_135_75"
+-   "no_dispersal_cabezon_mei_135_75"
+-   "no_dispersal_cabezon_white_135_75"
+-   "no_dispersal_china_rockfish_mei_135_75"
+-   "no_dispersal_china_rockfish_white_135_75"
 
@@
 ```{r}
-#| label: Good label name
+#| label: setup 
 #| echo: false
-#| 
-# c("larval_pool_blue_rockfish_mei_135_75",
-# "larval_pool_blue_rockfish_white_135_75",
-# "larval_pool_cabezon_mei_135_75",
-# "larval_pool_cabezon_white_135_75",
-# "larval_pool_china_rockfish_mei_135_75",
-# "larval_pool_china_rockfish_white_135_75",
-# "no_dispersal_blue_rockfish_mei_135_75",
-# "no_dispersal_blue_rockfish_white_135_75",
-# "no_dispersal_cabezon_mei_135_75",
-# "no_dispersal_cabezon_white_135_75",
-# "no_dispersal_china_rockfish_mei_135_75",
-# "no_dispersal_china_rockfish_white_135_75")
+
+# load packages, source functions, set options, make output file, establish DB connection
+library(targets)
+library(DBI)
+library(duckdb)
+library(cowplot)
+suppressMessages(library(tidyverse))
+
+options(dplyr.summarise.inform = FALSE)
 
@@
 supp_figs_path <- file.path("output", "supp_figs")
+
+# Load project functions
+source("R/functions.R")
+source("R/fig_functions.R")
 
@@
 ```{r}
-#| label: load-packages-data
+#| label: load-data-set-global-parms
 #| echo: false
 
-library(targets)
-suppressMessages(library(tidyverse))
-library(duckdb)
-options(dplyr.summarise.inform = FALSE)
 # Load relevant data from target objexts
 tar_load(sim_nums)
-tar_load(sim_len)
+tar_load(burn_in)
+tar_load(sim_len_135)
 tar_load(species_flep_fished_ind)
@@
 
-# Load project functions
-source("R/functions.R")
+# constants
+burn_in_parm <- burn_in
+sim_len_parm <- sim_len_135
 
-# constants
-burn_in_parm <- 500
-sim_len_parm <- 135
+# plotting params
+x_text_position_parm <- 550 
+max_reserve_frac <- 0.5
+max_f_fmsy <- 2.5
 
-x_text_position_parm <- 550
+# set 
+r_seed <- 11
+set.seed(r_seed)
 
-waa_g <- sim_species_parms[[nice_species]][["biom_const"]] * sim_species_derived_vars[[nice_species]][["length_at_age"]] ^
-                    sim_species_parms[[nice_species]][["biom_exp"]]
+# A total of 25 (2023/11/08) simulations were run for each paramter set
+# This set allows us to determine the number of simulations to use 
+# in the contour plots to produce clear contours by picking a random subset of
+# simulations up to the full set of simulations
 
-# use functions to create useful data structures
-# FLEP to F reference tables by species
-spec_fleps_2_fs <-
-  get_fs_from_fleps(species = nice_species,
-                    flep_inds = species_flep_fished_ind,
-                    f_vals =  fishing_mortality_values)
+# num_sims_2_avg <- 5
+
+sims_2_use <- 1:5 # sort(sample(1:sim_nums, size = num_sims_2_avg, replace = FALSE))
 
@@
 ## Main figures
+
+brf_white_lp_current \<- get_current_exp(table_name = "larval_pool_blue_rockfish_white_135_75")
+
+brf_white_lp_nice \<- get_nice_exp(table_name = "larval_pool_blue_rockfish_white_135_75")
+
+brf_white_lp_current\[\[1\]\]
+
+brf_white_lp_current\[\[2\]\]
+
+brf_white_lp_current\[\[3\]\]
+
+brf_white_lp_nice\[\[1\]\]
+
+brf_white_lp_nice\[\[2\]\]
+
+brf_white_lp_nice\[\[3\]\]
+
+```{r}
+#| label: main-figs-and-species-parms
+
+# Set table names to be used to make the main figures
+
+table_name_nd <- "no_dispersal_blue_rockfish_mei_135_75"
+table_name_lp <- "larval_pool_blue_rockfish_mei_135_75"
+table_name_nd_white <- "no_dispersal_blue_rockfish_white_135_75"
+table_name_lp_white <- "larval_pool_blue_rockfish_white_135_75"
+
+# Get meta data descriptins from the table names and the pretty 
+# versions for plotting
+
+brf_mei_nd_current <- get_current_exp(table_name = table_name_nd)
+brf_mei_nd_nice <- get_nice_exp(table_name = table_name_nd)
+
+brf_white_nd_current <- get_current_exp(table_name = table_name_nd_white)
+brf_white_nd_nice <- get_nice_exp(table_name = table_name_nd_white)
+
+brf_mei_lp_current <- get_current_exp(table_name = table_name_lp)
+brf_mei_lp_nice <- get_nice_exp(table_name = table_name_lp)
+
+brf_white_lp_current <- get_current_exp(table_name = table_name_lp_white)
+brf_white_lp_nice <- get_nice_exp(table_name = table_name_lp_white)
+
+```
 
@@
 
-set.seed(11)
-num_sims_2_avg <- 5
-sims_2_use <- sort(sample(1:sim_nums, size = num_sims_2_avg, replace = FALSE))
+# use species specific vB params to create a weight at age data.frame that can be used to convert abundance at age to biomass at age
+species_name <- brf_mei_nd_nice[[2]]
+brf_waa_g <- sim_species_parms[[species_name]][["biom_const"]] * sim_species_derived_vars[[species_name]][["length_at_age"]] ^
+                    sim_species_parms[[species_name]][["biom_exp"]]
 
-table_name <- "no_dispersal_blue_rockfish_mei_135_75"
+brf_waa_g_df <- data.frame(age = 1: sim_species_parms[[species_name]]$A_max,
+                           waa_g = brf_waa_g)
 
+# use functions to create useful data structures
+# FLEP to F reference tables by species
+spec_fleps_2_fs <-
+  get_fs_from_fleps(species = species_name,
+                    flep_inds = species_flep_fished_ind,
+                    f_vals =  fishing_mortality_values)
+
+## Qry 
 qry <- paste0("SELECT  sim_num, reserve_frac, flep_ratio, year, age, 
@@
               sum(yield) as yield,
-              FROM '", table_name, 
+              FROM '", table_name_nd, 
               "' WHERE sim_num IN (", toString(sims_2_use), ") AND year > 500 
@@
 
-out <- dbGetQuery(conn = con, qry)
+sim_res_out <- dbGetQuery(conn = con, qry)
 
-out_2 <- out %>%
-  group_by(sim_num, reserve_frac, flep_ratio) %>%
-  summarize(abundance = mean(abundance, na.rm = TRUE),
-            yield = mean(yield, na.rm=TRUE)) %>%
-  ungroup()
+#######
 
-ggplot(out_2, aes(x = as.numeric(reserve_frac), 
-                y = as.numeric(flep_ratio),
-                z = abundance)) +
-  facet_grid(sim_num ~ .) +
-  geom_contour_filled()
+########### PIPELINING
+F_brf_maxes_yield <- get_f_maxes_yield(input_df = sim_res_out,
+                                         fleps_2_fs = spec_fleps_2_fs)
+F_brf_maxes_yield
 
-out_3 <- out_2 %>%
-  group_by(reserve_frac, flep_ratio) %>%
-  summarize(abundance = mean(abundance, na.rm = TRUE),
-            yield = mean(yield, na.rm = TRUE)) %>%
-  ungroup()
+out_fs <- df_add_fs_out (input_df = sim_res_out,
+                         spec_fleps_2_fs = spec_fleps_2_fs,
+                         F_maxes_yield = F_brf_maxes_yield, waa_g_df = brf_waa_g_df)
+out_fs
 
-ggplot(out_3, aes(x = as.numeric(reserve_frac), 
-                y = as.numeric(flep_ratio),
-                z = abundance)) +
-  geom_contour_filled()
+med_yield <- get_median_yield(input_df = out_fs) 
+med_yield
 
-# qry <- "SELECT reserve_frac, flep_ratio, sum(number) as total_nums, sum(yield) as total_yield from '", table_name, "'where year > 500 group by reserve_frac, flep_ratio order by reserve_frac asc, flep_ratio asc"
+med_biomass <- get_median_biomass(input_df = out_fs, age_mat = sim_species_parms$`Blue rockfish`$A_mat)
+med_biomass
 
+out_yld_bm_sims_f_frac_yr <-
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs,
+                                     age_mat = sim_species_parms$`Blue rockfish`$A_mat)#, sims_num_2_use = sims_2_use
+
+# out_yld_bm_sims_f_frac_yr
+# pipeline works to here
+
+sum_stats_f_frac_df <-
+  summary_stats_by_f_frac(
+    out_sim_f_frac_yr = out_yld_bm_sims_f_frac_yr,
+    median_yield = med_yield,
+    median_biomass = med_biomass
+  )
+sum_stats_f_frac_df
+
+## Plotting
+
+p1 <- sum_stats_f_frac_df[[2]] %>%
+  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
+  ggplot(.,
+       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_biomass_thresh)) +
+  metR::geom_contour_fill(bins = 12) +
+  ggtitle(paste0(
+        brf_mei_nd_nice[[2]],
+        " ",
+        brf_mei_nd_nice[[1]],
+        " ",
+        brf_mei_nd_nice[[3]],
+        ":\nTime below mean median biomass "
+      )) +
+      xlab("Fraction of coastline in reserves") +
+      ylab("Harvest Rate (F/Fmsy)") +
+      scale_fill_viridis_c(option = "D", direction = -1) +
+      geom_segment(aes(
+        x = 0,
+        xend = max_reserve_frac,
+        y = 1,
+        yend = 1
+      ), colour = "black",
+      linetype = 2) +
+      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
+      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
+      theme_bw()
+
+p2 <- sum_stats_f_frac_df[[2]] %>%
+  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
+  ggplot(.,
+       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_yield_thresh)) +
+  metR::geom_contour_fill(bins = 12) + 
+  ggtitle(paste0(
+        brf_mei_nd_nice[[2]],
+        " ",
+        brf_mei_nd_nice[[1]],
+        " ",
+        brf_mei_nd_nice[[3]],
+        ":\nTime below median max yield"
+      )) +
+      xlab("Fraction of coastline in reserves") +
+      ylab("Harvest Rate (F/Fmsy)") +
+      scale_fill_viridis_c(option = "D", direction = -1) +
+      geom_segment(aes(
+        x = 0,
+        xend = max_reserve_frac,
+        y = 1,
+        yend = 1
+      ), colour = "black",
+      linetype = 2) +
+      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
+      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
+      theme_bw()
+
+fig3 <- plot_grid(p1, p2, labels = letters[1:2], label_size = 9, byrow = FALSE)
+
+ggsave(filename = "output/tmp_figs/fig3-brf-nd-mei-biomass-yield.png", 
+       plot = fig3, 
+       height = 8, width = 5)
+ggsave(filename = "output/tmp_figs/fig3-brf-nd-mei-biomass-yield.svg", 
+       plot = fig3, 
+       height = 8, width = 5)
+
+# ggsave(filename = "output/tmp_figs/fig3-yield.png", plot = p1)
+# ggsave(filename = "output/tmp_figs/fig3-biomass.png", plot = p2)
+# 
+# ggsave(filename = "output/tmp_figs/fig3-yield.svg", plot = p1)
+# ggsave(filename = "output/tmp_figs/fig3-biomass.svg", plot = p2)
+
+```
+
+```{r}
+out_fs %>%
+  group_by(sim_num, reserve_frac, f_fmsy, year) %>%
+  summarize(
+    ann_yield = sum(yield, na.rm = TRUE),
+    ann_biomass = sum(biomass_at_age, na.rm = TRUE)
+  ) %>%
+  filter(near(f_fmsy, 1) | near(f_fmsy, 0.52) | near(f_fmsy, 2.09),  near(as.numeric(reserve_frac), 0)) %>%
+  ggplot(., aes(x = year, y = ann_biomass)) +
+  geom_line() +
+  facet_grid(f_fmsy ~ sim_num)
+
+out_fs %>%
+  group_by(sim_num, reserve_frac, f_fmsy, year) %>%
+  summarize(
+    ann_yield = sum(yield, na.rm = TRUE),
+    ann_biomass = sum(biomass_at_age, na.rm = TRUE)
+  ) %>%
+ filter(near(f_fmsy, 1) | near(f_fmsy, 0.52) | near(f_fmsy, 2.09),  near(as.numeric(reserve_frac), 0)) %>%
+  ungroup() %>%
+  ggplot(., aes(x = year, y = ann_yield)) +
+  geom_line() +
+  facet_grid(f_fmsy ~ sim_num)
+
+out_fs %>%
+    group_by(sim_num, reserve_frac, f_fmsy, year) %>%
+    summarize(
+        ann_yield = sum(yield, na.rm = TRUE),
+        ann_biomass = sum(biomass_at_age, na.rm = TRUE)
+    ) %>%
+    # filter(near(f_fmsy, 1) | near(f_fmsy, 0.52) | near(f_fmsy, 2.09),  near(as.numeric(reserve_frac), 0)) %>%
+    ungroup() %>%
+  group_by(sim_num, f_fmsy) %>%
+  summarize(med_ann_yield = median(ann_yield)) %>%
+  ggplot(., aes(x = f_fmsy, y = med_ann_yield)) +
+  geom_line() +
+  facet_grid(sim_num ~ .)
+
+```
+
+### Figure 4
+
+Contour plots showing the buffering effects of harvest rate and marine reserves on the abundance of a fished population, when there is larval pool dispersal between the fished and reserve habitat patches.
+
+Species: Blue rockfish
+
+Dispersal: Larval Pool Dispersal
+
+Environmental noise: ENSO (MEI)
+
+```{r}
+#| label: figure_4
+
+# use species specific vB params to create a weight at age data.frame that can be used to convert abundance at age to biomass at age
+species_name <- brf_mei_lp_nice[[2]]
+brf_waa_g <- sim_species_parms[[species_name]][["biom_const"]] * sim_species_derived_vars[[species_name]][["length_at_age"]] ^
+                    sim_species_parms[[species_name]][["biom_exp"]]
+
+brf_waa_g_df <- data.frame(age = 1: sim_species_parms[[species_name]]$A_max,
+                           waa_g = brf_waa_g)
+
+# use functions to create useful data structures
+# FLEP to F reference tables by species
+spec_fleps_2_fs <-
+  get_fs_from_fleps(species = species_name,
+                    flep_inds = species_flep_fished_ind,
+                    f_vals =  fishing_mortality_values)
+
+## Qry 
+qry <- paste0("SELECT  sim_num, reserve_frac, flep_ratio, year, age, 
+              sum(number) as abundance,
+              sum(yield) as yield,
+              FROM '", table_name_lp, 
+              "' WHERE sim_num IN (", toString(sims_2_use), ") AND year > 500 
+              GROUP BY sim_num, reserve_frac, flep_ratio, year, age
+              ORDER BY sim_num, reserve_frac, flep_ratio, year, age
+              ")
+
+sim_res_out_brf_mei_lp <- dbGetQuery(conn = con, qry)
+
+#######
+
+########### PIPELINING
+F_brf_maxes_yield <- get_f_maxes_yield(input_df = sim_res_out_brf_mei_lp,
+                                         fleps_2_fs = spec_fleps_2_fs)
+F_brf_maxes_yield
+
+out_fs <- df_add_fs_out (input_df = sim_res_out_brf_mei_lp,
+                         spec_fleps_2_fs = spec_fleps_2_fs,
+                         F_maxes_yield = F_brf_maxes_yield, waa_g_df = brf_waa_g_df)
+out_fs
+
+med_yield <- get_median_yield(input_df = out_fs) 
+med_yield
+
+med_biomass <- get_median_biomass(input_df = out_fs,
+                                  age_mat = sim_species_parms$`Blue rockfish`$A_mat)
+med_biomass
+
+out_yld_bm_sims_f_frac_yr <-
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs, 
+                                     age_mat = sim_species_parms$`Blue rockfish`$A_mat)
+
+# pipeline works to here
+
+sum_stats_f_frac_df <-
+  summary_stats_by_f_frac(
+    out_sim_f_frac_yr = out_yld_bm_sims_f_frac_yr,
+    median_yield = med_yield,
+    median_biomass = med_biomass
+  )
+sum_stats_f_frac_df
+
+## Plotting
+
+p1 <- sum_stats_f_frac_df[[2]] %>%
+  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
+  ggplot(.,
+       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_biomass_thresh)) +
+  metR::geom_contour_fill(bins = 12) +
+  ggtitle(paste0(
+        brf_mei_lp_nice[[2]],
+        " ",
+        brf_mei_lp_nice[[1]],
+        " ",
+        brf_mei_lp_nice[[3]],
+        ":\nTime below mean median biomass "
+      )) +
+      xlab("Fraction of coastline in reserves") +
+      ylab("Harvest Rate (F/Fmsy)") +
+      scale_fill_viridis_c(option = "D", direction = -1) +
+      geom_segment(aes(
+        x = 0,
+        xend = max_reserve_frac,
+        y = 1,
+        yend = 1
+      ), colour = "black",
+      linetype = 2) +
+      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
+      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
+      theme_bw()
+
+p2 <- sum_stats_f_frac_df[[2]] %>%
+  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
+  ggplot(.,
+       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_yield_thresh)) +
+  metR::geom_contour_fill(bins = 12) + 
+  ggtitle(paste0(
+        brf_mei_lp_nice[[2]],
+        " ",
+        brf_mei_lp_nice[[1]],
+        " ",
+        brf_mei_lp_nice[[3]],
+        ":\nTime below median max yield"
+      )) +
+      xlab("Fraction of coastline in reserves") +
+      ylab("Harvest Rate (F/Fmsy)") +
+      scale_fill_viridis_c(option = "D", direction = -1) +
+      geom_segment(aes(
+        x = 0,
+        xend = max_reserve_frac,
+        y = 1,
+        yend = 1
+      ), colour = "black",
+      linetype = 2) +
+      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
+      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
+      theme_bw()
+
+fig4 <- plot_grid(p1, p2, labels = letters[1:2], label_size = 9, byrow = FALSE)
+
+ggsave(filename = "output/tmp_figs/fig4-brf-lp-biomass-yield.png", 
+       plot = fig4, 
+       height = 8, width = 5)
+ggsave(filename = "output/tmp_figs/fig4-brf-lp-biomass-yield.svg", 
+       plot = fig4, 
+       height = 8, width = 5)
+
+# ggsave(filename = "output/tmp_figs/fig4-yield.png", plot = p1)
+# ggsave(filename = "output/tmp_figs/fig4-biomass.png", plot = p2)
+# 
+# ggsave(filename = "output/tmp_figs/fig4-yield.svg", plot = p1)
+# ggsave(filename = "output/tmp_figs/fig4-biomass.svg", plot = p2)
+
+```
+
+```{r}
+
+#| label: boneyard
+prep_ann_yield_abund_for_plot <- function(df_out_fs,
+                                          frac_reserves = c(0, 0.25, 0.50),
+                                          f_fmsys = c(0, 0.52, 1.00, 2.09)) {
+
+  sim_num_2_use <- min(df_out_fs$sim_num)
+  if (length(f_fmsys) < 1 | is.null(f_fmsys)) {
+    stop("Please specify f_fmsy values to use")
+  }
+
+  if (length(frac_reserves) < 1 | is.null(frac_reserves)) {
+    stop("Please specify frac_reserves values to use")
+  }
+
+    # make a sub function
+
+    return(list(main_plt_df, supp_plt_df, med_yield))
+  }
 ```
@@
 #| label: figure_5
+
+# brf_mei_lp_nice[[2]]
+# brf_mei_lp_nice[[1]]
+# brf_mei_lp_nice[[3]]
+
+bio_yield_df <- out_fs
+summary_stats_df <- sum_stats_f_frac_df
+
+yield_thresh <- med_yield
+biomass_thresh <- med_biomass
+
+exp_deets <- brf_mei_lp_nice
+
+text <- TRUE
+# x_text_val <- 550
+x_min <- 500
+x_max <- 635
+x_text_val <- (x_max) - (x_max - x_min)/2
+
+r_seed <- 34
+
+frac_reserves <- c(0, 0.25, 0.50)
+f_fmsys <- c(0.52, 1.00, 2.09)
+
+# facet_bm_yld_ts_plots <- function(bio_yield_df,  # main_plt_df
+#                                  summary_stats_df, # sub_plt_df,
+#                                  yield_thresh,
+#                                  biomass_thresh,
+#                                  exp_deets,
+#                                  x_text_val = 550,
+#                                  r_seed = 34,
+#                                  frac_reserves = c(0, 0.25, 0.50),
+#                                  f_fmsys = c(0.52, 1.00, 2.09)) {
+
+set.seed(r_seed)
+sim_2_use <-
+  sample(sort(unique(bio_yield_df$sim_num)), 1, replace = FALSE)
+
+f_fmsys_bio <- c(0, f_fmsys)
+
+### FUNCTION
+plt_species <- unique(exp_deets[[2]])
+plt_dispersal <- unique(exp_deets[[1]])
+plt_noise <- unique(exp_deets[[3]])
+
+title_string <- paste0(
+  "Simulation results: \n",
+  plt_species,
+  " with ",
+  plt_dispersal,
+  " dispersal and ",
+  plt_noise,
+  " noise. \n"
+)
+
+### FUNCTION
+u_f_fmsys <- unique(bio_yield_df$f_fmsy)
+
+u_f_fmsys <-
+  purrr::map_dbl(f_fmsys_bio,  ~ u_f_fmsys[which.min(abs(u_f_fmsys - .x))])
+
+# u_f_fmsys <- u_f_fmsys[u_f_fmsys_ind]
+
+### FUNCTION
+quants_df <- bio_yield_df %>%
+  dplyr::group_by(sim_num, reserve_frac, f_fmsy, year) %>%
+  dplyr::summarize(annual_yield = sum(yield),
+                   annual_biomass = sum(biomass_at_age)) %>%
+  dplyr::ungroup() %>%
+  dplyr::group_by(sim_num, reserve_frac, f_fmsy) %>%
+  dplyr::summarize(
+    quant_80_bio = quantile(annual_biomass, 0.8),
+    quant_20_bio = quantile(annual_biomass, 0.2),
+    quant_80_yld = quantile(annual_yield, 0.8),
+    quant_20_yld = quantile(annual_yield, 0.2)
+  ) %>%
+  dplyr::ungroup() %>%
+  dplyr::group_by(reserve_frac, f_fmsy) %>%
+  dplyr::summarize(
+    quant_80_mean_bio = mean(quant_80_bio),
+    quant_20_mean_bio = mean(quant_20_bio),
+    quant_80_mean_yld = mean(quant_80_yld),
+    quant_20_mean_yld = mean(quant_20_yld)
+  ) %>%
+  dplyr::ungroup() %>%
+  dplyr::mutate(reserve_frac = as.numeric(reserve_frac)) %>%
+  dplyr::filter(reduce(map(
+    frac_reserves, near, x = reserve_frac, tol = 1e-4
+  ), `|`)) %>%
+  dplyr::filter(reduce(map(
+    u_f_fmsys, near, x = f_fmsy, tol = 1e-4
+  ), `|`))
+
+### FUNCTION
+bio_yield_sel_df <- bio_yield_df %>%
+  dplyr::mutate(reserve_frac = as.numeric(reserve_frac),
+                year = year - 500) %>%
+  dplyr::filter(sim_num == sim_2_use) %>%
+  dplyr::filter(reduce(map(
+    frac_reserves, near, x = reserve_frac, tol = 1e-4
+  ), `|`)) %>%
+  dplyr::filter(reduce(map(
+    u_f_fmsys, near, x = f_fmsy, tol = 1e-4
+  ), `|`)) %>%
+  dplyr::group_by(sim_num, reserve_frac, f_fmsy, year) %>%
+  dplyr::summarize(annual_biomass = sum(biomass_at_age),
+                   annual_yield = sum(yield)) %>%
+  dplyr::ungroup()
+
+### FUNCTION
+biom_ts_plt <- ggplot(
+  bio_yield_sel_df %>% dplyr::filter(sim_num == sim_2_use),
+  aes(x = year, y = annual_biomass)
+) +
+  facet_grid(reserve_frac ~ f_fmsy,
+             labeller = labeller(f_fmsy = label_both,
+                                 reserve_frac = label_both)) +
+  geom_ribbon(aes(
+    ymin = biomass_thresh,
+    ymax = pmin(annual_biomass, biomass_thresh),
+    fill = "Biomass lower"
+  )) +
+  geom_ribbon(aes(
+    ymin = annual_biomass,
+    ymax = pmin(annual_biomass, biomass_thresh),
+    fill = "Biomass higher"
+  )) +
+  geom_line(colour = "black") +
+    geom_segment(aes(x = 1, y = biomass_thresh, 
+                     xend = 135, yend = biomass_thresh),
+             colour = "red",
+             linewidth = 0.6) +
+  scale_fill_manual(values = c("black", "grey80")) +
+  # geom_text(
+  #   data = summary_stats_df,
+  #   x = x_text_val,
+  #   y = 11000,
+  #   aes(label = mean_biomass_lab)
+  # ) +
+  # geom_text(
+  #   data = summary_stats_df,
+  #   x = x_text_val,
+  #   y = 12500,
+  #   aes(label = sd_biomass_lab)
+# ) +
+# geom_text(
+#   data = summary_stats_df,
+#   x = x_text_val,
+#   y = 14000,
+#   aes(label = yrs_below_thresh)
+# ) +
+# geom_text(
+#   data = summary_stats_df,
+#   x = x_text_val,
+#   y = 9500,
+#   aes(label = cv_biomass_lab)
+# ) +
+labs(fill = "Above/Below Biomass threshold") +
+  ggtitle(title_string) +
+  xlab("Year") +
+  ylab("Biomass (metric tons)") +
+  ylim(0, NA) +
+  labs(colour = "Reserve\nfraction") +
+  theme_minimal() +
+  # geom_hline(data = quants_df, aes(yintercept = quant_80_mean_bio), colour = "orange", linewidth = 1.1, linetype = 1) +
+  # geom_hline(data = quants_df, aes(yintercept = quant_20_mean_bio), colour = "orange", linewidth = 1.1, linetype = 1) +
+  scale_x_continuous(expand = expansion(mult = 0, add = 0)) +
+  theme(
+    axis.line = element_line(colour = "black"),
+    panel.background = element_rect(fill = "white"),
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    panel.border = element_blank()
+  )
+
+#### ?? FUNCTION: YIELD VERSION
+yld_ts_plt <- bio_yield_sel_df %>%
+  dplyr::filter(f_fmsy != 0) %>%
+  ggplot(data = ., aes(x = year, y = annual_yield)) +
+  facet_grid(reserve_frac ~ f_fmsy,
+             labeller = labeller(f_fmsy = label_both,
+                                 reserve_frac = label_both)) +
+  geom_ribbon(aes(
+    ymin = yield_thresh,
+    ymax = pmin(annual_yield, yield_thresh),
+    fill = "Yield lower"
+  )) +
+  geom_ribbon(aes(
+    ymin = annual_yield,
+    ymax = pmin(annual_yield, yield_thresh),
+    fill = "Yield higher"
+  )) +
+  geom_line(colour = "black") +
+  geom_segment(aes(x = 1, y = yield_thresh, 
+                     xend = 135, yend = yield_thresh),
+             colour = "red",
+             linewidth = 0.6) +
+  scale_fill_manual(values = c("black", "grey80")) +
+  # geom_text(
+  #   data = summary_stats_df,
+  #   x = x_text_val,
+  #   y = 11000,
+  #   aes(label = mean_biomass_lab)
+  # ) +
+  # geom_text(
+  #   data = summary_stats_df,
+  #   x = x_text_val,
+  #   y = 12500,
+  #   aes(label = sd_biomass_lab)
+# ) +
+# geom_text(
+#   data = summary_stats_df,
+#   x = x_text_val,
+#   y = 14000,
+#   aes(label = yrs_below_thresh)
+# ) +
+# geom_text(
+#   data = summary_stats_df,
+#   x = x_text_val,
+#   y = 9500,
+#   aes(label = cv_biomass_lab)
+# ) +
+labs(fill = "Above/Below Yield threshold") +
+  ggtitle(title_string) +
+  xlab("Year") +
+  ylab("Yield (metric tons)") +
+  ylim(0, NA) +
+  labs(colour = "Reserve\nfraction") +
+  theme_minimal() +
+  # geom_hline(data = quants_df %>% dplyr::filter(f_fmsy != 0), aes(yintercept = quant_80_mean_yld), colour = "orange", linewidth = 1.1, linetype = 1) +
+  # geom_hline(data = quants_df %>% dplyr::filter(f_fmsy != 0), aes(yintercept = quant_20_mean_yld), colour = "orange", linewidth = 1.1, linetype = 1) +
+  scale_x_continuous(expand = expansion(mult = 0, add = 0)) +
+  theme(
+    axis.line = element_line(colour = "black"),
+    panel.background = element_rect(fill = "white"),
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    panel.border = element_blank()
+  )
+# }
+
+print(biom_ts_plt)
+print(yld_ts_plt)
+
+ggsave(filename = "output/tmp_figs/fig5-biomass-timeseries.png", plot = biom_ts_plt,
+       height = 8, width = 10)
+ggsave(filename = "output/tmp_figs/fig6-yield-timeseries.png", plot = yld_ts_plt,
+       height = 8, width = 10)
+
+ggsave(filename = "output/tmp_figs/fig5-biomass-timeseries.svg", plot = biom_ts_plt,
+       height = 8, width = 10)
+ggsave(filename = "output/tmp_figs/fig6-yield-timeseries.svg", plot = yld_ts_plt,
+       height = 8, width = 10)
 
@@
 
+t_c <- species_parms[which(species_parms$species == species_name),]$A_fish
+
+u_f_fmsys <- unique(bio_yield_df$f_fmsy)
+
+f_fmsys_targs <- c(0.52, 1.00, 2.09)
+
+u_f_fmsys <-
+  purrr::map_dbl(f_fmsys_targs,  ~ u_f_fmsys[which.min(abs(u_f_fmsys - .x))])
+
+recs_spec_disp_noise_ffmsy_plt <- bio_yield_df %>%
+  dplyr::filter(sim_num == 1, age == 1) %>%
+  dplyr::mutate(reserve_frac = as.numeric(reserve_frac)) %>%
+  dplyr::filter(reduce(map(
+    frac_reserves, near, x = reserve_frac, tol = 1e-4
+  ), `|`),
+  reduce(map(
+    u_f_fmsys, near, x = f_fmsy, tol = 1e-4
+  ), `|`)) %>%
+  mutate(year = year - 500,
+         lagged_year = year + t_c)
+
+yield_spec_disp_noise_prep_plt <- bio_yield_df %>% 
+  dplyr::filter(sim_num == 1) %>%
+  dplyr::mutate(reserve_frac = as.numeric(reserve_frac)) %>%
+  dplyr::group_by(reserve_frac, f_fmsy, year) %>%
+  dplyr::summarize(annual_yield = sum(yield)) %>%
+  dplyr::ungroup() %>%
+  dplyr::filter(reduce(map(
+    frac_reserves, near, x = reserve_frac, tol = 1e-4
+  ), `|`),
+  reduce(map(
+    u_f_fmsys, near, x = f_fmsy, tol = 1e-4
+  ), `|`))  %>%
+  mutate(year = year - 500)
+
+plt_start_yr <- 100
+plt_end_yr <- 135
+
+scaled_yield_plt <- yield_spec_disp_noise_prep_plt %>%
+  group_by(reserve_frac, f_fmsy) %>%
+  mutate(scaled_yield = scale(annual_yield)[,1]) %>%
+  ungroup()
+
+scaled_recs_plt <- recs_spec_disp_noise_ffmsy_plt %>% 
+  group_by(reserve_frac, f_fmsy) %>%
+  mutate(scaled_recruits = scale(biomass_at_age)[,1]) %>%
+  ungroup()
+
+scaled_yield_plt_4corr <- scaled_yield_plt %>%
+  mutate(reserve_frac = as.character(reserve_frac), 
+         f_fmsy = as.character(f_fmsy)) %>%
+  select(reserve_frac, f_fmsy, year, scaled_yield)
+
+scaled_recs_plt_4corr <- scaled_recs_plt %>%
+  mutate(reserve_frac = as.character(reserve_frac), 
+         f_fmsy = as.character(f_fmsy))  %>%
+  select(reserve_frac, f_fmsy, lagged_year, scaled_recruits)
+
+corr_vals <- scaled_yield_plt_4corr %>%
+  left_join(scaled_recs_plt_4corr,
+            by = c("reserve_frac" = "reserve_frac",
+                   "f_fmsy" = "f_fmsy",
+                   "year" = "lagged_year")) %>%
+  filter(.,complete.cases(reserve_frac, f_fmsy, year, scaled_yield, scaled_recruits)) %>%
+  group_by(reserve_frac, f_fmsy) %>%
+  summarise(corr = cor(scaled_yield, scaled_recruits))
+
+lagged_recs_yield_plt <- ggplot(scaled_yield_plt %>% 
+  filter(year > plt_start_yr, 
+         year <= plt_end_yr), 
+       aes(x = year, y = scaled_yield)) + 
+  facet_grid(reserve_frac ~ f_fmsy,
+               labeller = labeller(f_fmsy = label_both,
+                                   reserve_frac = label_both)) +
+  geom_line(linewidth = 1.2) +
+  geom_line(data = scaled_recs_plt %>% filter(lagged_year > plt_start_yr, 
+         lagged_year <= plt_end_yr), aes(x = lagged_year, y = scaled_recruits), 
+            colour = "blue", linewidth = 1.2) +
+  geom_text(
+      data = corr_vals,
+      x = 1.1 * plt_start_yr ,
+      y = 3,
+      aes(label = paste0("Corr: ", round(corr, 3)))
+  ) +
+  ylab("Scaled yield (black) and lagged + scaled recruits (blue)") +
+  xlab("Year") +
+  theme_bw()
+
+print(lagged_recs_yield_plt)
+
+ggsave(
+  filename = "output/tmp_figs/fig7-lagged-recs-yield-timeseries-lw.png",
+  plot = lagged_recs_yield_plt,
+  height = 8,
+  width = 10
+)
+
+ggsave(
+  filename = "output/tmp_figs/fig7-lagged-recs-yield-timeseries-lw.svg",
+  plot = lagged_recs_yield_plt,
+  height = 8,
+  width = 10
+)
 ```
+
+### Figure 3 - white noise check
+
+Contour plots showing the buffering effects of harvest rate and marine reserves on the abundance of a fished population, when there is no larval dispersal between the fished and reserve habitat patches.
+
+Species: Blue rockfish
+
+Dispersal: no dispersal
+
+Environmental noise: white noise
+
+```{r}
+
+```
+
+### Figure 4 - white noise check
+
+Contour plots showing the buffering effects of harvest rate and marine reserves on the abundance of a fished population, when there is larval pool dispersal between the fished and reserve habitat patches.
+
+Species: Blue rockfish
+
+Dispersal: Larval Pool Dispersal
+
+Environmental noise: White
+
+```{r}
+
+# 
+# ggsave(filename = "output/tmp_figs/fig4-yield-white-noise-chk.png", plot = p1)
+# ggsave(filename = "output/tmp_figs/fig4-biomass-white-noise-chk.png", plot = p2)
+
+```
+
+### Cabezon
+
+```{r}
+# # Set table names to be used to make the main figures
+# 
+# table_name_nd <- "no_dispersal_cabezon_mei_135_75"
+# table_name_lp <- "larval_pool_cabezon_mei_135_75"
+# table_name_nd_white <- "no_dispersal_abezon_white_135_75"
+# table_name_lp_white <- "larval_pool_cabezon_white_135_75"
+# 
+# # Get meta data descriptins from the table names and the pretty 
+# # versions for plotting
+# 
+# cab_mei_nd_current <- get_current_exp(table_name = table_name_nd)
+# cab_mei_nd_nice <- get_nice_exp(table_name = table_name_nd)
+# cab_white_nd_current <- get_current_exp(table_name = table_name_nd_white)
+# cab_white_nd_nice <- get_nice_exp(table_name = table_name_nd_white)
+# cab_mei_lp_current <- get_current_exp(table_name = table_name_lp)
+# cab_mei_lp_nice <- get_nice_exp(table_name = table_name_lp)
+# cab_white_lp_current <- get_current_exp(table_name = table_name_lp_white)
+# cab_white_lp_nice <- get_nice_exp(table_name = table_name_lp_white)
+#
+
+```
+
+### Figure 3 - MEI Cabezon
+
+Contour plots showing the buffering effects of harvest rate and marine reserves on the abundance of a fished population, when there is no larval dispersal between the fished and reserve habitat patches.
+
+Species: Cabezon
+
+Dispersal: No Dispersal
+
+Environmental noise: ENSO (MEI)
+
+```{r}
+#| label: figure_3
+# 
+# # use species specific vB params to create a weight at age data.frame that can be used to convert abundance at age to biomass at age
+# species_name <- cab_mei_nd_nice[[2]]
+# brf_waa_g <- sim_species_parms[[species_name]][["biom_const"]] * sim_species_derived_vars[[species_name]][["length_at_age"]] ^
+#                     sim_species_parms[[species_name]][["biom_exp"]]
+# 
+# brf_waa_g_df <- data.frame(age = 1: sim_species_parms[[species_name]]$A_max,
+#                            waa_g = brf_waa_g)
+# 
+# # use functions to create useful data structures
+# # FLEP to F reference tables by species
+# spec_fleps_2_fs <-
+#   get_fs_from_fleps(species = species_name,
+#                     flep_inds = species_flep_fished_ind,
+#                     f_vals =  fishing_mortality_values) 
+# 
+# ## Qry 
+# qry <- paste0("SELECT  sim_num, reserve_frac, flep_ratio, year, age, 
+#               sum(number) as abundance,
+#               sum(yield) as yield,
+#               FROM '", table_name_nd, 
+#               "' WHERE sim_num IN (", toString(sims_2_use), ") AND year > 500 
+#               GROUP BY sim_num, reserve_frac, flep_ratio, year, age
+#               ORDER BY sim_num, reserve_frac, flep_ratio, year, age
+#               ")
+# 
+# sim_res_out <- dbGetQuery(conn = con, qry)
+# 
+# #######
+# 
+# 
+# ########### PIPELINING
+# F_brf_maxes_yield <- get_f_maxes_yield(input_df = sim_res_out,
+#                                          fleps_2_fs = spec_fleps_2_fs)
+# F_brf_maxes_yield
+# 
+# out_fs <- df_add_fs_out (input_df = sim_res_out,
+#                          spec_fleps_2_fs = spec_fleps_2_fs,
+#                          F_maxes_yield = F_brf_maxes_yield, waa_g_df = brf_waa_g_df)
+# out_fs
+# 
+# med_yield <- get_median_yield(input_df = out_fs) 
+# med_yield
+# 
+# med_biomass <- get_median_biomass(input_df = out_fs, age_mat = sim_species_parms$`Blue rockfish`$A_mat)
+# med_biomass
+# 
+# out_yld_bm_sims_f_frac_yr <-
+#   df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs,
+#                                      age_mat = sim_species_parms$`Blue rockfish`$A_mat)#, sims_num_2_use = sims_2_use
+# 
+# # out_yld_bm_sims_f_frac_yr
+# # pipeline works to here
+# 
+# sum_stats_f_frac_df <-
+#   summary_stats_by_f_frac(
+#     out_sim_f_frac_yr = out_yld_bm_sims_f_frac_yr,
+#     median_yield = med_yield,
+#     median_biomass = med_biomass
+#   )
+# sum_stats_f_frac_df
+# 
+# ## Plotting
+# 
+# p1 <- sum_stats_f_frac_df[[2]] %>%
+#   filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
+#   ggplot(.,
+#        aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_yield_thresh)) +
+#   metR::geom_contour_fill(bins = 12) + 
+#   ggtitle(paste0(
+#         cab_mei_nd_nice[[2]],
+#         " ",
+#         cab_mei_nd_nice[[1]],
+#         " ",
+#         cab_mei_nd_nice[[3]],
+#         ":\nTime below median max yield"
+#       )) +
+#       xlab("Fraction of coastline in reserves") +
+#       ylab("Harvest Rate (F/Fmsy)") +
+#       scale_fill_viridis_c(option = "D", direction = -1) +
+#       geom_segment(aes(
+#         x = 0,
+#         xend = max_reserve_frac,
+#         y = 1,
+#         yend = 1
+#       ), colour = "black",
+#       linetype = 2) +
+#       scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
+#       scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
+#       theme_bw()
+# 
+# 
+# p2 <- sum_stats_f_frac_df[[2]] %>%
+#   filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
+#   ggplot(.,
+#        aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_biomass_thresh)) +
+#   metR::geom_contour_fill(bins = 12) +
+#   ggtitle(paste0(
+#         cab_mei_nd_nice[[2]],
+#         " ",
+#         cab_mei_nd_nice[[1]],
+#         " ",
+#         cab_mei_nd_nice[[3]],
+#         ":\nTime below mean median biomass "
+#       )) +
+#       xlab("Fraction of coastline in reserves") +
+#       ylab("Harvest Rate (F/Fmsy)") +
+#       scale_fill_viridis_c(option = "D", direction = -1) +
+#       geom_segment(aes(
+#         x = 0,
+#         xend = max_reserve_frac,
+#         y = 1,
+#         yend = 1
+#       ), colour = "black",
+#       linetype = 2) +
+#       scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
+#       scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
+#       theme_bw()
+# 
+# print(p1)
+# print(p2)
+
+# ggsave(filename = "output/tmp_figs/fig3-yield-cab.png", plot = p1)
+# ggsave(filename = "output/tmp_figs/fig3-biomass-cab.png", plot = p2)
+
+```
+
+### Better funcs
+
+```{r}
+
+table_name_chr_nd_white <- "no_dispersal_china_rockfish_white_135_75"
+table_name_cab_nd_white <- "no_dispersal_cabezon_white_135_75"
+table_name_chr_lp_white <- "larval_pool_china_rockfish_white_135_75"
+table_name_cab_lp_white <- "larval_pool_cabezon_white_135_75"
+
+table_name_chr_nd_mei <- "no_dispersal_china_rockfish_mei_135_75"
+table_name_cab_nd_mei <- "no_dispersal_cabezon_mei_135_75"
+table_name_chr_lp_mei <- "larval_pool_china_rockfish_mei_135_75"
+table_name_cab_lp_mei <- "larval_pool_cabezon_mei_135_75"
+
+# Get meta data descriptins from the table names and the pretty 
+# versions for plotting
+
+chr_nd_white_nice <- get_nice_exp(table_name = table_name_chr_nd_white)
+cab_nd_white_nice <- get_nice_exp(table_name = table_name_cab_nd_white)
+chr_lp_white_nice <- get_nice_exp(table_name = table_name_chr_lp_white)
+cab_lp_white_nice <- get_nice_exp(table_name = table_name_cab_lp_white)
+chr_nd_mei_nice <- get_nice_exp(table_name = table_name_chr_nd_mei)
+cab_nd_mei_nice <- get_nice_exp(table_name = table_name_cab_nd_mei)
+chr_lp_mei_nice <- get_nice_exp(table_name = table_name_chr_lp_mei)
+cab_lp_mei_nice <- get_nice_exp(table_name = table_name_cab_lp_mei)
+
+## Qry
+
+run_qry_get_sims <- function(table_name, burn_in = 500) {
+  con <- DBI::dbConnect(duckdb::duckdb(),
+                        dbdir = "data/sim_out.duckdb",
+                        read_only = FALSE)
+  qry <-
+    paste0(
+      "SELECT  sim_num, reserve_frac, flep_ratio, year, age,
+              sum(number) as abundance,
+              sum(yield) as yield,
+              FROM '",
+      table_name,
+      "' WHERE year > 500
+              GROUP BY sim_num, reserve_frac, flep_ratio, year, age
+              ORDER BY sim_num, reserve_frac, flep_ratio, year, age
+              "
+    )
+
+  sim_res_out <- dbGetQuery(conn = con, qry)
+  sim_res_out$year = sim_res_out$year - 500
+  DBI::dbDisconnect(conn = con, shutdown=TRUE)
+  return(sim_res_out)
+}
+
+chr_nd_white_df <-
+  run_qry_get_sims(table_name = table_name_chr_nd_white, burn_in = 500)
+cab_nd_white_df <-
+  run_qry_get_sims(table_name = table_name_cab_nd_white, burn_in = 500)
+chr_lp_white_df <-
+  run_qry_get_sims(table_name = table_name_chr_lp_white, burn_in = 500)
+cab_lp_white_df <-
+  run_qry_get_sims(table_name = table_name_cab_lp_white, burn_in = 500)
+chr_nd_mei_df <-
+  run_qry_get_sims(table_name = table_name_chr_nd_mei, burn_in = 500)
+cab_nd_mei_df <-
+  run_qry_get_sims(table_name = table_name_cab_nd_mei, burn_in = 500)
+chr_lp_mei_df <-
+  run_qry_get_sims(table_name = table_name_chr_lp_mei, burn_in = 500)
+cab_lp_mei_df <-
+  run_qry_get_sims(table_name = table_name_cab_lp_mei, burn_in = 500)
+
+# CABEZON
+# use species specific vB params to create a weight at age data.frame that can be used to convert abundance at age to biomass at age
+species_name_cab <- cab_nd_mei_nice[[2]]
+cab_waa_g <- sim_species_parms[[species_name_cab]][["biom_const"]] * sim_species_derived_vars[[species_name_cab]][["length_at_age"]] ^
+                    sim_species_parms[[species_name_cab]][["biom_exp"]]
+
+cab_waa_g_df <- data.frame(age = 1: sim_species_parms[[species_name_cab]]$A_max,
+                           waa_g = cab_waa_g)
+
+# use functions to create useful data structures
+# FLEP to F reference tables by species
+spec_fleps_2_fs_cab <-
+  get_fs_from_fleps(species = species_name,
+                    flep_inds = species_flep_fished_ind,
+                    f_vals =  fishing_mortality_values)
+
+# CHINA ROCKFISH
+# use species specific vB params to create a weight at age data.frame that can be used to convert abundance at age to biomass at age
+species_name_chr <- chr_nd_mei_nice[[2]]
+chr_waa_g <- sim_species_parms[[species_name_chr]][["biom_const"]] * sim_species_derived_vars[[species_name_chr]][["length_at_age"]] ^
+                    sim_species_parms[[species_name_chr]][["biom_exp"]]
+
+chr_waa_g_df <- data.frame(age = 1: sim_species_parms[[species_name_chr]]$A_max,
+                           waa_g = chr_waa_g)
+
+# use functions to create useful data structures
+# FLEP to F reference tables by species
+spec_fleps_2_fs_chr <-
+  get_fs_from_fleps(species = species_name_chr,
+                    flep_inds = species_flep_fished_ind,
+                    f_vals =  fishing_mortality_values)
+
+########### PIPELINING
+
+F_chr_nd_white_df_maxes_yield <- get_f_maxes_yield(input_df = chr_nd_white_df,
+                                         fleps_2_fs = spec_fleps_2_fs_chr)
+F_chr_nd_white_df_maxes_yield
+
+F_cab_nd_white_df_maxes_yield <- get_f_maxes_yield(input_df = cab_nd_white_df,
+                                         fleps_2_fs = spec_fleps_2_fs_cab)
+F_cab_nd_white_df_maxes_yield
+
+F_chr_lp_white_df_maxes_yield <- get_f_maxes_yield(input_df = chr_lp_white_df,
+                                         fleps_2_fs = spec_fleps_2_fs_chr)
+F_chr_lp_white_df_maxes_yield
+
+F_cab_lp_white_df_maxes_yield <- get_f_maxes_yield(input_df = cab_lp_white_df,
+                                         fleps_2_fs = spec_fleps_2_fs_cab)
+F_cab_lp_white_df_maxes_yield
+
+F_chr_nd_mei_df_maxes_yield <- get_f_maxes_yield(input_df = chr_nd_mei_df, 
+                                                 fleps_2_fs = spec_fleps_2_fs_chr)
+F_chr_nd_mei_df_maxes_yield
+
+F_cab_nd_mei_df_maxes_yield <- get_f_maxes_yield(input_df = cab_nd_mei_df, 
+                                                 fleps_2_fs = spec_fleps_2_fs_cab)
+F_cab_nd_mei_df_maxes_yield
+
+F_chr_lp_mei_df_maxes_yield <- get_f_maxes_yield(input_df = chr_lp_mei_df, 
+                                                 fleps_2_fs = spec_fleps_2_fs_chr)
+F_chr_lp_mei_df_maxes_yield
+
+F_cab_lp_mei_df_maxes_yield <- get_f_maxes_yield(input_df = cab_lp_mei_df, 
+                                                 fleps_2_fs = spec_fleps_2_fs_cab)
+F_cab_lp_mei_df_maxes_yield
+
+##----##
+# No dispersal
+# white
+chr_nd_white_out_fs <- df_add_fs_out (input_df = chr_nd_white_df,
+                         spec_fleps_2_fs = spec_fleps_2_fs_chr,
+                         F_maxes_yield = F_chr_nd_white_df_maxes_yield, 
+                         waa_g_df = chr_waa_g_df)
+chr_nd_white_out_fs[1:6,]
+
+cab_nd_white_out_fs <- df_add_fs_out (input_df = cab_nd_white_df,
+                         spec_fleps_2_fs = spec_fleps_2_fs_cab,
+                         F_maxes_yield = F_cab_nd_white_df_maxes_yield, 
+                         waa_g_df = cab_waa_g_df)
+cab_nd_white_out_fs[1:6,]
+# enso
+chr_nd_mei_out_fs <- df_add_fs_out (input_df = chr_nd_mei_df ,
+                         spec_fleps_2_fs = spec_fleps_2_fs_chr,
+                         F_maxes_yield = F_chr_nd_mei_df_maxes_yield, 
+                         waa_g_df = chr_waa_g_df)
+chr_nd_mei_out_fs[1:6,]
+
+cab_nd_mei_out_fs <- df_add_fs_out (input_df = cab_nd_mei_df,
+                         spec_fleps_2_fs = spec_fleps_2_fs_cab,
+                         F_maxes_yield = F_cab_nd_mei_df_maxes_yield, 
+                         waa_g_df = cab_waa_g_df)
+cab_nd_mei_out_fs[1:6,]
+
+# Larval pool
+# white
+chr_lp_white_out_fs <- df_add_fs_out (input_df = chr_lp_white_df,
+                         spec_fleps_2_fs = spec_fleps_2_fs_chr,
+                         F_maxes_yield = F_chr_lp_white_df_maxes_yield, 
+                         waa_g_df = chr_waa_g_df)
+chr_lp_white_out_fs[1:6,]
+
+cab_lp_white_out_fs <- df_add_fs_out (input_df = cab_lp_white_df,
+                         spec_fleps_2_fs = spec_fleps_2_fs_cab,
+                         F_maxes_yield = F_cab_lp_white_df_maxes_yield, 
+                         waa_g_df = cab_waa_g_df)
+cab_lp_white_out_fs[1:6,]
+# enso
+chr_lp_mei_out_fs <- df_add_fs_out (input_df = chr_lp_mei_df ,
+                         spec_fleps_2_fs = spec_fleps_2_fs_chr,
+                         F_maxes_yield = F_chr_lp_mei_df_maxes_yield, 
+                         waa_g_df = chr_waa_g_df)
+chr_lp_mei_out_fs[1:6,]
+
+cab_lp_mei_out_fs <- df_add_fs_out (input_df = cab_lp_mei_df,
+                         spec_fleps_2_fs = spec_fleps_2_fs_cab,
+                         F_maxes_yield = F_cab_lp_mei_df_maxes_yield, 
+                         waa_g_df = cab_waa_g_df)
+cab_lp_mei_out_fs[1:6,]
+
+##----##
+
+# White
+# No dispersal
+chr_nd_white_med_yield <- get_median_yield(input_df = chr_nd_white_out_fs) 
+chr_nd_white_med_yield
+cab_nd_white_med_yield <- get_median_yield(input_df = cab_nd_white_out_fs) 
+cab_nd_white_med_yield
+# larval pool dispersal 
+chr_lp_white_med_yield <- get_median_yield(input_df = chr_lp_white_out_fs) 
+chr_lp_white_med_yield
+cab_lp_white_med_yield <- get_median_yield(input_df = cab_lp_white_out_fs) 
+cab_lp_white_med_yield
+
+# ENSO
+# No dispersal
+chr_nd_mei_med_yield <- get_median_yield(input_df = chr_nd_mei_out_fs) 
+chr_nd_mei_med_yield
+cab_nd_mei_med_yield <- get_median_yield(input_df = cab_nd_mei_out_fs) 
+cab_nd_mei_med_yield
+# larval pool dispersal
+chr_lp_mei_med_yield <- get_median_yield(input_df = chr_lp_mei_out_fs) 
+chr_lp_mei_med_yield
+cab_lp_mei_med_yield <- get_median_yield(input_df = cab_lp_mei_out_fs) 
+cab_lp_mei_med_yield
+
+##----##
+
+med_biomass <- get_median_biomass(input_df = out_fs, 
+                                  age_mat = sim_species_parms$`Blue rockfish`$A_mat)
+
+# White
+# No dispersal
+chr_nd_white_med_biomass <- get_median_biomass(input_df = chr_nd_white_out_fs, 
+                                  age_mat = sim_species_parms$`China rockfish`$A_mat) 
+chr_nd_white_med_biomass
+cab_nd_white_med_biomass <- get_median_biomass(input_df = cab_nd_white_out_fs, 
+                                  age_mat = sim_species_parms$`Cabezon`$A_mat) 
+cab_nd_white_med_biomass
+# larval pool dispersal 
+chr_lp_white_med_biomass <- get_median_biomass(input_df = chr_lp_white_out_fs, 
+                                  age_mat = sim_species_parms$`China rockfish`$A_mat) 
+chr_lp_white_med_biomass
+cab_lp_white_med_biomass <- get_median_biomass(input_df = cab_lp_white_out_fs, 
+                                  age_mat = sim_species_parms$`Cabezon`$A_mat) 
+cab_lp_white_med_biomass
+
+# ENSO
+# No dispersal
+chr_nd_mei_med_biomass <- get_median_biomass(input_df = chr_nd_mei_out_fs, 
+                                  age_mat = sim_species_parms$`China rockfish`$A_mat) 
+chr_nd_mei_med_biomass
+cab_nd_mei_med_biomass <- get_median_biomass(input_df = cab_nd_mei_out_fs, 
+                                  age_mat = sim_species_parms$`Cabezon`$A_mat) 
+cab_nd_mei_med_biomass
+# larval pool dispersal
+chr_lp_mei_med_biomass <- get_median_biomass(input_df = chr_lp_mei_out_fs, 
+                                  age_mat = sim_species_parms$`China rockfish`$A_mat) 
+chr_lp_mei_med_biomass
+cab_lp_mei_med_biomass <- get_median_biomass(input_df = cab_lp_mei_out_fs, 
+                                  age_mat = sim_species_parms$`Cabezon`$A_mat) 
+cab_lp_mei_med_biomass
+
+##----##
+
+chr_nd_white_out_yld_bm_sims_f_frac_yr <-
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = chr_nd_white_out_fs,
+                                     age_mat = sim_species_parms$`China rockfish`$A_mat)
+cab_nd_white_out_yld_bm_sims_f_frac_yr <-
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = cab_nd_white_out_fs, age_mat = sim_species_parms$`Cabezon`$A_mat)
+chr_lp_white_out_yld_bm_sims_f_frac_yr <-
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = chr_lp_white_out_fs,
+                                     age_mat = sim_species_parms$`China rockfish`$A_mat)
+cab_lp_white_out_yld_bm_sims_f_frac_yr <-
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = cab_lp_white_out_fs, age_mat = sim_species_parms$`Cabezon`$A_mat)
+chr_nd_mei_out_yld_bm_sims_f_frac_yr <-
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = chr_nd_mei_out_fs,
+                                     age_mat = sim_species_parms$`China rockfish`$A_mat)
+cab_nd_mei_out_yld_bm_sims_f_frac_yr <-
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = cab_nd_mei_out_fs, age_mat = sim_species_parms$`Cabezon`$A_mat)
+chr_lp_mei_out_yld_bm_sims_f_frac_yr <-
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = chr_lp_mei_out_fs,
+                                     age_mat = sim_species_parms$`China rockfish`$A_mat)
+cab_lp_mei_out_yld_bm_sims_f_frac_yr <-
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = cab_lp_mei_out_fs, age_mat = sim_species_parms$`Cabezon`$A_mat)
+
+##----##
+
+chr_nd_white_sum_stats_f_frac_df <-
+  summary_stats_by_f_frac(
+    out_sim_f_frac_yr = chr_nd_white_out_yld_bm_sims_f_frac_yr,
+    median_yield = chr_nd_white_med_yield,
+    median_biomass = chr_nd_white_med_biomass
+  )
+
+cab_nd_white_sum_stats_f_frac_df <-
+  summary_stats_by_f_frac(
+    out_sim_f_frac_yr = cab_nd_white_out_yld_bm_sims_f_frac_yr,
+    median_yield = cab_nd_white_med_yield,
+    median_biomass = cab_nd_white_med_biomass
+  )
+
+chr_lp_white_sum_stats_f_frac_df <-
+  summary_stats_by_f_frac(
+    out_sim_f_frac_yr = chr_lp_white_out_yld_bm_sims_f_frac_yr,
+    median_yield = chr_lp_white_med_yield,
+    median_biomass = chr_lp_white_med_biomass
+  )
+
+cab_lp_white_sum_stats_f_frac_df <-
+  summary_stats_by_f_frac(
+    out_sim_f_frac_yr = cab_lp_white_out_yld_bm_sims_f_frac_yr,
+    median_yield = cab_lp_white_med_yield,
+    median_biomass = cab_lp_white_med_biomass
+  )
+
+chr_nd_mei_sum_stats_f_frac_df <-
+  summary_stats_by_f_frac(
+    out_sim_f_frac_yr = chr_nd_mei_out_yld_bm_sims_f_frac_yr,
+    median_yield = chr_nd_mei_med_yield,
+    median_biomass =   chr_nd_mei_med_biomass
+  )
+
+cab_nd_mei_sum_stats_f_frac_df <-
+  summary_stats_by_f_frac(
+    out_sim_f_frac_yr = cab_nd_mei_out_yld_bm_sims_f_frac_yr,
+    median_yield = cab_nd_mei_med_yield,
+    median_biomass =   cab_nd_mei_med_biomass
+  )
+
+chr_lp_mei_sum_stats_f_frac_df <-
+  summary_stats_by_f_frac(
+    out_sim_f_frac_yr = chr_lp_mei_out_yld_bm_sims_f_frac_yr,
+    median_yield = chr_lp_mei_med_yield,
+    median_biomass =   chr_lp_mei_med_biomass
+  )
+
+cab_lp_mei_sum_stats_f_frac_df <-
+  summary_stats_by_f_frac(
+    out_sim_f_frac_yr = cab_lp_mei_out_yld_bm_sims_f_frac_yr,
+    median_yield = cab_lp_mei_med_yield,
+    median_biomass =   cab_lp_mei_med_biomass
+  )
+
+```
+
+### Supp Fig 1
+
+Biomass and yield contours for Blue rockfish
+
+-   white noise
+
+-   no dispersal and larval pool
+
+```{r}
+#| label: supp_fig_1
+
+# Species: Blue rockfish
+# Dispersal: No Dispersal
+# Environmental noise: White
+
+con <- DBI::dbConnect(duckdb::duckdb(),
+                        dbdir = "data/sim_out.duckdb",
+                        read_only = FALSE)
+
+# use species specific vB params to create a weight at age data.frame that can be used to convert abundance at age to biomass at age
+species_name <- brf_mei_nd_nice[[2]]
+brf_waa_g <- sim_species_parms[[species_name]][["biom_const"]] * sim_species_derived_vars[[species_name]][["length_at_age"]] ^
+                    sim_species_parms[[species_name]][["biom_exp"]]
+
+brf_waa_g_df <- data.frame(age = 1: sim_species_parms[[species_name]]$A_max,
+                           waa_g = brf_waa_g)
+
+# use functions to create useful data structures
+# FLEP to F reference tables by species
+spec_fleps_2_fs <-
+  get_fs_from_fleps(species = species_name,
+                    flep_inds = species_flep_fished_ind,
+                    f_vals =  fishing_mortality_values)
+
+## Qry 
+qry <- paste0("SELECT  sim_num, reserve_frac, flep_ratio, year, age, 
+              sum(number) as abundance,
+              sum(yield) as yield,
+              FROM '", table_name_nd_white, 
+              "' WHERE sim_num IN (", toString(sims_2_use), ") AND year > 500 
+              GROUP BY sim_num, reserve_frac, flep_ratio, year, age
+              ORDER BY sim_num, reserve_frac, flep_ratio, year, age
+              ")
+
+sim_res_out <- dbGetQuery(conn = con, qry)
+
+#######
+
+########### PIPELINING
+F_brf_maxes_yield <- get_f_maxes_yield(input_df = sim_res_out,
+                                         fleps_2_fs = spec_fleps_2_fs)
+F_brf_maxes_yield
+
+out_fs <- df_add_fs_out (input_df = sim_res_out,
+                         spec_fleps_2_fs = spec_fleps_2_fs,
+                         F_maxes_yield = F_brf_maxes_yield, waa_g_df = brf_waa_g_df)
+out_fs
+
+med_yield <- get_median_yield(input_df = out_fs) 
+med_yield
+
+med_biomass <- get_median_biomass(input_df = out_fs, age_mat = sim_species_parms$`Blue rockfish`$A_mat)
+med_biomass
+
+out_yld_bm_sims_f_frac_yr <-
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs,
+                                     age_mat = sim_species_parms$`Blue rockfish`$A_mat)#, sims_num_2_use = sims_2_use
+
+# out_yld_bm_sims_f_frac_yr
+# pipeline works to here
+
+sum_stats_f_frac_df <-
+  summary_stats_by_f_frac(
+    out_sim_f_frac_yr = out_yld_bm_sims_f_frac_yr,
+    median_yield = med_yield,
+    median_biomass = med_biomass
+  )
+sum_stats_f_frac_df
+
+## Plotting
+
+p1 <- sum_stats_f_frac_df[[2]] %>%
+  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
+  ggplot(.,
+       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_biomass_thresh)) +
+  metR::geom_contour_fill(bins = 12) +
+  ggtitle(paste0(
+        brf_white_nd_nice[[2]],
+        " ",
+        brf_white_nd_nice[[1]],
+        " ",
+        brf_white_nd_nice[[3]],
+        ":\nTime below mean median biomass "
+      )) +
+      xlab("Fraction of coastline in reserves") +
+      ylab("Harvest Rate (F/Fmsy)") +
+      scale_fill_viridis_c(option = "D", direction = -1) +
+      geom_segment(aes(
+        x = 0,
+        xend = max_reserve_frac,
+        y = 1,
+        yend = 1
+      ), colour = "black",
+      linetype = 2) +
+      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
+      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
+      theme_bw()
+
+p2 <- sum_stats_f_frac_df[[2]] %>%
+  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
+  ggplot(.,
+       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_yield_thresh)) +
+  metR::geom_contour_fill(bins = 12) + 
+  ggtitle(paste0(
+        brf_white_nd_nice[[2]],
+        " ",
+        brf_white_nd_nice[[1]],
+        " ",
+        brf_white_nd_nice[[3]],
+        ":\nTime below median max yield"
+      )) +
+      xlab("Fraction of coastline in reserves") +
+      ylab("Harvest Rate (F/Fmsy)") +
+      scale_fill_viridis_c(option = "D", direction = -1) +
+      geom_segment(aes(
+        x = 0,
+        xend = max_reserve_frac,
+        y = 1,
+        yend = 1
+      ), colour = "black",
+      linetype = 2) +
+      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
+      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
+      theme_bw()
+
+# Species: Blue rockfish
+# Dispersal: Larval Pool Dispersal
+# Environmental noise: White
+# use species specific vB params to create a weight at age data.frame that can be used to convert abundance at age to biomass at age
+species_name <- brf_mei_lp_nice[[2]]
+brf_waa_g <- sim_species_parms[[species_name]][["biom_const"]] * sim_species_derived_vars[[species_name]][["length_at_age"]] ^
+                    sim_species_parms[[species_name]][["biom_exp"]]
+
+brf_waa_g_df <- data.frame(age = 1: sim_species_parms[[species_name]]$A_max,
+                           waa_g = brf_waa_g)
+
+# use functions to create useful data structures
+# FLEP to F reference tables by species
+spec_fleps_2_fs <-
+  get_fs_from_fleps(species = species_name,
+                    flep_inds = species_flep_fished_ind,
+                    f_vals =  fishing_mortality_values)
+
+## Qry 
+qry <- paste0("SELECT  sim_num, reserve_frac, flep_ratio, year, age, 
+              sum(number) as abundance,
+              sum(yield) as yield,
+              FROM '", table_name_lp_white, 
+              "' WHERE sim_num IN (", toString(sims_2_use), ") AND year > 500 
+              GROUP BY sim_num, reserve_frac, flep_ratio, year, age
+              ORDER BY sim_num, reserve_frac, flep_ratio, year, age
+              ")
+
+sim_res_out <- dbGetQuery(conn = con, qry)
+
+#######
+
+########### PIPELINING
+F_brf_maxes_yield <- get_f_maxes_yield(input_df = sim_res_out,
+                                         fleps_2_fs = spec_fleps_2_fs)
+F_brf_maxes_yield
+
+out_fs <- df_add_fs_out (input_df = sim_res_out,
+                         spec_fleps_2_fs = spec_fleps_2_fs,
+                         F_maxes_yield = F_brf_maxes_yield, waa_g_df = brf_waa_g_df)
+out_fs
+
+med_yield <- get_median_yield(input_df = out_fs) 
+med_yield
+
+med_biomass <- get_median_biomass(input_df = out_fs,
+                                  age_mat = sim_species_parms$`Blue rockfish`$A_mat)
+med_biomass
+
+out_yld_bm_sims_f_frac_yr <-
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs, 
+                                     age_mat = sim_species_parms$`Blue rockfish`$A_mat)
+
+# pipeline works to here
+
+sum_stats_f_frac_df <-
+  summary_stats_by_f_frac(
+    out_sim_f_frac_yr = out_yld_bm_sims_f_frac_yr,
+    median_yield = med_yield,
+    median_biomass = med_biomass
+  )
+sum_stats_f_frac_df
+
+## Plotting
+
+p3 <- sum_stats_f_frac_df[[2]] %>%
+  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
+  ggplot(.,
+       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_biomass_thresh)) +
+  metR::geom_contour_fill(bins = 12) +
+  ggtitle(paste0(
+        brf_white_lp_nice[[2]],
+        " ",
+        brf_white_lp_nice[[1]],
+        " ",
+        brf_white_lp_nice[[3]],
+        ":\nTime below mean median biomass "
+      )) +
+      xlab("Fraction of coastline in reserves") +
+      ylab("Harvest Rate (F/Fmsy)") +
+      scale_fill_viridis_c(option = "D", direction = -1) +
+      geom_segment(aes(
+        x = 0,
+        xend = max_reserve_frac,
+        y = 1,
+        yend = 1
+      ), colour = "black",
+      linetype = 2) +
+      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
+      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
+      theme_bw()
+
+p4 <- sum_stats_f_frac_df[[2]] %>%
+  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
+  ggplot(.,
+       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_yield_thresh)) +
+  metR::geom_contour_fill(bins = 12) + 
+  ggtitle(paste0(
+        brf_white_lp_nice[[2]],
+        " ",
+        brf_white_lp_nice[[1]],
+        " ",
+        brf_white_lp_nice[[3]],
+        ":\nTime below median max yield"
+      )) +
+      xlab("Fraction of coastline in reserves") +
+      ylab("Harvest Rate (F/Fmsy)") +
+      scale_fill_viridis_c(option = "D", direction = -1) +
+      geom_segment(aes(
+        x = 0,
+        xend = max_reserve_frac,
+        y = 1,
+        yend = 1
+      ), colour = "black",
+      linetype = 2) +
+      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
+      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
+      theme_bw()
+
+# print(p1)
+# print(p2)
+# print(p3)
+# print(p4)
+
+p_s1 <- plot_grid(p1, p2, p3, p4, labels = letters[1:4], label_size = 9, byrow = FALSE)
+
+print(p_s1)
+
+ggsave(filename = "output/tmp_figs/sup_fig1-brf-biomass-yield-white-nd-lp.png", 
+       plot = p_s1, 
+       width = 12,
+       height = 8)
+ggsave(filename = "output/tmp_figs/sup_fig1-brf-biomass-yield-white-nd-lp.svg", 
+       plot = p_s1, 
+       width = 12,
+       height = 8)
+
+DBI::dbDisconnect(conn = con, shutdown=TRUE)
+
+```
+
+### Supp Fig 2
+
+China rockfish and Cabezon -- Biomass and Yield contour plots
+
+-   ENSO noise
+
+-   No dispersal
+
+```{r}
+#| label: supp_fig_2
+
+## Contour plot for each species
+### China rockfish
+# Biomass
+
+p1 <- chr_nd_mei_sum_stats_f_frac_df[[2]] %>%
+  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
+  ggplot(.,
+       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_biomass_thresh)) +
+  metR::geom_contour_fill(bins = 12) +
+  ggtitle(paste0(
+        chr_nd_mei_nice[[2]],
+        " ",
+        chr_nd_mei_nice[[1]],
+        " ",
+        chr_nd_mei_nice[[3]],
+        ":\nTime below mean median biomass "
+      )) +
+      xlab("Fraction of coastline in reserves") +
+      ylab("Harvest Rate (F/Fmsy)") +
+      scale_fill_viridis_c(option = "D", direction = -1) +
+      geom_segment(aes(
+        x = 0,
+        xend = max_reserve_frac,
+        y = 1,
+        yend = 1
+      ), colour = "black",
+      linetype = 2) +
+      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
+      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
+      theme_bw()
+
+# Yield
+p2 <- chr_nd_mei_sum_stats_f_frac_df[[2]] %>%
+  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
+  ggplot(.,
+       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_yield_thresh)) +
+  metR::geom_contour_fill(bins = 12) + 
+  ggtitle(paste0(
+        chr_nd_mei_nice[[2]],
+        " ",
+        chr_nd_mei_nice[[1]],
+        " ",
+        chr_nd_mei_nice[[3]],
+        ":\nTime below median max yield"
+      )) +
+      xlab("Fraction of coastline in reserves") +
+      ylab("Harvest Rate (F/Fmsy)") +
+      scale_fill_viridis_c(option = "D", direction = -1) +
+      geom_segment(aes(
+        x = 0,
+        xend = max_reserve_frac,
+        y = 1,
+        yend = 1
+      ), colour = "black",
+      linetype = 2) +
+      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
+      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
+      theme_bw()
+
+print(p1)
+print(p2)
+
+### Cabezon
+# Biomass
+p3 <- cab_nd_mei_sum_stats_f_frac_df[[2]] %>%
+  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
+  ggplot(.,
+       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_biomass_thresh)) +
+  metR::geom_contour_fill(bins = 12) +
+  ggtitle(paste0(
+        cab_nd_mei_nice[[2]],
+        " ",
+        cab_nd_mei_nice[[1]],
+        " ",
+        cab_nd_mei_nice[[3]],
+        ":\nTime below mean median biomass "
+      )) +
+      xlab("Fraction of coastline in reserves") +
+      ylab("Harvest Rate (F/Fmsy)") +
+      scale_fill_viridis_c(option = "D", direction = -1) +
+      geom_segment(aes(
+        x = 0,
+        xend = max_reserve_frac,
+        y = 1,
+        yend = 1
+      ), colour = "black",
+      linetype = 2) +
+      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
+      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
+      theme_bw()
+
+# Yield
+p4 <- cab_nd_mei_sum_stats_f_frac_df[[2]] %>%
+  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
+  ggplot(.,
+       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_yield_thresh)) +
+  metR::geom_contour_fill(bins = 12) + 
+  ggtitle(paste0(
+        cab_nd_mei_nice[[2]],
+        " ",
+        cab_nd_mei_nice[[1]],
+        " ",
+        cab_nd_mei_nice[[3]],
+        ":\nTime below median max yield"
+      )) +
+      xlab("Fraction of coastline in reserves") +
+      ylab("Harvest Rate (F/Fmsy)") +
+      scale_fill_viridis_c(option = "D", direction = -1) +
+      geom_segment(aes(
+        x = 0,
+        xend = max_reserve_frac,
+        y = 1,
+        yend = 1
+      ), colour = "black",
+      linetype = 2) +
+      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
+      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
+      theme_bw()
+
+p_s2 <- plot_grid(p1, p2, p3, p4, labels = letters[1:4], label_size = 12, byrow = FALSE)
+
+print(p_s2)
+ggsave(filename = "output/tmp_figs/sup-fig2-cab-chr-nodisp-mei-yld-biom.png", 
+       plot = p_s2, 
+       width = 12,
+       height = 8)
+ggsave(filename = "output/tmp_figs/sup-fig2-cab-chr-nodisp-mei-yld-biom.svg", 
+       plot = p_s2, 
+       width = 12,
+       height = 8)
+
+```
+
+### Supp Fig 3
+
+China rockfish and Cabezon -- Biomass and Yield contour plots
+
+-   ENSO noise
+
+-   larval pool dispersal
+
+```{r}
+#| label: supp_fig_3
+
+## Contour plot for each species
+### China rockfish
+# Biomass
+
+p1 <- chr_lp_mei_sum_stats_f_frac_df[[2]] %>%
+  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
+  ggplot(.,
+       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_biomass_thresh)) +
+  metR::geom_contour_fill(bins = 12) +
+  ggtitle(paste0(
+        chr_lp_mei_nice[[2]],
+        " ",
+        chr_lp_mei_nice[[1]],
+        " ",
+        chr_lp_mei_nice[[3]],
+        ":\nTime below mean median biomass "
+      )) +
+      xlab("Fraction of coastline in reserves") +
+      ylab("Harvest Rate (F/Fmsy)") +
+      scale_fill_viridis_c(option = "D", direction = -1) +
+      geom_segment(aes(
+        x = 0,
+        xend = max_reserve_frac,
+        y = 1,
+        yend = 1
+      ), colour = "black",
+      linetype = 2) +
+      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
+      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
+      theme_bw()
+
+# Yield
+p2 <- chr_lp_mei_sum_stats_f_frac_df[[2]] %>%
+  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
+  ggplot(.,
+       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_yield_thresh)) +
+  metR::geom_contour_fill(bins = 12) + 
+  ggtitle(paste0(
+        chr_lp_mei_nice[[2]],
+        " ",
+        chr_lp_mei_nice[[1]],
+        " ",
+        chr_lp_mei_nice[[3]],
+        ":\nTime below median max yield"
+      )) +
+      xlab("Fraction of coastline in reserves") +
+      ylab("Harvest Rate (F/Fmsy)") +
+      scale_fill_viridis_c(option = "D", direction = -1) +
+      geom_segment(aes(
+        x = 0,
+        xend = max_reserve_frac,
+        y = 1,
+        yend = 1
+      ), colour = "black",
+      linetype = 2) +
+      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
+      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
+      theme_bw()
+
+print(p1)
+print(p2)
+
+### Cabezon
+# Biomass
+p3 <- cab_lp_mei_sum_stats_f_frac_df[[2]] %>%
+  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
+  ggplot(.,
+       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_biomass_thresh)) +
+  metR::geom_contour_fill(bins = 12) +
+  ggtitle(paste0(
+        cab_lp_mei_nice[[2]],
+        " ",
+        cab_lp_mei_nice[[1]],
+        " ",
+        cab_lp_mei_nice[[3]],
+        ":\nTime below mean median biomass "
+      )) +
+      xlab("Fraction of coastline in reserves") +
+      ylab("Harvest Rate (F/Fmsy)") +
+      scale_fill_viridis_c(option = "D", direction = -1) +
+      geom_segment(aes(
+        x = 0,
+        xend = max_reserve_frac,
+        y = 1,
+        yend = 1
+      ), colour = "black",
+      linetype = 2) +
+      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
+      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
+      theme_bw()
+
+# Yield
+p4 <- cab_lp_mei_sum_stats_f_frac_df[[2]] %>%
+  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
+  ggplot(.,
+       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_yield_thresh)) +
+  metR::geom_contour_fill(bins = 12) + 
+  ggtitle(paste0(
+        cab_lp_mei_nice[[2]],
+        " ",
+        cab_lp_mei_nice[[1]],
+        " ",
+        cab_lp_mei_nice[[3]],
+        ":\nTime below median max yield"
+      )) +
+      xlab("Fraction of coastline in reserves") +
+      ylab("Harvest Rate (F/Fmsy)") +
+      scale_fill_viridis_c(option = "D", direction = -1) +
+      geom_segment(aes(
+        x = 0,
+        xend = max_reserve_frac,
+        y = 1,
+        yend = 1
+      ), colour = "black",
+      linetype = 2) +
+      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
+      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
+      theme_bw()
+
+p_s3 <- plot_grid(p1, p2, p3, p4, labels = letters[1:4], label_size = 12, byrow = FALSE)
+
+print(p_s3)
+ggsave(filename = "output/tmp_figs/sup-fig3-cab-chr-lp-disp-mei-yld-biom.png", 
+       plot = p_s3, 
+       width = 12,
+       height = 8)
+ggsave(filename = "output/tmp_figs/sup-fig3-cab-chr-lp-disp-mei-yld-biom.svg", 
+       plot = p_s3, 
+       width = 12,
+       height = 8)
+
+```
+
+### Supp Fig 4
+
+Yield contours for Cabezon and China rockfish
+
+-   white noise (or do we want ENSO?) --- white vs ENSO
+
+-   Larval pool dispersal
+
+```{r}
+#| label: supp_fig_4
+#| 
+```

### 2023-12-18 R/fig_functions (dpkilduff@gmail.com).R

@@ -1,0 +1,221 @@
+# Functions for table meta data
+
+get_current_exp <- function(table_name) {
+  # returns species, dispersal, noise params to extract from duckdb table names 
+  valid_dispersal <- c("larval_pool", "no_dispersal")
+  valid_species <-
+    c("blue_rockfish", "cabezon", "china_rockfish", "pacific_cod", "kelp_bass")
+  valid_noise <- c("mei_135_75", "white_135_75")
+  
+  current_dispersal <-
+    valid_dispersal[stringr::str_detect(table_name, valid_dispersal)]
+  current_species <-
+    valid_species[stringr::str_detect(table_name, valid_species)]
+  current_noise <-
+    valid_noise[stringr::str_detect(table_name, valid_noise)]
+  return(list(current_dispersal, current_species, current_noise))
+}
+
+get_nice_exp <- function(table_name) {
+  # returns "pretty" version of species, dispersal, noise params for plotting
+  valid_dispersal <- c("larval_pool", "no_dispersal")
+  valid_species <-
+    c("blue_rockfish", "cabezon", "china_rockfish", "pacific_cod", "kelp_bass")
+  valid_noise <- c("mei_135_75", "white_135_75")
+  
+  pretty_dispersal <- c("Larval pool", "No dispersal")
+  pretty_species <- c("Blue rockfish", "Cabezon", "China rockfish", "Pacific cod", "Kelp bass")
+  pretty_noise <- c("ENSO", "White")
+  
+  nice_dispersal <-
+    pretty_dispersal[stringr::str_detect(table_name, valid_dispersal)]
+  nice_species <-
+    pretty_species[stringr::str_detect(table_name, valid_species)]
+  nice_noise <-
+    pretty_noise[stringr::str_detect(table_name, valid_noise)]
+  
+  return(list(nice_dispersal, nice_species, nice_noise))
+}
+
+
+
+#' Get Fishing Mortality Levels that Maximize Yield
+#'
+#' For each FLEP ratio, find the fishing mortality level  
+#' that maximizes yield when there are no reserves.
+#'
+#' @param input_df dataframe with simulation results 
+#' @param fleps_2_fs dataframe matching FLEP ratios to F values
+#' 
+#' @return Vector of optimal F values for maximum yield for each FLEP ratio
+#'
+#' @examples
[…]

### 2023-12-18 R/fig_functions.R

@@ -1,0 +1,221 @@
+# Functions for table meta data
+
+get_current_exp <- function(table_name) {
+  # returns species, dispersal, noise params to extract from duckdb table names 
+  valid_dispersal <- c("larval_pool", "no_dispersal")
+  valid_species <-
+    c("blue_rockfish", "cabezon", "china_rockfish")
+  valid_noise <- c("mei_135_75", "white_135_75")
+  
+  current_dispersal <-
+    valid_dispersal[stringr::str_detect(table_name, valid_dispersal)]
+  current_species <-
+    valid_species[stringr::str_detect(table_name, valid_species)]
+  current_noise <-
+    valid_noise[stringr::str_detect(table_name, valid_noise)]
+  return(list(current_dispersal, current_species, current_noise))
+}
+
+get_nice_exp <- function(table_name) {
+  # returns "pretty" version of species, dispersal, noise params for plotting
+  valid_dispersal <- c("larval_pool", "no_dispersal")
+  valid_species <-
+    c("blue_rockfish", "cabezon", "china_rockfish", "pacific_cod", "kelp_bass")
+  valid_noise <- c("mei_135_75", "white_135_75")
+  
+  pretty_dispersal <- c("Larval pool", "No dispersal")
+  pretty_species <- c("Blue rockfish", "Cabezon", "China rockfish", "Pacific cod", "Kelp bass")
+  pretty_noise <- c("ENSO", "White")
+  
+  nice_dispersal <-
+    pretty_dispersal[stringr::str_detect(table_name, valid_dispersal)]
+  nice_species <-
+    pretty_species[stringr::str_detect(table_name, valid_species)]
+  nice_noise <-
+    pretty_noise[stringr::str_detect(table_name, valid_noise)]
+  
+  return(list(nice_dispersal, nice_species, nice_noise))
+}
+
+
+
+#' Get Fishing Mortality Levels that Maximize Yield
+#'
+#' For each FLEP ratio, find the fishing mortality level  
+#' that maximizes yield when there are no reserves.
+#'
+#' @param input_df dataframe with simulation results 
+#' @param fleps_2_fs dataframe matching FLEP ratios to F values
+#' 
+#' @return Vector of optimal F values for maximum yield for each FLEP ratio
+#'
+#' @examples
+#' input_df <- data.frame(sim_num = rep(1, 30), 
[…]

### 2023-12-18 R/functions.R

@@ -24,7 +24,7 @@
 #'
 #' sp_parms <- load_species_parms() # add how to use in targets workflow
 #'
-
+#### USED
 load_species_parms <-
   function(fp = file.path("data", "species_parameters.csv")) {
     spec_parms_fp <- fp
@@ -107,7 +107,37 @@ get_species_parms <- function(df_parms, species_name) {
   )
 }
 
-#' add documentation
+#' Return a list life history parameters for multiple species
+#'
+#' Given a dataframe of fish life history parameters and a vector of species names,
+#' this function retrieves the parameters for each species using the 
+#' get_species_parms() function.
+#'
+#' @param parm_df Dataframe of model parameters by species
+#' @param sp_names Character vector of species names
+#' 
+#' @return Named list of parameter lists, one list per species
+#' 
+#' @examples 
+#' params_df <- data.frame(
+#'   species = c("Cod", "Rockfish"),
+#'   M = c(0.2, 0.1),
+#'   L_inf = c(60, 40), 
+#'   k = c(0.5, 0.7),
+#'   t_0 = c(0.05, -0.05),
+#'   A_max  c(15, 27),
+#'   A_mat = c(3, 5),
+#'   A_fish = c(4, 5),
+#'   biom_const = c(1.1, 0.9),
+#'   biom_exp = c(3.02, 3)
+#' )
+#'
+#' species <- c("Cod", "Rockfish")
+#'
+#' species_params <- list_species_parms(params_df, species)
+#'
+#' @export 
+#### USED 
 list_species_parms <- function(parm_df,
                                sp_names) {
   sim_species_parms <- sp_names %>%
@@ -117,38 +147,6 @@ list_species_parms <- function(parm_df,
   
   return(sim_species_parms)
 }
-
-# test_function <- function(sp_names,
-#                           df_parms) {
-#   sim_species_parms <- sp_names %>%
-#     purrr::set_names() %>%
-#     purrr::map(.,
-#                ~ get_species_parms(df_parms = parm_df, species_name =  .x))
-#
-#   sp_names <- species_names
-#   df_parms <- species_parms
-#   out <- vector(mode = "list", length = length(sp_names))
-#
-#   for (i in 1:length(sp_names)) {
-#     df_species <- df_parms %>%
-#       dplyr::filter(species == sp_names[i])
-#     sp_parms_list <- list(
-#       species = df_species$species,
-#       M = df_species$M,
-#       L_inf = df_species$L_inf,
[…]

### 2023-12-18 R/test_functions.R

@@ -8,7 +8,7 @@
 # number = NA_real_
 # yield = NA_real_
 
-
+#### USED
 run_sims_sm_write <- function(expmts,
                               spec_name,
                               alpha_bh,
@@ -78,7 +78,7 @@ run_sims_sm_write <- function(expmts,
                     sim_spec_pars[[j]][["biom_exp"]],
                   alpha = alpha_bh[[j]],
                   beta = beta_bh,
-                  noise_series = noise_dat
+                  noise_series = noise_dat[,m] ########
                 )
                 
                 out_Ns <-
@@ -131,15 +131,20 @@ run_sims_sm_write <- function(expmts,
               }
             }
             print("Before ddb write")
-            print(head(dt_ddb))
+            
+            tab_name <- paste0(expmts[i], "_", tolower(sub(
+              " ", "_", spec_name[j]
+            )), "_", k, "_", substring(as.character(recr_sd[l]), 3))
+            
+            print(tab_name)
+            
+            print(tail(dt_ddb))
             duckdb::dbWriteTable(con,
-                                 paste0(expmts[i], "_", tolower(sub(
-                                   " ", "_", spec_name[j]
-                                 )), "_", k, "_", substring(as.character(recr_sd[l]), 3)),
+                                 tab_name,
                                  dt_ddb,
                                  append = TRUE) # FALSE
             print("After ddb write")
-            print(head(dt_ddb))
+            print(tail(dt_ddb))
             rm(dt_ddb)
             
           }
@@ -153,116 +158,3 @@ run_sims_sm_write <- function(expmts,
   return(dt)
 }
 
-
-# run_sims_sm_write <- function(dt,
-#                      expmts,
-#                      spec_name,
-#                      alpha_bh,
-#                      beta_bh,
-#                      recr_sd,
-#                      fleps,
-#                      frac_reserves,
-#                      noise_vec,
-#                      noise_dat,
-#                      n_years,
-#                      num_sims,
-#                      num_patches,
-#                      les_mats,
-#                      conn_mats,
-#                      in_out_fracs,
-#                      sim_results,
-#                      sim_spec_dervars,
-#                      f_vals,
-#                      spec_flep_f_ind,
-#                      sim_spec_pars) {
-# 
-#   con <-
-#     dbConnect(duckdb::duckdb(),
-#               dbdir = "data/sim_out.duckdb",
[…]

### 2023-12-18 _targets.R

@@ -1,7 +1,3 @@
-# add unit/data tests (via testthat and assertr)
-# add version control?
-
-
 library(targets)
 library(tarchetypes)
 source(file.path("R", "functions.R"))
@@ -16,23 +12,18 @@ tar_option_set(
     "fst",
     "qs",
     "metR",
-    "isoband",
-    "signal",
-    "imager"
+    "isoband"
+    # "signal", # using fft(..., inverse = TRUE) instead of ifft(...)
+    # "imager" # used in old plotting function: plt_sdmn_yield_lp_diff_nd_gradvec_cont2
   )
 )
 
 
-# "Blue rockfish",
-# "Cabezon",
-# "Kelp bass",
-# "Pacific cod",
-# "China rockfish"
-
-
 r_seed <- 11
 tar_seed(default = r_seed)
+
 ## TODO: check for duck.db files and delete before running
+
 list(
   tar_target(exp_names_nd,
              "no_dispersal"),
@@ -77,31 +68,29 @@ list(
   # Simulation length burn_in and actual sim_len:
   tar_target(burn_in,
              500),
-  tar_target(sim_len,
-             512),
+  # tar_target(sim_len,
+  #            512),
   tar_target(sim_len_135,
              135),
-  tar_target(n_years,
-             burn_in + sim_len),
+  # tar_target(n_years,
+  #            burn_in + sim_len),
   tar_target(n_years_135,
              burn_in + sim_len_135),
-  tar_target(sim_yrs,
-             1:n_years),
+  # tar_target(sim_yrs,
+  #            1:n_years),
   tar_target(sim_yrs_135,
              1:n_years_135),
   # Run how many replicate simulations?
   tar_target(sim_nums,
-             25),
+             5), ### --> 10
   tar_target(sd_recruitment,
              0.75),
   # Fraction of lifetime egg production (FLEP)
   # Lower FLEPs correspond to populations that have experienced higher exploitation
   # 0.3 is close to population collapse, so 0.4 is close enough to get cohort resonance
   tar_target(flep_ratios,
-             # c(seq(0.2, 0.8, by = 0.2), 0.998)),
              c(seq(0.2, 0.975, by = 0.025), 0.998)),
   tar_target(reserve_fracs,
-             # seq(0, 0.8, by = 0.2)),
              seq(0, 0.8, by = 0.05)),
[…]

### 2023-12-21 ms_figures_supp_figs.qmd
prep before push to gh repo

@@
 source("R/functions.R")
-source("R/fig_functions.R")
+# source("R/fig_functions.R")
 
@@
 
-# A total of 25 (2023/11/08) simulations were run for each paramter set
+# A total of 5 (2023/12/20) simulations were run for each paramter set
 # This set allows us to determine the number of simulations to use 
@@
 
-#######
-
-########### PIPELINING
 F_brf_maxes_yield <- get_f_maxes_yield(input_df = sim_res_out,
                                          fleps_2_fs = spec_fleps_2_fs)
-F_brf_maxes_yield
-
-out_fs <- df_add_fs_out (input_df = sim_res_out,
+# F_brf_maxes_yield
+
+out_fs <- df_add_fs_out(
+  input_df = sim_res_out,
   spec_fleps_2_fs = spec_fleps_2_fs,
-                         F_maxes_yield = F_brf_maxes_yield, waa_g_df = brf_waa_g_df)
-out_fs
+  F_maxes_yield = F_brf_maxes_yield,
+  waa_g_df = brf_waa_g_df
+)
+# out_fs
 
 med_yield <- get_median_yield(input_df = out_fs) 
-med_yield
-
-med_biomass <- get_median_biomass(input_df = out_fs, age_mat = sim_species_parms$`Blue rockfish`$A_mat)
-med_biomass
+# med_yield
+
+med_biomass <- get_median_biomass(input_df = out_fs)
+# med_biomass
 
 out_yld_bm_sims_f_frac_yr <-
-  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs,
-                                     age_mat = sim_species_parms$`Blue rockfish`$A_mat)#, sims_num_2_use = sims_2_use
-
-# out_yld_bm_sims_f_frac_yr
-# pipeline works to here
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs)
 
@@
   )
-sum_stats_f_frac_df
+# sum_stats_f_frac_df
 
@@
 
-fig3 <- plot_grid(p1, p2, labels = letters[1:2], label_size = 9, byrow = FALSE)
+fig3 <-
+  plot_grid(
+    p1,
+    p2,
+    labels = letters[1:2],
+    label_size = 9,
+    byrow = TRUE,
+    nrow = 2,
+    ncol = 1
+  )
 
@@
        plot = fig3, 
-       height = 8, width = 5)
+       height = 10,
+       width = 8)
 ggsave(filename = "output/tmp_figs/fig3-brf-nd-mei-biomass-yield.svg", 
        plot = fig3, 
-       height = 8, width = 5)
-
-# ggsave(filename = "output/tmp_figs/fig3-yield.png", plot = p1)
-# ggsave(filename = "output/tmp_figs/fig3-biomass.png", plot = p2)
-# 
-# ggsave(filename = "output/tmp_figs/fig3-yield.svg", plot = p1)
-# ggsave(filename = "output/tmp_figs/fig3-biomass.svg", plot = p2)
-
-```
-
-```{r}
-out_fs %>%
-  group_by(sim_num, reserve_frac, f_fmsy, year) %>%
-  summarize(
-    ann_yield = sum(yield, na.rm = TRUE),
-    ann_biomass = sum(biomass_at_age, na.rm = TRUE)
-  ) %>%
-  filter(near(f_fmsy, 1) | near(f_fmsy, 0.52) | near(f_fmsy, 2.09),  near(as.numeric(reserve_frac), 0)) %>%
-  ggplot(., aes(x = year, y = ann_biomass)) +
-  geom_line() +
-  facet_grid(f_fmsy ~ sim_num)
-
-out_fs %>%
-  group_by(sim_num, reserve_frac, f_fmsy, year) %>%
-  summarize(
-    ann_yield = sum(yield, na.rm = TRUE),
-    ann_biomass = sum(biomass_at_age, na.rm = TRUE)
-  ) %>%
- filter(near(f_fmsy, 1) | near(f_fmsy, 0.52) | near(f_fmsy, 2.09),  near(as.numeric(reserve_frac), 0)) %>%
-  ungroup() %>%
-  ggplot(., aes(x = year, y = ann_yield)) +
-  geom_line() +
-  facet_grid(f_fmsy ~ sim_num)
-
-out_fs %>%
-    group_by(sim_num, reserve_frac, f_fmsy, year) %>%
-    summarize(
-        ann_yield = sum(yield, na.rm = TRUE),
-        ann_biomass = sum(biomass_at_age, na.rm = TRUE)
-    ) %>%
-    # filter(near(f_fmsy, 1) | near(f_fmsy, 0.52) | near(f_fmsy, 2.09),  near(as.numeric(reserve_frac), 0)) %>%
-    ungroup() %>%
-  group_by(sim_num, f_fmsy) %>%
-  summarize(med_ann_yield = median(ann_yield)) %>%
-  ggplot(., aes(x = f_fmsy, y = med_ann_yield)) +
-  geom_line() +
-  facet_grid(sim_num ~ .)
+       height = 10,
+       width = 8)
 
@@
 
-med_biomass <- get_median_biomass(input_df = out_fs,
-                                  age_mat = sim_species_parms$`Blue rockfish`$A_mat)
+med_biomass <- get_median_biomass(input_df = out_fs)
 med_biomass
@@
 out_yld_bm_sims_f_frac_yr <-
-  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs, 
-                                     age_mat = sim_species_parms$`Blue rockfish`$A_mat)
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs)
 
@@
 
-fig4 <- plot_grid(p1, p2, labels = letters[1:2], label_size = 9, byrow = FALSE)
+fig4 <-
+  plot_grid(
+    p1,
+    p2,
+    labels = letters[1:2],
+    label_size = 9,
+    byrow = TRUE,
+    nrow = 2,
+    ncol = 1
+  )
 
@@
        plot = fig4, 
-       height = 8, width = 5)
+       height = 10,
+       width = 8)
 ggsave(filename = "output/tmp_figs/fig4-brf-lp-biomass-yield.svg", 
        plot = fig4, 
-       height = 8, width = 5)
-
-# ggsave(filename = "output/tmp_figs/fig4-yield.png", plot = p1)
-# ggsave(filename = "output/tmp_figs/fig4-biomass.png", plot = p2)
-# 
-# ggsave(filename = "output/tmp_figs/fig4-yield.svg", plot = p1)
-# ggsave(filename = "output/tmp_figs/fig4-biomass.svg", plot = p2)
-
-```
-
-```{r}
-
-#| label: boneyard
-prep_ann_yield_abund_for_plot <- function(df_out_fs,
-                                          frac_reserves = c(0, 0.25, 0.50),
-                                          f_fmsys = c(0, 0.52, 1.00, 2.09)) {
-
-  sim_num_2_use <- min(df_out_fs$sim_num)
-  if (length(f_fmsys) < 1 | is.null(f_fmsys)) {
-    stop("Please specify f_fmsy values to use")
-  }
-
-  if (length(frac_reserves) < 1 | is.null(frac_reserves)) {
-    stop("Please specify frac_reserves values to use")
-  }
-
-    # make a sub function
-
-    return(list(main_plt_df, supp_plt_df, med_yield))
-  }
-```
-
-### Figure 4
-
-Contour plots showing the buffering effects of harvest rate and marine reserves on the abundance of a fished population, when the fished and reserve patches share a larval pool.
-
-Species: Blue rockfish
-
-Dispersal: Larval pool
-
-Environmental noise: ENSO (MEI)
-
-```{r}
-#| label: figure_4
+       height = 10,
+       width = 8)
+
 ```
@@
 
-# brf_mei_lp_nice[[2]]
-# brf_mei_lp_nice[[1]]
-# brf_mei_lp_nice[[3]]
-
 bio_yield_df <- out_fs
@@
 # x_text_val <- 550
-x_min <- 500
-x_max <- 635
+x_min <- 1
+x_max <- 135
 x_text_val <- (x_max) - (x_max - x_min)/2
@@
   purrr::map_dbl(f_fmsys_bio,  ~ u_f_fmsys[which.min(abs(u_f_fmsys - .x))])
-
-# u_f_fmsys <- u_f_fmsys[u_f_fmsys_ind]
-
-### FUNCTION
-quants_df <- bio_yield_df %>%
-  dplyr::group_by(sim_num, reserve_frac, f_fmsy, year) %>%
-  dplyr::summarize(annual_yield = sum(yield),
-                   annual_biomass = sum(biomass_at_age)) %>%
-  dplyr::ungroup() %>%
-  dplyr::group_by(sim_num, reserve_frac, f_fmsy) %>%
-  dplyr::summarize(
-    quant_80_bio = quantile(annual_biomass, 0.8),
-    quant_20_bio = quantile(annual_biomass, 0.2),
-    quant_80_yld = quantile(annual_yield, 0.8),
-    quant_20_yld = quantile(annual_yield, 0.2)
-  ) %>%
-  dplyr::ungroup() %>%
-  dplyr::group_by(reserve_frac, f_fmsy) %>%
-  dplyr::summarize(
-    quant_80_mean_bio = mean(quant_80_bio),
-    quant_20_mean_bio = mean(quant_20_bio),
-    quant_80_mean_yld = mean(quant_80_yld),
-    quant_20_mean_yld = mean(quant_20_yld)
-  ) %>%
-  dplyr::ungroup() %>%
-  dplyr::mutate(reserve_frac = as.numeric(reserve_frac)) %>%
-  dplyr::filter(reduce(map(
-    frac_reserves, near, x = reserve_frac, tol = 1e-4
-  ), `|`)) %>%
-  dplyr::filter(reduce(map(
-    u_f_fmsys, near, x = f_fmsy, tol = 1e-4
-  ), `|`))
 
@@
   dplyr::summarize(annual_biomass = sum(biomass_at_age),
-                   annual_yield = sum(yield)) %>%
+                   annual_yield = sum(yield),
+                   rel_annual_biomass = sum(biomass_at_age) / med_biomass,
+                   rel_annual_yield = sum(yield) / med_yield) %>%
   dplyr::ungroup()
 
-### FUNCTION
+### Biomass
 biom_ts_plt <- ggplot(
   bio_yield_sel_df %>% dplyr::filter(sim_num == sim_2_use),
-  aes(x = year, y = annual_biomass)
+  aes(x = year, y = rel_annual_biomass)
+  # aes(x = year, y = annual_biomass)
 ) +
@@
                                  reserve_frac = label_both)) +
+  # geom_ribbon(aes(
+  #   ymin = biomass_thresh,
+  #   ymax = pmin(annual_biomass, biomass_thresh),
+  #   fill = "Biomass lower"
+  # )) +
     geom_ribbon(aes(
-    ymin = biomass_thresh,
-    ymax = pmin(annual_biomass, biomass_thresh),
+    ymin = 1,
+    ymax = pmin(rel_annual_biomass, 1),
     fill = "Biomass lower"
   )) +
+  # geom_ribbon(aes(
+  #   ymin = annual_biomass,
+  #   ymax = pmin(annual_biomass, biomass_thresh),
+  #   fill = "Biomass higher"
+  # )) +
     geom_ribbon(aes(
-    ymin = annual_biomass,
-    ymax = pmin(annual_biomass, biomass_thresh),
+    ymin = rel_annual_biomass,
+    ymax = pmin(rel_annual_biomass, 1),
     fill = "Biomass higher"
@@
   geom_line(colour = "black") +
-    geom_segment(aes(x = 1, y = biomass_thresh, 
-                     xend = 135, yend = biomass_thresh),
+    geom_segment(aes(x = 1, y = 1, 
+                     xend = 135, yend = 1),
              colour = "red",
@@
   xlab("Year") +
-  ylab("Biomass (metric tons)") +
+  # ylab("Biomass (metric tons)") +
+  ylab("Relative Biomass") +
   ylim(0, NA) +
   labs(colour = "Reserve\nfraction") +
-  theme_minimal() +
-  # geom_hline(data = quants_df, aes(yintercept = quant_80_mean_bio), colour = "orange", linewidth = 1.1, linetype = 1) +
-  # geom_hline(data = quants_df, aes(yintercept = quant_20_mean_bio), colour = "orange", linewidth = 1.1, linetype = 1) +
+  theme_bw() +
   scale_x_continuous(expand = expansion(mult = 0, add = 0)) +
@@
     axis.line = element_line(colour = "black"),
-    panel.background = element_rect(fill = "white"),
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    panel.border = element_blank()
-  )
-
-#### ?? FUNCTION: YIELD VERSION
+    panel.background = element_rect(fill = "white")#,
+    # panel.grid.major = element_blank(),
+    # panel.grid.minor = element_blank(),
+    # panel.border = element_blank()
+  )
+
+#### Yield
 yld_ts_plt <- bio_yield_sel_df %>%
   dplyr::filter(f_fmsy != 0) %>%
-  ggplot(data = ., aes(x = year, y = annual_yield)) +
+  ggplot(data = ., aes(x = year, y = rel_annual_yield)) +
   facet_grid(reserve_frac ~ f_fmsy,
@@
   geom_ribbon(aes(
-    ymin = yield_thresh,
-    ymax = pmin(annual_yield, yield_thresh),
+    ymin = 1,
+    ymax = pmin(rel_annual_yield, 1),
     fill = "Yield lower"
@@
   geom_ribbon(aes(
-    ymin = annual_yield,
-    ymax = pmin(annual_yield, yield_thresh),
+    ymin = rel_annual_yield,
+    ymax = pmin(rel_annual_yield, 1),
     fill = "Yield higher"
@@
   geom_line(colour = "black") +
-  geom_segment(aes(x = 1, y = yield_thresh, 
-                     xend = 135, yend = yield_thresh),
+  geom_segment(aes(x = 1, y = 1, 
+                     xend = 135, yend = 1),
              colour = "red",
@@
   xlab("Year") +
-  ylab("Yield (metric tons)") +
+  # ylab("Yield (metric tons)") +
+  ylab("Relative Yield") +
   ylim(0, NA) +
   labs(colour = "Reserve\nfraction") +
-  theme_minimal() +
-  # geom_hline(data = quants_df %>% dplyr::filter(f_fmsy != 0), aes(yintercept = quant_80_mean_yld), colour = "orange", linewidth = 1.1, linetype = 1) +
-  # geom_hline(data = quants_df %>% dplyr::filter(f_fmsy != 0), aes(yintercept = quant_20_mean_yld), colour = "orange", linewidth = 1.1, linetype = 1) +
+  theme_bw() +
   scale_x_continuous(expand = expansion(mult = 0, add = 0)) +
@@
     axis.line = element_line(colour = "black"),
-    panel.background = element_rect(fill = "white"),
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    panel.border = element_blank()
+    panel.background = element_rect(fill = "white")#,
+    # panel.grid.major = element_blank(),
+    # panel.grid.minor = element_blank(),
+    # panel.border = element_blank()
   )
@@
 
+```
+
+### Figure 5 with text
+
+```{r}
+### Biomass
+
+summary_stats_df_plot <- summary_stats_df[[2]] %>%
+  dplyr::filter(reduce(map(
+    frac_reserves, near, x = as.numeric(reserve_frac), tol = 1e-4
+  ), `|`)) %>%
+  dplyr::filter(reduce(map(
+    u_f_fmsys, near, x = f_fmsy, tol = 1e-4
+  ), `|`))
+
+summary_stats_df_plot_yld <- summary_stats_df[[2]] %>%
+  dplyr::filter(reduce(map(
+    frac_reserves, near, x = as.numeric(reserve_frac), tol = 1e-4
+  ), `|`)) %>%
+  dplyr::filter(reduce(map(
+    u_f_fmsys[-1], near, x = f_fmsy, tol = 1e-4
+  ), `|`))
+
+biom_ts_plt <- ggplot(
+  bio_yield_sel_df %>% dplyr::filter(sim_num == sim_2_use),
+  aes(x = year, y = rel_annual_biomass)
+  # aes(x = year, y = annual_biomass)
+) +
+  facet_grid(reserve_frac ~ f_fmsy,
+             labeller = labeller(f_fmsy = label_both,
+                                 reserve_frac = label_both)) +
+  # geom_ribbon(aes(
+  #   ymin = biomass_thresh,
+  #   ymax = pmin(annual_biomass, biomass_thresh),
+  #   fill = "Biomass lower"
+  # )) +
+    geom_ribbon(aes(
+    ymin = 1,
+    ymax = pmin(rel_annual_biomass, 1),
+    fill = "Biomass lower"
+  )) +
+  # geom_ribbon(aes(
+  #   ymin = annual_biomass,
+  #   ymax = pmin(annual_biomass, biomass_thresh),
+  #   fill = "Biomass higher"
+  # )) +
+    geom_ribbon(aes(
+    ymin = rel_annual_biomass,
+    ymax = pmin(rel_annual_biomass, 1),
+    fill = "Biomass higher"
+  )) +
+  geom_line(colour = "black") +
+    geom_segment(aes(x = 1, y = 1, 
+                     xend = 135, yend = 1),
+             colour = "red",
+             linewidth = 0.6) +
+  scale_fill_manual(values = c("black", "grey80")) +
+geom_text(
+  data = summary_stats_df_plot,
+  x = x_text_val,
+  # y = 11000,
+  # aes(label = mean_biomass_lab)
+  y = 3.4,
+  size = 3,
+  aes(label = mean_rel_biomass_lab)
+) +
+geom_text(
+  data = summary_stats_df_plot,
+  x = x_text_val,
+  # y = 12500,
+  # aes(label = sd_biomass_lab)
+  y = 3.1,
+  size = 3,
+  aes(label = sd_rel_biomass_lab)
+) +
+geom_text(
+  data = summary_stats_df_plot,
+  x = x_text_val,
+  # y = 14000,
+  # aes(label = yrs_below_thresh)
+  y = 2.8,
+  size = 3,
+  aes(label = yrs_below_biomass_thresh_lab)
+) +
+geom_text(
+  data = summary_stats_df_plot,
+  x = x_text_val,
+  # y = 9500,
+  # aes(label = cv_biomass_lab)  
+  y = 2.5,
+  size = 3,
+  aes(label = cv_rel_biomass_lab)
+) +
+labs(fill = "Above/Below Biomass threshold") +
+  ggtitle(title_string) +
+  xlab("Year") +
+  # ylab("Biomass (metric tons)") +
+  ylab("Relative Biomass") +
+  ylim(0, NA) +
+  labs(colour = "Reserve\nfraction") +
+  theme_bw() +
+  scale_x_continuous(expand = expansion(mult = 0, add = 0)) +
+  theme(
+    axis.line = element_line(colour = "black"),
+    panel.background = element_rect(fill = "white")#,
+    # panel.grid.major = element_blank(),
+    # panel.grid.minor = element_blank(),
+    # panel.border = element_blank()
+  )
+
+#### Yield
+# summary_stats_df_plot_yld
+
+yld_ts_plt <- bio_yield_sel_df %>%
+  dplyr::filter(f_fmsy != 0) %>%
+  ggplot(data = ., aes(x = year, y = rel_annual_yield)) +
+  facet_grid(reserve_frac ~ f_fmsy,
+             labeller = labeller(f_fmsy = label_both,
+                                 reserve_frac = label_both)) +
+  geom_ribbon(aes(
+    ymin = 1,
+    ymax = pmin(rel_annual_yield, 1),
+    fill = "Yield lower"
+  )) +
+  geom_ribbon(aes(
+    ymin = rel_annual_yield,
+    ymax = pmin(rel_annual_yield, 1),
+    fill = "Yield higher"
+  )) +
+  geom_line(colour = "black") +
+  geom_segment(aes(x = 1, y = 1, 
+                     xend = 135, yend = 1),
+             colour = "red",
+             linewidth = 0.6) +
+  scale_fill_manual(values = c("black", "grey80")) +
+geom_text(
+  # data = summary_stats_df,
+  data = summary_stats_df_plot_yld,
+  x = x_text_val,
+  # y = 11000,
+  # aes(label = mean_biomass_lab)
+  y = 2.45,
+  size = 3,
+  aes(label = mean_biomass_lab)
+) +
+geom_text(
+  # data = summary_stats_df,
+  data = summary_stats_df_plot_yld,
+  x = x_text_val,
+  # y = 12500,
+  # aes(label = sd_biomass_lab)
+  y = 2.2,
+  size = 3, 
+  aes(label = sd_rel_yield_lab)
+) +
+geom_text(
+  # data = summary_stats_df,
+  data = summary_stats_df_plot_yld,
+  x = x_text_val,
+  # y = 14000,
+  y = 1.95,
+  size = 3,
+  aes(label = yrs_below_yield_thresh_lab)
+) +
+geom_text(
+  # data = summary_stats_df,
+  data = summary_stats_df_plot_yld,
+  x = x_text_val,
+  # y = 9500,
+  # aes(label = cv_yield_lab)
+  y = 1.7,
+  size = 3,
+  aes(label = cv_rel_yield_lab)
+) +
+labs(fill = "Above/Below Yield threshold") +
+  ggtitle(title_string) +
+  xlab("Year") +
+  # ylab("Yield (metric tons)") +
+  ylab("Relative Yield") +
+  ylim(0, 2.6) +
+  labs(colour = "Reserve\nfraction") +
+  theme_bw() +
+  scale_x_continuous(expand = expansion(mult = 0, add = 0)) +
+  theme(
+    axis.line = element_line(colour = "black"),
+    panel.background = element_rect(fill = "white")#,
+    # panel.grid.major = element_blank(),
+    # panel.grid.minor = element_blank(),
+    # panel.border = element_blank()
+  )
+# }
+
+print(biom_ts_plt)
+print(yld_ts_plt)
+
+ggsave(filename = "output/tmp_figs/fig5-biomass-timeseries-text.png", plot = biom_ts_plt,
+       height = 8, width = 14)
+ggsave(filename = "output/tmp_figs/fig6-yield-timeseries-text.png", plot = yld_ts_plt,
+       height = 8, width = 14)
+
+ggsave(filename = "output/tmp_figs/fig5-biomass-timeseries-text.svg", plot = biom_ts_plt,
+       height = 8, width = 14)
+ggsave(filename = "output/tmp_figs/fig6-yield-timeseries-text.svg", plot = yld_ts_plt,
+       height = 8, width = 14)
 ```
@@
 
-med_biomass <- get_median_biomass(input_df = out_fs, 
-                                  age_mat = sim_species_parms$`Blue rockfish`$A_mat)
+med_biomass <- get_median_biomass(input_df = out_fs)
 
@@
 # No dispersal
-chr_nd_white_med_biomass <- get_median_biomass(input_df = chr_nd_white_out_fs, 
-                                  age_mat = sim_species_parms$`China rockfish`$A_mat) 
+chr_nd_white_med_biomass <- get_median_biomass(input_df = chr_nd_white_out_fs) 
 chr_nd_white_med_biomass
-cab_nd_white_med_biomass <- get_median_biomass(input_df = cab_nd_white_out_fs, 
-                                  age_mat = sim_species_parms$`Cabezon`$A_mat) 
+cab_nd_white_med_biomass <- get_median_biomass(input_df = cab_nd_white_out_fs) 
 cab_nd_white_med_biomass
 # larval pool dispersal 
-chr_lp_white_med_biomass <- get_median_biomass(input_df = chr_lp_white_out_fs, 
-                                  age_mat = sim_species_parms$`China rockfish`$A_mat) 
+chr_lp_white_med_biomass <- get_median_biomass(input_df = chr_lp_white_out_fs) 
 chr_lp_white_med_biomass
-cab_lp_white_med_biomass <- get_median_biomass(input_df = cab_lp_white_out_fs, 
-                                  age_mat = sim_species_parms$`Cabezon`$A_mat) 
+cab_lp_white_med_biomass <- get_median_biomass(input_df = cab_lp_white_out_fs) 
 cab_lp_white_med_biomass
@@
 # No dispersal
-chr_nd_mei_med_biomass <- get_median_biomass(input_df = chr_nd_mei_out_fs, 
-                                  age_mat = sim_species_parms$`China rockfish`$A_mat) 
+chr_nd_mei_med_biomass <- get_median_biomass(input_df = chr_nd_mei_out_fs) 
 chr_nd_mei_med_biomass
-cab_nd_mei_med_biomass <- get_median_biomass(input_df = cab_nd_mei_out_fs, 
-                                  age_mat = sim_species_parms$`Cabezon`$A_mat) 
+cab_nd_mei_med_biomass <- get_median_biomass(input_df = cab_nd_mei_out_fs) 
 cab_nd_mei_med_biomass
 # larval pool dispersal
-chr_lp_mei_med_biomass <- get_median_biomass(input_df = chr_lp_mei_out_fs, 
-                                  age_mat = sim_species_parms$`China rockfish`$A_mat) 
+chr_lp_mei_med_biomass <- get_median_biomass(input_df = chr_lp_mei_out_fs) 
 chr_lp_mei_med_biomass
-cab_lp_mei_med_biomass <- get_median_biomass(input_df = cab_lp_mei_out_fs, 
-                                  age_mat = sim_species_parms$`Cabezon`$A_mat) 
+cab_lp_mei_med_biomass <- get_median_biomass(input_df = cab_lp_mei_out_fs) 
 cab_lp_mei_med_biomass
@@
 chr_nd_white_out_yld_bm_sims_f_frac_yr <-
-  df_yld_bm_stats_by_sim_f_frac_year(input_df = chr_nd_white_out_fs,
-                                     age_mat = sim_species_parms$`China rockfish`$A_mat)
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = chr_nd_white_out_fs)
 cab_nd_white_out_yld_bm_sims_f_frac_yr <-
-  df_yld_bm_stats_by_sim_f_frac_year(input_df = cab_nd_white_out_fs, age_mat = sim_species_parms$`Cabezon`$A_mat)
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = cab_nd_white_out_fs)
 chr_lp_white_out_yld_bm_sims_f_frac_yr <-
-  df_yld_bm_stats_by_sim_f_frac_year(input_df = chr_lp_white_out_fs,
-                                     age_mat = sim_species_parms$`China rockfish`$A_mat)
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = chr_lp_white_out_fs)
 cab_lp_white_out_yld_bm_sims_f_frac_yr <-
-  df_yld_bm_stats_by_sim_f_frac_year(input_df = cab_lp_white_out_fs, age_mat = sim_species_parms$`Cabezon`$A_mat)
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = cab_lp_white_out_fs)
 chr_nd_mei_out_yld_bm_sims_f_frac_yr <-
-  df_yld_bm_stats_by_sim_f_frac_year(input_df = chr_nd_mei_out_fs,
-                                     age_mat = sim_species_parms$`China rockfish`$A_mat)
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = chr_nd_mei_out_fs)
 cab_nd_mei_out_yld_bm_sims_f_frac_yr <-
-  df_yld_bm_stats_by_sim_f_frac_year(input_df = cab_nd_mei_out_fs, age_mat = sim_species_parms$`Cabezon`$A_mat)
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = cab_nd_mei_out_fs)
 chr_lp_mei_out_yld_bm_sims_f_frac_yr <-
-  df_yld_bm_stats_by_sim_f_frac_year(input_df = chr_lp_mei_out_fs,
-                                     age_mat = sim_species_parms$`China rockfish`$A_mat)
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = chr_lp_mei_out_fs)
 cab_lp_mei_out_yld_bm_sims_f_frac_yr <-
-  df_yld_bm_stats_by_sim_f_frac_year(input_df = cab_lp_mei_out_fs, age_mat = sim_species_parms$`Cabezon`$A_mat)
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = cab_lp_mei_out_fs)
 

### 2023-12-21 R/fig_functions (dpkilduff@gmail.com).R

@@ -1,221 +1,0 @@
-# Functions for table meta data
-
-get_current_exp <- function(table_name) {
-  # returns species, dispersal, noise params to extract from duckdb table names 
-  valid_dispersal <- c("larval_pool", "no_dispersal")
-  valid_species <-
-    c("blue_rockfish", "cabezon", "china_rockfish", "pacific_cod", "kelp_bass")
-  valid_noise <- c("mei_135_75", "white_135_75")
-  
-  current_dispersal <-
-    valid_dispersal[stringr::str_detect(table_name, valid_dispersal)]
-  current_species <-
-    valid_species[stringr::str_detect(table_name, valid_species)]
-  current_noise <-
-    valid_noise[stringr::str_detect(table_name, valid_noise)]
-  return(list(current_dispersal, current_species, current_noise))
-}
-
-get_nice_exp <- function(table_name) {
-  # returns "pretty" version of species, dispersal, noise params for plotting
-  valid_dispersal <- c("larval_pool", "no_dispersal")
-  valid_species <-
-    c("blue_rockfish", "cabezon", "china_rockfish", "pacific_cod", "kelp_bass")
-  valid_noise <- c("mei_135_75", "white_135_75")
-  
-  pretty_dispersal <- c("Larval pool", "No dispersal")
-  pretty_species <- c("Blue rockfish", "Cabezon", "China rockfish", "Pacific cod", "Kelp bass")
-  pretty_noise <- c("ENSO", "White")
-  
-  nice_dispersal <-
-    pretty_dispersal[stringr::str_detect(table_name, valid_dispersal)]
-  nice_species <-
-    pretty_species[stringr::str_detect(table_name, valid_species)]
-  nice_noise <-
-    pretty_noise[stringr::str_detect(table_name, valid_noise)]
-  
-  return(list(nice_dispersal, nice_species, nice_noise))
-}
-
-
-
-#' Get Fishing Mortality Levels that Maximize Yield
-#'
-#' For each FLEP ratio, find the fishing mortality level  
-#' that maximizes yield when there are no reserves.
-#'
-#' @param input_df dataframe with simulation results 
-#' @param fleps_2_fs dataframe matching FLEP ratios to F values
-#' 
-#' @return Vector of optimal F values for maximum yield for each FLEP ratio
-#'
-#' @examples
[…]

### 2023-12-21 R/fig_functions.R

@@ -1,221 +1,0 @@
-# Functions for table meta data
-
-get_current_exp <- function(table_name) {
-  # returns species, dispersal, noise params to extract from duckdb table names 
-  valid_dispersal <- c("larval_pool", "no_dispersal")
-  valid_species <-
-    c("blue_rockfish", "cabezon", "china_rockfish")
-  valid_noise <- c("mei_135_75", "white_135_75")
-  
-  current_dispersal <-
-    valid_dispersal[stringr::str_detect(table_name, valid_dispersal)]
-  current_species <-
-    valid_species[stringr::str_detect(table_name, valid_species)]
-  current_noise <-
-    valid_noise[stringr::str_detect(table_name, valid_noise)]
-  return(list(current_dispersal, current_species, current_noise))
-}
-
-get_nice_exp <- function(table_name) {
-  # returns "pretty" version of species, dispersal, noise params for plotting
-  valid_dispersal <- c("larval_pool", "no_dispersal")
-  valid_species <-
-    c("blue_rockfish", "cabezon", "china_rockfish", "pacific_cod", "kelp_bass")
-  valid_noise <- c("mei_135_75", "white_135_75")
-  
-  pretty_dispersal <- c("Larval pool", "No dispersal")
-  pretty_species <- c("Blue rockfish", "Cabezon", "China rockfish", "Pacific cod", "Kelp bass")
-  pretty_noise <- c("ENSO", "White")
-  
-  nice_dispersal <-
-    pretty_dispersal[stringr::str_detect(table_name, valid_dispersal)]
-  nice_species <-
-    pretty_species[stringr::str_detect(table_name, valid_species)]
-  nice_noise <-
-    pretty_noise[stringr::str_detect(table_name, valid_noise)]
-  
-  return(list(nice_dispersal, nice_species, nice_noise))
-}
-
-
-
-#' Get Fishing Mortality Levels that Maximize Yield
-#'
-#' For each FLEP ratio, find the fishing mortality level  
-#' that maximizes yield when there are no reserves.
-#'
-#' @param input_df dataframe with simulation results 
-#' @param fleps_2_fs dataframe matching FLEP ratios to F values
-#' 
-#' @return Vector of optimal F values for maximum yield for each FLEP ratio
-#'
-#' @examples
-#' input_df <- data.frame(sim_num = rep(1, 30), 
[…]

### 2023-12-21 R/functions.R

@@ -1,5 +1,4 @@
-#' functions. R
-
+# functions.R
 
 #'
 #' @title load life history and fishery parameters for California 'fish' species
@@ -307,220 +306,25 @@ list_lep <- function(spec_names, sim_spec_der_var) {
   return(lifetime_eggs_production)
 }
 
+#' Downloads and processes annual MEI data from NOAA
 #'
-#' @title make a species specific Leslie matrix for each patch at a specified
-#' level of FLEP (e.g., fishing mortality)
+#' @description
+#' This function downloads the extended Multivariate ENSO Index (MEI) data
+#' from the NOAA Physical Sciences Laboratory website, processes it into an
+#' annual time series, and adds a column for ENSO phase based on MEI values.
 #'
-#' @description creates a matrix (or array -- one matrix for each patch) that contains
-#' age-specific fecundity values on the first row and survival from age a-1 to
-#' age a on the sub-diagonal (a Leslie matrix)
+#' @return
+#' A data frame with columns:
+#'   - year: The year (integer).
+#'   - mei: The annual average MEI value (numeric).
+#'   - phase: The ENSO phase, either "0" for negative MEI or "1" for positive MEI (character).
 #'
-#' @return returns a Leslie matrix (or multiple Leslie matrices as an array, with
-#' one matrix for each patch)
+#' @note
+#' This function relies on an external website for data access and may be
+#' affected by changes to the website's structure or data format.
 #'
-#' @param num_patches the number of patches included in the model
-#' @param surv_fished_matrix a matrix of cumulative
-#' survival to each age at many levels of fishing mortality
-#' @param surv_fished_ind index of the column that corresponds the survival vector for a
-#' given level of fishing (or FLEP - the fraction of lifetime egg production)
-#' @param age_max numeric the value of the maximum age for a selected species
-#' @param fecundity_at_age vector of fecundity (number of eggs produced) at each age
-#'
-#' @examples
-#'
-#' les_mat_cbzn_F0 <- make_leslie_mat(num_patches = 1,
-#'                                    surv_fished_matrix = derived_vars_cbzn$surv_fished,
-#'                                    surv_fished_ind = 1,
-#'                                    age_max = lh_parms_cbzn$A_max,
[…]

### 2023-12-21 R/test_functions.R

@@ -1,160 +1,0 @@
-# 
-# sim_num = num_sims_dt
-# reserve_frac = reserve_fracs_dt
-# flep_ratio = flep_ratios_dt
-# year = year_vals_dt
-# age = age_vals_dt
-# patch_num = patch_num_dt
-# number = NA_real_
-# yield = NA_real_
-
-#### USED
-run_sims_sm_write <- function(expmts,
-                              spec_name,
-                              alpha_bh,
-                              beta_bh,
-                              recr_sd,
-                              num_sims,
-                              frac_reserves,
-                              fleps,
-                              n_years,
-                              noise_vec,
-                              noise_dat,
-                              num_patches,
-                              les_mats,
-                              conn_mats,
-                              in_out_fracs,
-                              sim_results,
-                              sim_spec_dervars,
-                              f_vals,
-                              spec_flep_f_ind,
-                              sim_spec_pars) {
-  
-  con <-
-    dbConnect(duckdb::duckdb(),
-              dbdir = "data/sim_out.duckdb",
-              read_only = FALSE)
-  
-  for (i in 1:length(expmts)) {
-    for (j in 1:length(spec_name)) {
-      for (k in noise_vec) {
-        for (l in 1:length(recr_sd)) {
-          for (m in 1:num_sims) {
-            print(paste0("num_sims: ", m))
-            for (n in 1:length(frac_reserves)) {
-              # print(paste0("frac_res: ", frac_reserves[n]))
-              for (o in 1:length(fleps)) {
-                # print(paste0("fleps: ", fleps[o]))
-                dt_one <- data.table(sim_num = m, 
-                                     reserve_frac=as.character(frac_reserves[n]), 
-                                     flep_ratio=as.character(fleps[o]), 
-                                     number = list(), 
-                                     yield = list())
-                
-                # dt_one <- dt[i = .(
-                #   expmts[i],
-                #   spec_name[j],
-                #   alpha_bh[j],
-                #   recr_sd[m],
-                #   frac_reserves[o],
-                #   fleps[n],
-                #   p,
-                #   q
-                # ), ]
-                # dt_one <- dt[i = sim_num == m & near(reserve_frac, frac_reserves[n]) & near(flep_ratio, fleps[o]),]
-                
-                out <- run_patch_sims2(
-                  t_steps = n_years,
[…]

### 2023-12-21 _targets.R

@@ -1,7 +1,6 @@
 library(targets)
 library(tarchetypes)
 source(file.path("R", "functions.R"))
-source(file.path("R", "test_functions.R"))
 options(tidyverse.quiet = TRUE)
 tar_option_set(
   packages = c(
@@ -18,11 +17,10 @@ tar_option_set(
   )
 )
 
-
 r_seed <- 11
 tar_seed(default = r_seed)
 
-## TODO: check for duck.db files and delete before running
+## NOTE:check for duckdb file ("data/sim_out.duckdb") and delete before running
 
 list(
   tar_target(exp_names_nd,
@@ -68,26 +66,20 @@ list(
   # Simulation length burn_in and actual sim_len:
   tar_target(burn_in,
              500),
-  # tar_target(sim_len,
-  #            512),
   tar_target(sim_len_135,
              135),
-  # tar_target(n_years,
-  #            burn_in + sim_len),
   tar_target(n_years_135,
              burn_in + sim_len_135),
-  # tar_target(sim_yrs,
-  #            1:n_years),
   tar_target(sim_yrs_135,
              1:n_years_135),
   # Run how many replicate simulations?
   tar_target(sim_nums,
-             5), ### --> 10
+             5), 
   tar_target(sd_recruitment,
              0.75),
   # Fraction of lifetime egg production (FLEP)
   # Lower FLEPs correspond to populations that have experienced higher exploitation
-  # 0.3 is close to population collapse, so 0.4 is close enough to get cohort resonance
+  # 0.3 is close to population collapse, 0.4 is close enough to get cohort resonance
   tar_target(flep_ratios,
              c(seq(0.2, 0.975, by = 0.025), 0.998)),
   tar_target(reserve_fracs,
@@ -244,27 +236,13 @@ list(
     larvpool_disp_conn_mat %>% purrr::map(., ~ matrix(.x[, 1], nrow = 2))
   ),
   # Environmental noise
-  # need to make n_sims number of noise signals for enso and white
-  # tar_target(noises_white,
-  #            "white"),
   tar_target(noises_white_135,
                         "white_135"),
-  # tar_target(noises_enso,
-  #            "enso"),
[…]

### 2023-12-21 report-generator.R

@@ -1,39 +1,0 @@
-library(quarto)
-library(DBI)
-library(duckdb)
-library(tidyverse)
-
-if (exists(x = "con")) dbDisconnect(con, shutdown=TRUE)
-con <- DBI::dbConnect(duckdb::duckdb(),
-                      dbdir = "data/sim_out.duckdb",
-                      read_only = FALSE) # change to TRUE???
-
-avail_tables <- DBI::dbListTables(con)
-
-exp_tabs <- avail_tables[!str_detect(avail_tables, "enso_75|white_75|mei_135_25|white_135_25")]
-
-DBI::dbDisconnect(conn = con, shutdown = TRUE)
-
-exp_tabs <- exp_tabs[str_detect(exp_tabs, "blue_rockfish")]
-
-run_html <- function(experiment) {
-  quarto::quarto_render(
-    "recs-abund-yield-parameters.qmd",
-    output_format = "html",
-    execute_params = list(experiment = experiment),
-    output_file = glue::glue("ts-contour-plots-{experiment}.html")
-  )
-}
-
-purrr::map(exp_tabs, run_html)
-
-# 
-# con <- DBI::dbConnect(duckdb::duckdb(),
-#                       dbdir = "data/sim_out.duckdb",
-#                       read_only = FALSE) # change to TRUE???
-# nd_qry <- "select * from 'no_dispersal_blue_rockfish_mei_135_75' limit 2000"
-# lp_qry <- "select * from 'larval_pool_blue_rockfish_mei_135_75' limit 2000"
-# nd_df <- dbGetQuery(con, nd_qry)
-# lp_df <- dbGetQuery(con, lp_qry)
-# all.equal(nd_df, lp_df)
-# DBI::dbDisconnect(con, shutdown = TRUE)

### 2023-12-21 test_duckdb_connect.R

@@ -1,44 +1,0 @@
-# Install and load packages
-# Uncomment next 5 lines first time the project is run
-# install.packages(c("DBI", "ggplot2"))
-library(remotes)
-# ## duckdb note: newer package versions cannot read databases written with older versions
-# ## until the duckdb (R package) version reaches 1.0
-install_version("duckdb", version = "0.7.0", repos = "https://cloud.r-project.org/")
-
-library(DBI)
-library(duckdb)
-library(ggplot2)
-
-# connect to the database
-con <- DBI::dbConnect(duckdb::duckdb(),
-                      dbdir = "data/sim_out.duckdb",
-                      read_only = FALSE)
-# list the names of tables in the database
-tables <- dbListTables(con)
-
-# query one of the tables # larval_pool_blue_rockfish_mei_135_75
-for (i in 1:length(tables)) {
-  out <- dbGetQuery(conn = con, paste0("SELECT reserve_frac, flep_ratio, sum(number) as total_nums, sum(yield) as total_yield 
-                               from '", tables[i], "' 
-                               where year > 500
-                               group by reserve_frac, flep_ratio
-                               order by reserve_frac asc, flep_ratio asc"))
-  
-  print(tail(out))
-  
-}
-
-# make some quick plots that are kind of like the real plots for the last table of the loop
-ggplot(out, aes(x = as.numeric(reserve_frac), 
-                y = as.numeric(flep_ratio),
-                z = total_nums)) +
-  geom_contour_filled()
-
-ggplot(out, aes(x = as.numeric(reserve_frac), 
-                y = as.numeric(flep_ratio),
-                z = total_yield)) +
-  geom_contour_filled()
-
-# close the connection
-DBI::dbDisconnect(con, shutdown = TRUE)

### 2023-12-23 ms_figures_supp_figs.qmd
refactor all code for main figs to streamline and/or use functions

@@
 
-List of DuckDB tables
+List of tables in "data/sim_out.duckdb":
 
@@
 
+This .rmd file can be run as a script that produces the main text figues and the supporting figures for the manuscript *Marine reserves can provide buffering against environmental fluctuations to overexploited but not sustainably harvested fisheries*.
+
+In RStudio, click on `Code` -\> `Run Region` --\> `Run All` to run the script and create all the files.
+
+To render an .html file from RStudio, click the Render button.
+
+To export to pdf, follow the instructions [here](https://quarto.org/docs/output-formats/pdf-basics.html) to install a Quarto "friendly" Tex distribution.
+Then click the small down arrow of the Render button and select `Render as pdf`
+
+Exporting to a Word (.docx) file requires that MS Word/Office is installed, then click the small down arrow of the Render button and select `Render as MS Word` .
+
 ```{r}
@@
 library(targets)
+suppressMessages(library(tidyverse))
+library(cowplot)
 library(DBI)
 library(duckdb)
-library(cowplot)
-suppressMessages(library(tidyverse))
 
@@
 source("R/functions.R")
-# source("R/fig_functions.R")
 
@@
 
-con <- DBI::dbConnect(duckdb::duckdb(),
-                      dbdir = "data/sim_out.duckdb",
-                      read_only = FALSE)
 ```
@@
 # plotting params
-x_text_position_parm <- 550 
 max_reserve_frac <- 0.5
@@
 
-# A total of 5 (2023/12/20) simulations were run for each paramter set
-# This set allows us to determine the number of simulations to use 
-# in the contour plots to produce clear contours by picking a random subset of
-# simulations up to the full set of simulations
-
-# num_sims_2_avg <- 5
-
-sims_2_use <- 1:5 # sort(sample(1:sim_nums, size = num_sims_2_avg, replace = FALSE))
+# A total of `sim_nums` simulations were run for each paramter set.
+# Running multiple simulations helps to produce clear contours and reduce
+# impact of artifacts of a single simulation run
+
+sims_2_use <- 1:sim_nums
 
@@
 
-## Main figures
-
-brf_white_lp_current \<- get_current_exp(table_name = "larval_pool_blue_rockfish_white_135_75")
-
-brf_white_lp_nice \<- get_nice_exp(table_name = "larval_pool_blue_rockfish_white_135_75")
-
-brf_white_lp_current\[\[1\]\]
-
-brf_white_lp_current\[\[2\]\]
-
-brf_white_lp_current\[\[3\]\]
-
-brf_white_lp_nice\[\[1\]\]
-
-brf_white_lp_nice\[\[2\]\]
-
-brf_white_lp_nice\[\[3\]\]
+## Main text figures
 
@@
 
-# Set table names to be used to make the main figures
-
-table_name_nd <- "no_dispersal_blue_rockfish_mei_135_75"
-table_name_lp <- "larval_pool_blue_rockfish_mei_135_75"
-table_name_nd_white <- "no_dispersal_blue_rockfish_white_135_75"
-table_name_lp_white <- "larval_pool_blue_rockfish_white_135_75"
+# Set table names to be used to make the main figures for blue rockfish
+
+table_name_brf_nd_mei <- "no_dispersal_blue_rockfish_mei_135_75"
+table_name_brf_lp_mei <- "larval_pool_blue_rockfish_mei_135_75"
+table_name_brf_nd_white <- "no_dispersal_blue_rockfish_white_135_75"
+table_name_brf_lp_white <- "larval_pool_blue_rockfish_white_135_75"
 
@@
 
-brf_mei_nd_current <- get_current_exp(table_name = table_name_nd)
-brf_mei_nd_nice <- get_nice_exp(table_name = table_name_nd)
-
-brf_white_nd_current <- get_current_exp(table_name = table_name_nd_white)
-brf_white_nd_nice <- get_nice_exp(table_name = table_name_nd_white)
-
-brf_mei_lp_current <- get_current_exp(table_name = table_name_lp)
-brf_mei_lp_nice <- get_nice_exp(table_name = table_name_lp)
-
-brf_white_lp_current <- get_current_exp(table_name = table_name_lp_white)
-brf_white_lp_nice <- get_nice_exp(table_name = table_name_lp_white)
-
-```
-
-### Figure 3
-
-Contour plots showing the buffering effects of harvest rate and marine reserves on the abundance of a fished population, when there is no larval dispersal between the fished and reserve habitat patches.
-
-Species: Blue rockfish
-
-Dispersal: No Dispersal
-
-Environmental noise: ENSO (MEI)
-
-```{r}
-#| label: figure_3
+brf_nd_mei_current <- get_current_exp(table_name = table_name_brf_nd_mei)
+brf_nd_mei_nice <- get_nice_exp(table_name = table_name_brf_nd_mei)
+
+brf_nd_white_current <- get_current_exp(table_name = table_name_brf_nd_white)
+brf_nd_white_nice <- get_nice_exp(table_name = table_name_brf_nd_white)
+
+brf_lp_mei_current <- get_current_exp(table_name = table_name_brf_lp_mei)
+brf_lp_mei_nice <- get_nice_exp(table_name = table_name_brf_lp_mei)
+
+brf_lp_white_current <- get_current_exp(table_name = table_name_brf_lp_white)
+brf_lp_white_nice <- get_nice_exp(table_name = table_name_brf_lp_white)
+
+## Blue rockfish reproductive biology and fishery params
 
 # use species specific vB params to create a weight at age data.frame that can be used to convert abundance at age to biomass at age
-species_name <- brf_mei_nd_nice[[2]]
+species_name <- brf_nd_mei_nice[[2]]
 brf_waa_g <- sim_species_parms[[species_name]][["biom_const"]] * sim_species_derived_vars[[species_name]][["length_at_age"]] ^
@@
 # FLEP to F reference tables by species
-spec_fleps_2_fs <-
+spec_fleps_2_fs_brf <-
   get_fs_from_fleps(species = species_name,
@@
 
-## Qry 
-qry <- paste0("SELECT  sim_num, reserve_frac, flep_ratio, year, age, 
-              sum(number) as abundance,
-              sum(yield) as yield,
-              FROM '", table_name_nd, 
-              "' WHERE sim_num IN (", toString(sims_2_use), ") AND year > 500 
-              GROUP BY sim_num, reserve_frac, flep_ratio, year, age
-              ORDER BY sim_num, reserve_frac, flep_ratio, year, age
-              ")
-
-sim_res_out <- dbGetQuery(conn = con, qry)
-
-F_brf_maxes_yield <- get_f_maxes_yield(input_df = sim_res_out,
-                                         fleps_2_fs = spec_fleps_2_fs)
-# F_brf_maxes_yield
-
-out_fs <- df_add_fs_out(
-  input_df = sim_res_out,
-  spec_fleps_2_fs = spec_fleps_2_fs,
-  F_maxes_yield = F_brf_maxes_yield,
+```
+
+### Figure 3
+
+Contour plots showing the buffering effects of harvest rate and marine reserves on the abundance of a fished population, when there is no larval dispersal between the fished and reserve habitat patches.
+
+Species: Blue rockfish
+
+Dispersal: No Dispersal
+
+Environmental noise: ENSO (MEI)
+
+```{r}
+#| label: figure_3
+
+sim_res_out_brf_nd_mei <-
+  qry_get_sim_data_for_analysis(table_name = table_name_brf_nd_mei)
+# sim_res_out_brf_nd_mei
+
+F_brf_maxes_yield_brf_nd_mei <- get_f_maxes_yield(input_df = sim_res_out_brf_nd_mei,
+                                         fleps_2_fs = spec_fleps_2_fs_brf)
+# F_brf_maxes_yield_brf_nd_mei
+
+out_fs_brf_nd_mei <- df_add_fs_out(
+  input_df = sim_res_out_brf_nd_mei,
+  spec_fleps_2_fs = spec_fleps_2_fs_brf,
+  F_maxes_yield = F_brf_maxes_yield_brf_nd_mei,
   waa_g_df = brf_waa_g_df
 )
-# out_fs
-
-med_yield <- get_median_yield(input_df = out_fs) 
-# med_yield
-
-med_biomass <- get_median_biomass(input_df = out_fs)
-# med_biomass
-
-out_yld_bm_sims_f_frac_yr <-
-  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs)
-
-sum_stats_f_frac_df <-
+# out_fs_brf_nd_mei
+
+med_yield_brf <- get_median_yield(input_df = out_fs_brf_nd_mei) 
+# med_yield_brf
+
+med_biomass_brf <- get_median_biomass(input_df = out_fs_brf_nd_mei)
+# med_biomass__brf_nd_mei
+
+out_yld_bm_sims_f_frac_yr_brf_nd_mei <-
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs_brf_nd_mei)
+# out_yld_bm_sims_f_frac_yr_brf_nd_mei
+
+sum_stats_f_frac_df_brf_nd_mei <-
   summary_stats_by_f_frac(
-    out_sim_f_frac_yr = out_yld_bm_sims_f_frac_yr,
-    median_yield = med_yield,
-    median_biomass = med_biomass
-  )
-# sum_stats_f_frac_df
+    out_sim_f_frac_yr = out_yld_bm_sims_f_frac_yr_brf_nd_mei,
+    median_yield = med_yield_brf,
+    median_biomass = med_biomass_brf
+  )
+# sum_stats_f_frac_df_brf_nd_mei
 
@@
 
-p1 <- sum_stats_f_frac_df[[2]] %>%
-  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
-  ggplot(.,
-       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_biomass_thresh)) +
-  metR::geom_contour_fill(bins = 12) +
-  ggtitle(paste0(
-        brf_mei_nd_nice[[2]],
-        " ",
-        brf_mei_nd_nice[[1]],
-        " ",
-        brf_mei_nd_nice[[3]],
-        ":\nTime below mean median biomass "
-      )) +
-      xlab("Fraction of coastline in reserves") +
-      ylab("Harvest Rate (F/Fmsy)") +
-      scale_fill_viridis_c(option = "D", direction = -1) +
-      geom_segment(aes(
-        x = 0,
-        xend = max_reserve_frac,
-        y = 1,
-        yend = 1
-      ), colour = "black",
-      linetype = 2) +
-      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
-      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
-      theme_bw()
-
-p2 <- sum_stats_f_frac_df[[2]] %>%
-  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
-  ggplot(.,
-       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_yield_thresh)) +
-  metR::geom_contour_fill(bins = 12) + 
-  ggtitle(paste0(
-        brf_mei_nd_nice[[2]],
-        " ",
-        brf_mei_nd_nice[[1]],
-        " ",
-        brf_mei_nd_nice[[3]],
-        ":\nTime below median max yield"
-      )) +
-      xlab("Fraction of coastline in reserves") +
-      ylab("Harvest Rate (F/Fmsy)") +
-      scale_fill_viridis_c(option = "D", direction = -1) +
-      geom_segment(aes(
-        x = 0,
-        xend = max_reserve_frac,
-        y = 1,
-        yend = 1
-      ), colour = "black",
-      linetype = 2) +
-      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
-      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
-      theme_bw()
+p1 <-
+  plot_contour_bm_below_thresh(sum_stats_f_frac_df = sum_stats_f_frac_df_brf_nd_mei,
+                               spec_disp_noise = brf_nd_mei_nice)
+
+p2 <-
+  plot_contour_yld_below_thresh(sum_stats_f_frac_df = sum_stats_f_frac_df_brf_nd_mei,
+                                spec_disp_noise = brf_nd_mei_nice)
 
@@
 
-ggsave(filename = "output/tmp_figs/fig3-brf-nd-mei-biomass-yield.png", 
+print(fig3)
+
+ggsave(filename = "output/main_figs/fig3-brf-nd-mei-biomass-yield.png",
        plot = fig3,
@@
        width = 8)
-ggsave(filename = "output/tmp_figs/fig3-brf-nd-mei-biomass-yield.svg", 
+ggsave(filename = "output/main_figs/fig3-brf-nd-mei-biomass-yield.svg",
        plot = fig3,
@@
 
-# use species specific vB params to create a weight at age data.frame that can be used to convert abundance at age to biomass at age
-species_name <- brf_mei_lp_nice[[2]]
-brf_waa_g <- sim_species_parms[[species_name]][["biom_const"]] * sim_species_derived_vars[[species_name]][["length_at_age"]] ^
-                    sim_species_parms[[species_name]][["biom_exp"]]
-
-brf_waa_g_df <- data.frame(age = 1: sim_species_parms[[species_name]]$A_max,
-                           waa_g = brf_waa_g)
-
-# use functions to create useful data structures
-# FLEP to F reference tables by species
-spec_fleps_2_fs <-
-  get_fs_from_fleps(species = species_name,
-                    flep_inds = species_flep_fished_ind,
-                    f_vals =  fishing_mortality_values)
+# # use species specific vB params to create a weight at age data.frame that can be used to convert abundance at age to biomass at age
+# species_name <- brf_mei_lp_nice[[2]]
+# brf_waa_g <- sim_species_parms[[species_name]][["biom_const"]] * sim_species_derived_vars[[species_name]][["length_at_age"]] ^
+#                     sim_species_parms[[species_name]][["biom_exp"]]
+# 
+# brf_waa_g_df <- data.frame(age = 1: sim_species_parms[[species_name]]$A_max,
+#                            waa_g = brf_waa_g)
+# 
+# # use functions to create useful data structures
+# # FLEP to F reference tables by species
+# spec_fleps_2_fs <-
+#   get_fs_from_fleps(species = species_name,
+#                     flep_inds = species_flep_fished_ind,
+#                     f_vals =  fishing_mortality_values)
 
 ## Qry
-qry <- paste0("SELECT  sim_num, reserve_frac, flep_ratio, year, age, 
-              sum(number) as abundance,
-              sum(yield) as yield,
-              FROM '", table_name_lp, 
-              "' WHERE sim_num IN (", toString(sims_2_use), ") AND year > 500 
-              GROUP BY sim_num, reserve_frac, flep_ratio, year, age
-              ORDER BY sim_num, reserve_frac, flep_ratio, year, age
-              ")
-
-sim_res_out_brf_mei_lp <- dbGetQuery(conn = con, qry)
-
-#######
-
-########### PIPELINING
-F_brf_maxes_yield <- get_f_maxes_yield(input_df = sim_res_out_brf_mei_lp,
-                                         fleps_2_fs = spec_fleps_2_fs)
-F_brf_maxes_yield
-
-out_fs <- df_add_fs_out (input_df = sim_res_out_brf_mei_lp,
-                         spec_fleps_2_fs = spec_fleps_2_fs,
-                         F_maxes_yield = F_brf_maxes_yield, waa_g_df = brf_waa_g_df)
-out_fs
-
-med_yield <- get_median_yield(input_df = out_fs) 
-med_yield
-
-med_biomass <- get_median_biomass(input_df = out_fs)
-med_biomass
-
-out_yld_bm_sims_f_frac_yr <-
-  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs)
-
-# pipeline works to here
-
-sum_stats_f_frac_df <-
+
+sim_res_out_brf_lp_mei <-
+  qry_get_sim_data_for_analysis(table_name = table_name_brf_lp_mei)
+
+F_brf_maxes_yield_brf_lp_mei <- get_f_maxes_yield(input_df = sim_res_out_brf_lp_mei,
+                                         fleps_2_fs = spec_fleps_2_fs_brf)
+# F_brf_maxes_yield_brf_lp_mei
+
+out_fs_brf_lp_mei <- df_add_fs_out (input_df = sim_res_out_brf_lp_mei,
+                         spec_fleps_2_fs = spec_fleps_2_fs_brf,
+                         F_maxes_yield = F_brf_maxes_yield_brf_lp_mei, 
+                         waa_g_df = brf_waa_g_df)
+# out_fs_brf_lp_mei
+
+out_yld_bm_sims_f_frac_yr_brf_lp_mei <-
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs_brf_lp_mei)
+# out_yld_bm_sims_f_frac_yr_brf_lp_mei
+
+sum_stats_f_frac_df_brf_lp_mei <-
   summary_stats_by_f_frac(
-    out_sim_f_frac_yr = out_yld_bm_sims_f_frac_yr,
-    median_yield = med_yield,
-    median_biomass = med_biomass
-  )
-sum_stats_f_frac_df
+    out_sim_f_frac_yr = out_yld_bm_sims_f_frac_yr_brf_lp_mei,
+    median_yield = med_yield_brf,
+    median_biomass = med_biomass_brf
+  )
+# sum_stats_f_frac_df_brf_lp_mei
 
@@
 
-p1 <- sum_stats_f_frac_df[[2]] %>%
-  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
-  ggplot(.,
-       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_biomass_thresh)) +
-  metR::geom_contour_fill(bins = 12) +
-  ggtitle(paste0(
-        brf_mei_lp_nice[[2]],
-        " ",
-        brf_mei_lp_nice[[1]],
-        " ",
-        brf_mei_lp_nice[[3]],
-        ":\nTime below mean median biomass "
-      )) +
-      xlab("Fraction of coastline in reserves") +
-      ylab("Harvest Rate (F/Fmsy)") +
-      scale_fill_viridis_c(option = "D", direction = -1) +
-      geom_segment(aes(
-        x = 0,
-        xend = max_reserve_frac,
-        y = 1,
-        yend = 1
-      ), colour = "black",
-      linetype = 2) +
-      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
-      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
-      theme_bw()
-
-p2 <- sum_stats_f_frac_df[[2]] %>%
-  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
-  ggplot(.,
-       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_yield_thresh)) +
-  metR::geom_contour_fill(bins = 12) + 
-  ggtitle(paste0(
-        brf_mei_lp_nice[[2]],
-        " ",
-        brf_mei_lp_nice[[1]],
-        " ",
-        brf_mei_lp_nice[[3]],
-        ":\nTime below median max yield"
-      )) +
-      xlab("Fraction of coastline in reserves") +
-      ylab("Harvest Rate (F/Fmsy)") +
-      scale_fill_viridis_c(option = "D", direction = -1) +
-      geom_segment(aes(
-        x = 0,
-        xend = max_reserve_frac,
-        y = 1,
-        yend = 1
-      ), colour = "black",
-      linetype = 2) +
-      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
-      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
-      theme_bw()
+p1 <-
+  plot_contour_bm_below_thresh(sum_stats_f_frac_df = sum_stats_f_frac_df_brf_lp_mei,
+                               spec_disp_noise = brf_lp_mei_nice)
+
+p2 <-
+  plot_contour_yld_below_thresh(sum_stats_f_frac_df = sum_stats_f_frac_df_brf_lp_mei,
+                                spec_disp_noise = brf_lp_mei_nice)
 
@@
 
-ggsave(filename = "output/tmp_figs/fig4-brf-lp-biomass-yield.png", 
+print(fig4)
+
+ggsave(
+  filename = "output/main_figs/fig4-brf-lp-mei-biomass-yield.png",
   plot = fig4,
   height = 10,
-       width = 8)
-ggsave(filename = "output/tmp_figs/fig4-brf-lp-biomass-yield.svg", 
+  width = 8
+)
+ggsave(
+  filename = "output/main_figs/fig4-brf-lp-mei-biomass-yield.svg",
   plot = fig4,
   height = 10,
-       width = 8)
+  width = 8
+)
 
@@
 
-### Figure 5
-
-Representative timeseries of total population biomass under different combinations of fishing rate and marine reserve protection.
+### Figure 5 and 6
+
+Representative timeseries of total population biomass and yield ( under different combinations of fishing rate and marine reserve protection.
 
@@
 ```{r}
-#| label: figure_5
-
-bio_yield_df <- out_fs
-summary_stats_df <- sum_stats_f_frac_df
-
-yield_thresh <- med_yield
-biomass_thresh <- med_biomass
-
-exp_deets <- brf_mei_lp_nice
-
-text <- TRUE
-# x_text_val <- 550
-x_min <- 1
-x_max <- 135
-x_text_val <- (x_max) - (x_max - x_min)/2
-
-r_seed <- 34
-
-frac_reserves <- c(0, 0.25, 0.50)
-f_fmsys <- c(0.52, 1.00, 2.09)
-
-# facet_bm_yld_ts_plots <- function(bio_yield_df,  # main_plt_df
-#                                  summary_stats_df, # sub_plt_df,
-#                                  yield_thresh,
-#                                  biomass_thresh,
-#                                  exp_deets,
-#                                  x_text_val = 550,
-#                                  r_seed = 34,
-#                                  frac_reserves = c(0, 0.25, 0.50),
-#                                  f_fmsys = c(0.52, 1.00, 2.09)) {
-
-set.seed(r_seed)
-sim_2_use <-
-  sample(sort(unique(bio_yield_df$sim_num)), 1, replace = FALSE)
-
-f_fmsys_bio <- c(0, f_fmsys)
-
-### FUNCTION
-plt_species <- unique(exp_deets[[2]])
-plt_dispersal <- unique(exp_deets[[1]])
-plt_noise <- unique(exp_deets[[3]])
-
-title_string <- paste0(
-  "Simulation results: \n",
-  plt_species,
-  " with ",
-  plt_dispersal,
-  " dispersal and ",
-  plt_noise,
-  " noise. \n"
-)
-
-### FUNCTION
-u_f_fmsys <- unique(bio_yield_df$f_fmsy)
+#| label: figure_5_6
+
+biom_ts_plt <- facet_plot_bm_ts_plots(
+  bio_yield_df = out_fs_brf_lp_mei,
+  biomass_thresh = med_biomass_brf,
+  yield_thresh = med_yield_brf,
+  exp_deets = brf_lp_mei_nice,
+  r_seed = 34,
+  frac_reserves = c(0, 0.25, 0.50),
+  f_fmsys = c(0, 0.5, 1.00, 2.)
+)
+
+yield_ts_plt <- facet_plot_yld_ts_plots(
+  bio_yield_df = out_fs_brf_lp_mei,
+  biomass_thresh = med_biomass_brf,
+  yield_thresh = med_yield_brf,
+  exp_deets = brf_lp_mei_nice,
+  r_seed = 34,
+  frac_reserves = c(0, 0.25, 0.50),
+  f_fmsys = c(0.5, 1.00, 2.)
+)
+
+print(yield_ts_plt)
+
+print(biom_ts_plt)
+
+ggsave(filename = "output/main_figs/fig5-biomass-timeseries-brf-lp-mei.png", plot = biom_ts_plt,
+       height = 8, width = 10)
+ggsave(filename = "output/main_figs/fig5-biomass-timeseries-brf-lp-mei.svg", plot = biom_ts_plt,
+       height = 8, width = 10)
+
+ggsave(filename = "output/main_figs/fig6-yield-timeseries-brf-lp-mei.png", plot = yield_ts_plt,
+       height = 8, width = 10)
+ggsave(filename = "output/main_figs/fig6-yield-timeseries-brf-lp-mei.svg", plot = yield_ts_plt,
+       height = 8, width = 10)
+
+```
+
+### Figure 5 with text
+
+```{r}
+#| label: fig_5_text
+### Biomass
+
+frac_reserves <- c(0, 0.25, 0.5)
+f_fmsys <- c(0, 0.5, 1.00, 2)
+
+u_f_fmsys <- unique(sum_stats_f_frac_df_brf_lp_mei[[2]]$f_fmsy)
 
   u_f_fmsys <-
-  purrr::map_dbl(f_fmsys_bio,  ~ u_f_fmsys[which.min(abs(u_f_fmsys - .x))])
-
-### FUNCTION
-bio_yield_sel_df <- bio_yield_df %>%
-  dplyr::mutate(reserve_frac = as.numeric(reserve_frac),
-                year = year - 500) %>%
-  dplyr::filter(sim_num == sim_2_use) %>%
-  dplyr::filter(reduce(map(
-    frac_reserves, near, x = reserve_frac, tol = 1e-4
-  ), `|`)) %>%
-  dplyr::filter(reduce(map(
-    u_f_fmsys, near, x = f_fmsy, tol = 1e-4
-  ), `|`)) %>%
-  dplyr::group_by(sim_num, reserve_frac, f_fmsy, year) %>%
-  dplyr::summarize(annual_biomass = sum(biomass_at_age),
-                   annual_yield = sum(yield),
-                   rel_annual_biomass = sum(biomass_at_age) / med_biomass,
-                   rel_annual_yield = sum(yield) / med_yield) %>%
-  dplyr::ungroup()
-
-### Biomass
-biom_ts_plt <- ggplot(
-  bio_yield_sel_df %>% dplyr::filter(sim_num == sim_2_use),
-  aes(x = year, y = rel_annual_biomass)
-  # aes(x = year, y = annual_biomass)
-) +
-  facet_grid(reserve_frac ~ f_fmsy,
-             labeller = labeller(f_fmsy = label_both,
-                                 reserve_frac = label_both)) +
-  # geom_ribbon(aes(
-  #   ymin = biomass_thresh,
-  #   ymax = pmin(annual_biomass, biomass_thresh),
-  #   fill = "Biomass lower"
-  # )) +
-    geom_ribbon(aes(
-    ymin = 1,
-    ymax = pmin(rel_annual_biomass, 1),
-    fill = "Biomass lower"
-  )) +
-  # geom_ribbon(aes(
-  #   ymin = annual_biomass,
-  #   ymax = pmin(annual_biomass, biomass_thresh),
-  #   fill = "Biomass higher"
-  # )) +
-    geom_ribbon(aes(
-    ymin = rel_annual_biomass,
-    ymax = pmin(rel_annual_biomass, 1),
-    fill = "Biomass higher"
-  )) +
-  geom_line(colour = "black") +
-    geom_segment(aes(x = 1, y = 1, 
-                     xend = 135, yend = 1),
-             colour = "red",
-             linewidth = 0.6) +
-  scale_fill_manual(values = c("black", "grey80")) +
-  # geom_text(
-  #   data = summary_stats_df,
-  #   x = x_text_val,
-  #   y = 11000,
-  #   aes(label = mean_biomass_lab)
-  # ) +
-  # geom_text(
-  #   data = summary_stats_df,
-  #   x = x_text_val,
-  #   y = 12500,
-  #   aes(label = sd_biomass_lab)
-# ) +
-# geom_text(
-#   data = summary_stats_df,
-#   x = x_text_val,
-#   y = 14000,
-#   aes(label = yrs_below_thresh)
-# ) +
-# geom_text(
-#   data = summary_stats_df,
-#   x = x_text_val,
-#   y = 9500,
-#   aes(label = cv_biomass_lab)
-# ) +
-labs(fill = "Above/Below Biomass threshold") +
-  ggtitle(title_string) +
-  xlab("Year") +
-  # ylab("Biomass (metric tons)") +
-  ylab("Relative Biomass") +
-  ylim(0, NA) +
-  labs(colour = "Reserve\nfraction") +
-  theme_bw() +
-  scale_x_continuous(expand = expansion(mult = 0, add = 0)) +
-  theme(
-    axis.line = element_line(colour = "black"),
-    panel.background = element_rect(fill = "white")#,
-    # panel.grid.major = element_blank(),
-    # panel.grid.minor = element_blank(),
-    # panel.border = element_blank()
-  )
-
-#### Yield
-yld_ts_plt <- bio_yield_sel_df %>%
-  dplyr::filter(f_fmsy != 0) %>%
-  ggplot(data = ., aes(x = year, y = rel_annual_yield)) +
-  facet_grid(reserve_frac ~ f_fmsy,
-             labeller = labeller(f_fmsy = label_both,
-                                 reserve_frac = label_both)) +
-  geom_ribbon(aes(
-    ymin = 1,
-    ymax = pmin(rel_annual_yield, 1),
-    fill = "Yield lower"
-  )) +
-  geom_ribbon(aes(
-    ymin = rel_annual_yield,
-    ymax = pmin(rel_annual_yield, 1),
-    fill = "Yield higher"
-  )) +
-  geom_line(colour = "black") +
-  geom_segment(aes(x = 1, y = 1, 
-                     xend = 135, yend = 1),
-             colour = "red",
-             linewidth = 0.6) +
-  scale_fill_manual(values = c("black", "grey80")) +
-  # geom_text(
-  #   data = summary_stats_df,
-  #   x = x_text_val,
-  #   y = 11000,
-  #   aes(label = mean_biomass_lab)
-  # ) +
-  # geom_text(
-  #   data = summary_stats_df,
-  #   x = x_text_val,
-  #   y = 12500,
-  #   aes(label = sd_biomass_lab)
-# ) +
-# geom_text(
-#   data = summary_stats_df,
-#   x = x_text_val,
-#   y = 14000,
-#   aes(label = yrs_below_thresh)
-# ) +
-# geom_text(
-#   data = summary_stats_df,
-#   x = x_text_val,
-#   y = 9500,
-#   aes(label = cv_biomass_lab)
-# ) +
-labs(fill = "Above/Below Yield threshold") +
-  ggtitle(title_string) +
-  xlab("Year") +
-  # ylab("Yield (metric tons)") +
-  ylab("Relative Yield") +
-  ylim(0, NA) +
-  labs(colour = "Reserve\nfraction") +
-  theme_bw() +
-  scale_x_continuous(expand = expansion(mult = 0, add = 0)) +
-  theme(
-    axis.line = element_line(colour = "black"),
-    panel.background = element_rect(fill = "white")#,
-    # panel.grid.major = element_blank(),
-    # panel.grid.minor = element_blank(),
-    # panel.border = element_blank()
-  )
-# }
-
-print(biom_ts_plt)
-print(yld_ts_plt)
-
-ggsave(filename = "output/tmp_figs/fig5-biomass-timeseries.png", plot = biom_ts_plt,
-       height = 8, width = 10)
-ggsave(filename = "output/tmp_figs/fig6-yield-timeseries.png", plot = yld_ts_plt,
-       height = 8, width = 10)
-
-ggsave(filename = "output/tmp_figs/fig5-biomass-timeseries.svg", plot = biom_ts_plt,
-       height = 8, width = 10)
-ggsave(filename = "output/tmp_figs/fig6-yield-timeseries.svg", plot = yld_ts_plt,
-       height = 8, width = 10)
-
-```
-
-### Figure 5 with text
-
-```{r}
-### Biomass
-
-summary_stats_df_plot <- summary_stats_df[[2]] %>%
+    purrr::map_dbl(f_fmsys,  ~ u_f_fmsys[which.min(abs(u_f_fmsys - .x))])
+
+summary_stats_df_plot_bm <- sum_stats_f_frac_df_brf_lp_mei[[2]] %>%
   dplyr::filter(reduce(map(
@@
 
-summary_stats_df_plot_yld <- summary_stats_df[[2]] %>%
+summary_stats_df_plot_yld <- sum_stats_f_frac_df_brf_lp_mei[[2]] %>%
   dplyr::filter(reduce(map(
@@
 
-biom_ts_plt <- ggplot(
-  bio_yield_sel_df %>% dplyr::filter(sim_num == sim_2_use),
-  aes(x = year, y = rel_annual_biomass)
-  # aes(x = year, y = annual_biomass)
-) +
-  facet_grid(reserve_frac ~ f_fmsy,
-             labeller = labeller(f_fmsy = label_both,
-                                 reserve_frac = label_both)) +
-  # geom_ribbon(aes(
-  #   ymin = biomass_thresh,
-  #   ymax = pmin(annual_biomass, biomass_thresh),
-  #   fill = "Biomass lower"
-  # )) +
-    geom_ribbon(aes(
-    ymin = 1,
-    ymax = pmin(rel_annual_biomass, 1),
-    fill = "Biomass lower"
-  )) +
-  # geom_ribbon(aes(
-  #   ymin = annual_biomass,
-  #   ymax = pmin(annual_biomass, biomass_thresh),
-  #   fill = "Biomass higher"
-  # )) +
-    geom_ribbon(aes(
-    ymin = rel_annual_biomass,
-    ymax = pmin(rel_annual_biomass, 1),
-    fill = "Biomass higher"
-  )) +
-  geom_line(colour = "black") +
-    geom_segment(aes(x = 1, y = 1, 
-                     xend = 135, yend = 1),
-             colour = "red",
-             linewidth = 0.6) +
-  scale_fill_manual(values = c("black", "grey80")) +
+# Location to place text
+x_text_val <- 135/2
+
+biom_ts_plt <- biom_ts_plt +
   geom_text(
-  data = summary_stats_df_plot,
+    data = summary_stats_df_plot_bm,
     x = x_text_val,
-  # y = 11000,
-  # aes(label = mean_biomass_lab)
     y = 3.4,
@@
   geom_text(
-  data = summary_stats_df_plot,
+    data = summary_stats_df_plot_bm,
     x = x_text_val,
-  # y = 12500,
-  # aes(label = sd_biomass_lab)
     y = 3.1,
@@
   geom_text(
-  data = summary_stats_df_plot,
+    data = summary_stats_df_plot_bm,
     x = x_text_val,
-  # y = 14000,
-  # aes(label = yrs_below_thresh)
     y = 2.8,
-  size = 3,
-  aes(label = yrs_below_biomass_thresh_lab)
-) +
-geom_text(
-  data = summary_stats_df_plot,
-  x = x_text_val,
-  # y = 9500,
-  # aes(label = cv_biomass_lab)  
-  y = 2.5,
     size = 3,
@@
   ) +
-labs(fill = "Above/Below Biomass threshold") +
-  ggtitle(title_string) +
-  xlab("Year") +
-  # ylab("Biomass (metric tons)") +
-  ylab("Relative Biomass") +
-  ylim(0, NA) +
-  labs(colour = "Reserve\nfraction") +
-  theme_bw() +
-  scale_x_continuous(expand = expansion(mult = 0, add = 0)) +
-  theme(
-    axis.line = element_line(colour = "black"),
-    panel.background = element_rect(fill = "white")#,
-    # panel.grid.major = element_blank(),
-    # panel.grid.minor = element_blank(),
-    # panel.border = element_blank()
-  )
-
-#### Yield
-# summary_stats_df_plot_yld
-
-yld_ts_plt <- bio_yield_sel_df %>%
-  dplyr::filter(f_fmsy != 0) %>%
-  ggplot(data = ., aes(x = year, y = rel_annual_yield)) +
-  facet_grid(reserve_frac ~ f_fmsy,
-             labeller = labeller(f_fmsy = label_both,
-                                 reserve_frac = label_both)) +
-  geom_ribbon(aes(
-    ymin = 1,
-    ymax = pmin(rel_annual_yield, 1),
-    fill = "Yield lower"
-  )) +
-  geom_ribbon(aes(
-    ymin = rel_annual_yield,
-    ymax = pmin(rel_annual_yield, 1),
-    fill = "Yield higher"
-  )) +
-  geom_line(colour = "black") +
-  geom_segment(aes(x = 1, y = 1, 
-                     xend = 135, yend = 1),
-             colour = "red",
-             linewidth = 0.6) +
-  scale_fill_manual(values = c("black", "grey80")) +
   geom_text(
-  # data = summary_stats_df,
+    data = summary_stats_df_plot_bm,
+    x = x_text_val,
+    y = 2.5,
+    size = 3,
+    aes(label = yrs_below_biomass_thresh_lab)
+  )
+
+print(biom_ts_plt)
+
+ggsave(
+  filename = "output/main_figs/fig5-biomass-timeseries-brf-lp-mei-text.png",
+  plot = biom_ts_plt,
+  height = 8,
+  width = 14
+)
+ggsave(
+  filename = "output/main_figs/fig5-biomass-timeseries-brf-lp-mei-text.svg",
+  plot = biom_ts_plt,
+  height = 8,
+  width = 14
+)
+
+```
+
+### Figure 6 with text
+
+```{r}
+#| label: figure_6_text
+
+# Yield
+
+yield_ts_plt <- yield_ts_plt +
+  geom_text(
     data = summary_stats_df_plot_yld,
     x = x_text_val,
-  # y = 11000,
-  # aes(label = mean_biomass_lab)
-  y = 2.45,
-  size = 3,
-  aes(label = mean_biomass_lab)
+    y = 1.9,
+    size = 2,
+    aes(label = mean_rel_yield_lab)
   ) +
   geom_text(
-  # data = summary_stats_df,
     data = summary_stats_df_plot_yld,
     x = x_text_val,
-  # y = 12500,
-  # aes(label = sd_biomass_lab)
-  y = 2.2,
-  size = 3, 
+    y = 1.8,
+    size = 2,
     aes(label = sd_rel_yield_lab)
@@
   geom_text(
-  # data = summary_stats_df,
     data = summary_stats_df_plot_yld,
     x = x_text_val,
-  # y = 14000,
-  y = 1.95,
-  size = 3,
-  aes(label = yrs_below_yield_thresh_lab)
+    y = 1.7,
+    size = 2,
+    aes(label = cv_rel_yield_lab)
   ) +
   geom_text(
-  # data = summary_stats_df,
     data = summary_stats_df_plot_yld,
     x = x_text_val,
-  # y = 9500,
-  # aes(label = cv_yield_lab)
-  y = 1.7,
-  size = 3,
-  aes(label = cv_rel_yield_lab)
-) +
-labs(fill = "Above/Below Yield threshold") +
-  ggtitle(title_string) +
-  xlab("Year") +
-  # ylab("Yield (metric tons)") +
-  ylab("Relative Yield") +
-  ylim(0, 2.6) +
-  labs(colour = "Reserve\nfraction") +
-  theme_bw() +
-  scale_x_continuous(expand = expansion(mult = 0, add = 0)) +
-  theme(
-    axis.line = element_line(colour = "black"),
-    panel.background = element_rect(fill = "white")#,
-    # panel.grid.major = element_blank(),
-    # panel.grid.minor = element_blank(),
-    # panel.border = element_blank()
-  )
-# }
-
-print(biom_ts_plt)
-print(yld_ts_plt)
-
-ggsave(filename = "output/tmp_figs/fig5-biomass-timeseries-text.png", plot = biom_ts_plt,
-       height = 8, width = 14)
-ggsave(filename = "output/tmp_figs/fig6-yield-timeseries-text.png", plot = yld_ts_plt,
-       height = 8, width = 14)
-
-ggsave(filename = "output/tmp_figs/fig5-biomass-timeseries-text.svg", plot = biom_ts_plt,
-       height = 8, width = 14)
-ggsave(filename = "output/tmp_figs/fig6-yield-timeseries-text.svg", plot = yld_ts_plt,
-       height = 8, width = 14)
-```
-
-### Figure 6
-
-Representative timeseries of fishery yield under different combinations of fishing rate and marine reserve protection.
-
-Species: Blue rockfish
-
-Dispersal: Larval pool
-
-Environmental noise: ENSO (MEI)
-
-```{r}
-#| label: figure_6
+    y = 1.6,
+    size = 2,
+    aes(label = yrs_below_yield_thresh_lab)
+  )
+
+print(yield_ts_plt)
+
+ggsave(
+  filename = "output/main_figs/fig6-yield-timeseries-brf-lp-mei-text.png",
+  plot = yield_ts_plt,
+  height = 8,
+  width = 14
+)
+ggsave(
+  filename = "output/main_figs/fig6-yield-timeseries-brf-lp-mei-text.svg",
+  plot = yield_ts_plt,
+  height = 8,
+  width = 14
+)
 
@@
 
-u_f_fmsys <- unique(bio_yield_df$f_fmsy)
-
-f_fmsys_targs <- c(0.52, 1.00, 2.09)
+u_f_fmsys <- unique(out_fs_brf_lp_mei$f_fmsy)
+
+f_fmsys_targs <- c(0.5, 1.00, 2.)
 
@@
 
-recs_spec_disp_noise_ffmsy_plt <- bio_yield_df %>%
+recs_spec_disp_noise_ffmsy_plt <- out_fs_brf_lp_mei %>%
   dplyr::filter(sim_num == 1, age == 1) %>%
@@
 
-yield_spec_disp_noise_prep_plt <- bio_yield_df %>% 
+yield_spec_disp_noise_prep_plt <- out_fs_brf_lp_mei %>% 
   dplyr::filter(sim_num == 1) %>%
@@
 ggsave(
-  filename = "output/tmp_figs/fig7-lagged-recs-yield-timeseries-lw.png",
+  filename = "output/main_figs/fig7-lagged-recs-yield-timeseries-lw-brf-lp-mei.png",
   plot = lagged_recs_yield_plt,
@@
 ggsave(
-  filename = "output/tmp_figs/fig7-lagged-recs-yield-timeseries-lw.svg",
+  filename = "output/main_figs/fig7-lagged-recs-yield-timeseries-lw-brf-lp-mei.svg",
   plot = lagged_recs_yield_plt,
@@
 # use species specific vB params to create a weight at age data.frame that can be used to convert abundance at age to biomass at age
-species_name <- brf_mei_nd_nice[[2]]
+species_name <- brf_nd_mei_nice[[2]]
 brf_waa_g <- sim_species_parms[[species_name]][["biom_const"]] * sim_species_derived_vars[[species_name]][["length_at_age"]] ^

### 2023-12-23 ms_figures_supp_figs.qmd
clean up supp figure plots

@@
 
-### Figure 3 - white noise check
-
-Contour plots showing the buffering effects of harvest rate and marine reserves on the abundance of a fished population, when there is no larval dispersal between the fished and reserve habitat patches.
-
-Species: Blue rockfish
-
-Dispersal: no dispersal
-
-Environmental noise: white noise
-
-```{r}
-
-```
-
-### Figure 4 - white noise check
-
-Contour plots showing the buffering effects of harvest rate and marine reserves on the abundance of a fished population, when there is larval pool dispersal between the fished and reserve habitat patches.
-
-Species: Blue rockfish
-
-Dispersal: Larval Pool Dispersal
-
-Environmental noise: White
-
-```{r}
-
-# 
-# ggsave(filename = "output/tmp_figs/fig4-yield-white-noise-chk.png", plot = p1)
-# ggsave(filename = "output/tmp_figs/fig4-biomass-white-noise-chk.png", plot = p2)
-
-```
-
-### Cabezon
-
-```{r}
-# # Set table names to be used to make the main figures
-# 
-# table_name_nd <- "no_dispersal_cabezon_mei_135_75"
-# table_name_lp <- "larval_pool_cabezon_mei_135_75"
-# table_name_nd_white <- "no_dispersal_abezon_white_135_75"
-# table_name_lp_white <- "larval_pool_cabezon_white_135_75"
-# 
-# # Get meta data descriptins from the table names and the pretty 
-# # versions for plotting
-# 
-# cab_mei_nd_current <- get_current_exp(table_name = table_name_nd)
-# cab_mei_nd_nice <- get_nice_exp(table_name = table_name_nd)
-# cab_white_nd_current <- get_current_exp(table_name = table_name_nd_white)
-# cab_white_nd_nice <- get_nice_exp(table_name = table_name_nd_white)
-# cab_mei_lp_current <- get_current_exp(table_name = table_name_lp)
-# cab_mei_lp_nice <- get_nice_exp(table_name = table_name_lp)
-# cab_white_lp_current <- get_current_exp(table_name = table_name_lp_white)
-# cab_white_lp_nice <- get_nice_exp(table_name = table_name_lp_white)
-#
-
-```
-
-### Figure 3 - MEI Cabezon
-
-Contour plots showing the buffering effects of harvest rate and marine reserves on the abundance of a fished population, when there is no larval dispersal between the fished and reserve habitat patches.
-
-Species: Cabezon
-
-Dispersal: No Dispersal
-
-Environmental noise: ENSO (MEI)
-
-```{r}
-#| label: figure_3
-# 
-# # use species specific vB params to create a weight at age data.frame that can be used to convert abundance at age to biomass at age
-# species_name <- cab_mei_nd_nice[[2]]
-# brf_waa_g <- sim_species_parms[[species_name]][["biom_const"]] * sim_species_derived_vars[[species_name]][["length_at_age"]] ^
-#                     sim_species_parms[[species_name]][["biom_exp"]]
-# 
-# brf_waa_g_df <- data.frame(age = 1: sim_species_parms[[species_name]]$A_max,
-#                            waa_g = brf_waa_g)
-# 
-# # use functions to create useful data structures
-# # FLEP to F reference tables by species
-# spec_fleps_2_fs <-
-#   get_fs_from_fleps(species = species_name,
-#                     flep_inds = species_flep_fished_ind,
-#                     f_vals =  fishing_mortality_values) 
-# 
-# ## Qry 
-# qry <- paste0("SELECT  sim_num, reserve_frac, flep_ratio, year, age, 
-#               sum(number) as abundance,
-#               sum(yield) as yield,
-#               FROM '", table_name_nd, 
-#               "' WHERE sim_num IN (", toString(sims_2_use), ") AND year > 500 
-#               GROUP BY sim_num, reserve_frac, flep_ratio, year, age
-#               ORDER BY sim_num, reserve_frac, flep_ratio, year, age
-#               ")
-# 
-# sim_res_out <- dbGetQuery(conn = con, qry)
-# 
-# #######
-# 
-# 
-# ########### PIPELINING
-# F_brf_maxes_yield <- get_f_maxes_yield(input_df = sim_res_out,
-#                                          fleps_2_fs = spec_fleps_2_fs)
-# F_brf_maxes_yield
-# 
-# out_fs <- df_add_fs_out (input_df = sim_res_out,
-#                          spec_fleps_2_fs = spec_fleps_2_fs,
-#                          F_maxes_yield = F_brf_maxes_yield, waa_g_df = brf_waa_g_df)
-# out_fs
-# 
-# med_yield <- get_median_yield(input_df = out_fs) 
-# med_yield
-# 
-# med_biomass <- get_median_biomass(input_df = out_fs, age_mat = sim_species_parms$`Blue rockfish`$A_mat)
-# med_biomass
-# 
-# out_yld_bm_sims_f_frac_yr <-
-#   df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs,
-#                                      age_mat = sim_species_parms$`Blue rockfish`$A_mat)#, sims_num_2_use = sims_2_use
-# 
-# # out_yld_bm_sims_f_frac_yr
-# # pipeline works to here
-# 
-# sum_stats_f_frac_df <-
-#   summary_stats_by_f_frac(
-#     out_sim_f_frac_yr = out_yld_bm_sims_f_frac_yr,
-#     median_yield = med_yield,
-#     median_biomass = med_biomass
-#   )
-# sum_stats_f_frac_df
-# 
-# ## Plotting
-# 
-# p1 <- sum_stats_f_frac_df[[2]] %>%
-#   filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
-#   ggplot(.,
-#        aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_yield_thresh)) +
-#   metR::geom_contour_fill(bins = 12) + 
-#   ggtitle(paste0(
-#         cab_mei_nd_nice[[2]],
-#         " ",
-#         cab_mei_nd_nice[[1]],
-#         " ",
-#         cab_mei_nd_nice[[3]],
-#         ":\nTime below median max yield"
-#       )) +
-#       xlab("Fraction of coastline in reserves") +
-#       ylab("Harvest Rate (F/Fmsy)") +
-#       scale_fill_viridis_c(option = "D", direction = -1) +
-#       geom_segment(aes(
-#         x = 0,
-#         xend = max_reserve_frac,
-#         y = 1,
-#         yend = 1
-#       ), colour = "black",
-#       linetype = 2) +
-#       scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
-#       scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
-#       theme_bw()
-# 
-# 
-# p2 <- sum_stats_f_frac_df[[2]] %>%
-#   filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
-#   ggplot(.,
-#        aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_biomass_thresh)) +
-#   metR::geom_contour_fill(bins = 12) +
-#   ggtitle(paste0(
-#         cab_mei_nd_nice[[2]],
-#         " ",
-#         cab_mei_nd_nice[[1]],
-#         " ",
-#         cab_mei_nd_nice[[3]],
-#         ":\nTime below mean median biomass "
-#       )) +
-#       xlab("Fraction of coastline in reserves") +
-#       ylab("Harvest Rate (F/Fmsy)") +
-#       scale_fill_viridis_c(option = "D", direction = -1) +
-#       geom_segment(aes(
-#         x = 0,
-#         xend = max_reserve_frac,
-#         y = 1,
-#         yend = 1
-#       ), colour = "black",
-#       linetype = 2) +
-#       scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
-#       scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
-#       theme_bw()
-# 
-# print(p1)
-# print(p2)
-
-# ggsave(filename = "output/tmp_figs/fig3-yield-cab.png", plot = p1)
-# ggsave(filename = "output/tmp_figs/fig3-biomass-cab.png", plot = p2)
-
-```
-
-### Better funcs
+### Supplemental figure prep
 
@@
 
-########### PIPELINING
-
 F_chr_nd_white_df_maxes_yield <- get_f_maxes_yield(input_df = chr_nd_white_df,
                                          fleps_2_fs = spec_fleps_2_fs_chr)
-F_chr_nd_white_df_maxes_yield
 
@@
                                          fleps_2_fs = spec_fleps_2_fs_cab)
-F_cab_nd_white_df_maxes_yield
 
@@
                                          fleps_2_fs = spec_fleps_2_fs_chr)
-F_chr_lp_white_df_maxes_yield
 
@@
                                          fleps_2_fs = spec_fleps_2_fs_cab)
-F_cab_lp_white_df_maxes_yield
 
@@
                                                  fleps_2_fs = spec_fleps_2_fs_chr)
-F_chr_nd_mei_df_maxes_yield
 
@@
                                                  fleps_2_fs = spec_fleps_2_fs_cab)
-F_cab_nd_mei_df_maxes_yield
 
@@
                                                  fleps_2_fs = spec_fleps_2_fs_chr)
-F_chr_lp_mei_df_maxes_yield
 
@@
                                                  fleps_2_fs = spec_fleps_2_fs_cab)
-F_cab_lp_mei_df_maxes_yield
 
@@
                          waa_g_df = chr_waa_g_df)
-chr_nd_white_out_fs[1:6,]
 
@@
                          waa_g_df = cab_waa_g_df)
-cab_nd_white_out_fs[1:6,]
 # enso
@@
                          waa_g_df = chr_waa_g_df)
-chr_nd_mei_out_fs[1:6,]
 
@@
                          waa_g_df = cab_waa_g_df)
-cab_nd_mei_out_fs[1:6,]
 
@@
                          waa_g_df = chr_waa_g_df)
-chr_lp_white_out_fs[1:6,]
 
@@
                          waa_g_df = cab_waa_g_df)
-cab_lp_white_out_fs[1:6,]
+
 # enso
@@
                          waa_g_df = chr_waa_g_df)
-chr_lp_mei_out_fs[1:6,]
 
@@
                          waa_g_df = cab_waa_g_df)
-cab_lp_mei_out_fs[1:6,]
-
-##----##
 
@@
 chr_nd_white_med_yield <- get_median_yield(input_df = chr_nd_white_out_fs)
-chr_nd_white_med_yield
+
 cab_nd_white_med_yield <- get_median_yield(input_df = cab_nd_white_out_fs)
-cab_nd_white_med_yield
+
 # larval pool dispersal 
 chr_lp_white_med_yield <- get_median_yield(input_df = chr_lp_white_out_fs)
-chr_lp_white_med_yield
+
 cab_lp_white_med_yield <- get_median_yield(input_df = cab_lp_white_out_fs)
-cab_lp_white_med_yield
 
@@
 chr_nd_mei_med_yield <- get_median_yield(input_df = chr_nd_mei_out_fs)
-chr_nd_mei_med_yield
+
 cab_nd_mei_med_yield <- get_median_yield(input_df = cab_nd_mei_out_fs)
-cab_nd_mei_med_yield
+
 # larval pool dispersal
 chr_lp_mei_med_yield <- get_median_yield(input_df = chr_lp_mei_out_fs)
-chr_lp_mei_med_yield
+
 cab_lp_mei_med_yield <- get_median_yield(input_df = cab_lp_mei_out_fs)
-cab_lp_mei_med_yield
-
-##----##
-
-med_biomass <- get_median_biomass(input_df = out_fs)
 
@@
 chr_nd_white_med_biomass <- get_median_biomass(input_df = chr_nd_white_out_fs)
-chr_nd_white_med_biomass
+
 cab_nd_white_med_biomass <- get_median_biomass(input_df = cab_nd_white_out_fs)
-cab_nd_white_med_biomass
-# larval pool dispersal 
+
 chr_lp_white_med_biomass <- get_median_biomass(input_df = chr_lp_white_out_fs)
-chr_lp_white_med_biomass
+
 cab_lp_white_med_biomass <- get_median_biomass(input_df = cab_lp_white_out_fs)
-cab_lp_white_med_biomass
 
@@
 chr_nd_mei_med_biomass <- get_median_biomass(input_df = chr_nd_mei_out_fs)
-chr_nd_mei_med_biomass
+
 cab_nd_mei_med_biomass <- get_median_biomass(input_df = cab_nd_mei_out_fs)
-cab_nd_mei_med_biomass
+
 # larval pool dispersal
 chr_lp_mei_med_biomass <- get_median_biomass(input_df = chr_lp_mei_out_fs)
-chr_lp_mei_med_biomass
+
 cab_lp_mei_med_biomass <- get_median_biomass(input_df = cab_lp_mei_out_fs)
-cab_lp_mei_med_biomass
-
-##----##
 
@@
 
+p1 <-
+  plot_contour_bm_below_thresh(sum_stats_f_frac_df = ,
+                               spec_disp_noise = )
+
+p2 <-
+  plot_contour_yld_below_thresh(sum_stats_f_frac_df = ,
+                                spec_disp_noise = )
+
 con <- DBI::dbConnect(duckdb::duckdb(),
@@
 
-#######
-
-########### PIPELINING
 F_brf_maxes_yield <- get_f_maxes_yield(input_df = sim_res_out,
@@
 
-ggsave(filename = "output/tmp_figs/sup_fig1-brf-biomass-yield-white-nd-lp.png", 
+ggsave(filename = "output/supp_figs/sup_fig1-brf-biomass-yield-white-nd-lp.png", 
        plot = p_s1, 
@@
        height = 8)
-ggsave(filename = "output/tmp_figs/sup_fig1-brf-biomass-yield-white-nd-lp.svg", 
+ggsave(filename = "output/supp_figs/sup_fig1-brf-biomass-yield-white-nd-lp.svg", 
        plot = p_s1, 
@@
 print(p_s2)
-ggsave(filename = "output/tmp_figs/sup-fig2-cab-chr-nodisp-mei-yld-biom.png", 
+ggsave(filename = "output/supp_figs/sup-fig2-cab-chr-nodisp-mei-yld-biom.png", 
        plot = p_s2, 
@@
        height = 8)
-ggsave(filename = "output/tmp_figs/sup-fig2-cab-chr-nodisp-mei-yld-biom.svg", 
+ggsave(filename = "output/supp_figs/sup-fig2-cab-chr-nodisp-mei-yld-biom.svg", 
        plot = p_s2, 
@@
 print(p_s3)
-ggsave(filename = "output/tmp_figs/sup-fig3-cab-chr-lp-disp-mei-yld-biom.png", 
+ggsave(filename = "output/supp_figs/sup-fig3-cab-chr-lp-disp-mei-yld-biom.png", 
        plot = p_s3, 
@@
        height = 8)
-ggsave(filename = "output/tmp_figs/sup-fig3-cab-chr-lp-disp-mei-yld-biom.svg", 
+ggsave(filename = "output/supp_figs/sup-fig3-cab-chr-lp-disp-mei-yld-biom.svg", 
        plot = p_s3, 

### 2023-12-24 ms_figures_supp_figs.qmd
Clean docs (#1)
* refactor all code for main figs to streamline and/or use functions

* clean up supp figure plots

* finish refactor of ms_figures_supp_figs.qmd

@@
 #| label: figure_4
-
-# # use species specific vB params to create a weight at age data.frame that can be used to convert abundance at age to biomass at age
-# species_name <- brf_mei_lp_nice[[2]]
-# brf_waa_g <- sim_species_parms[[species_name]][["biom_const"]] * sim_species_derived_vars[[species_name]][["length_at_age"]] ^
-#                     sim_species_parms[[species_name]][["biom_exp"]]
-# 
-# brf_waa_g_df <- data.frame(age = 1: sim_species_parms[[species_name]]$A_max,
-#                            waa_g = brf_waa_g)
-# 
-# # use functions to create useful data structures
-# # FLEP to F reference tables by species
-# spec_fleps_2_fs <-
-#   get_fs_from_fleps(species = species_name,
-#                     flep_inds = species_flep_fished_ind,
-#                     f_vals =  fishing_mortality_values)
 
@@
 # Species: Blue rockfish
-# Dispersal: No Dispersal
+# Dispersal: No Dispersal/Larval Pool
 # Environmental noise: White
 
+sim_res_out_brf_nd_white <-
+  qry_get_sim_data_for_analysis(table_name = table_name_brf_nd_white)
+sim_res_out_brf_lp_white <-
+  qry_get_sim_data_for_analysis(table_name = table_name_brf_lp_white)
+
+F_brf_maxes_yield_brf_nd_white <-
+  get_f_maxes_yield(input_df = sim_res_out_brf_nd_white,
+                    fleps_2_fs = spec_fleps_2_fs_brf)
+F_brf_maxes_yield_brf_lp_white <-
+  get_f_maxes_yield(input_df = sim_res_out_brf_lp_white,
+                    fleps_2_fs = spec_fleps_2_fs_brf)
+
+out_fs_brf_nd_white <- df_add_fs_out(
+  input_df = sim_res_out_brf_nd_white,
+  spec_fleps_2_fs = spec_fleps_2_fs_brf,
+  F_maxes_yield = F_brf_maxes_yield_brf_nd_white,
+  waa_g_df = brf_waa_g_df
+)
+out_fs_brf_lp_white <- df_add_fs_out(
+  input_df = sim_res_out_brf_lp_white,
+  spec_fleps_2_fs = spec_fleps_2_fs_brf,
+  F_maxes_yield = F_brf_maxes_yield_brf_lp_white,
+  waa_g_df = brf_waa_g_df
+)
+
+med_yield_brf <- get_median_yield(input_df = out_fs_brf_nd_white)
+
+med_biomass_brf <- get_median_biomass(input_df = out_fs_brf_nd_white)
+
+out_yld_bm_sims_f_frac_yr_brf_nd_white <-
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs_brf_nd_white)
+out_yld_bm_sims_f_frac_yr_brf_lp_white <-
+  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs_brf_lp_white)
+
+sum_stats_f_frac_df_brf_nd_white <-
+  summary_stats_by_f_frac(
+    out_sim_f_frac_yr = out_yld_bm_sims_f_frac_yr_brf_nd_white,
+    median_yield = med_yield_brf,
+    median_biomass = med_biomass_brf
+  )
+sum_stats_f_frac_df_brf_lp_white <-
+  summary_stats_by_f_frac(
+    out_sim_f_frac_yr = out_yld_bm_sims_f_frac_yr_brf_lp_white,
+    median_yield = med_yield_brf,
+    median_biomass = med_biomass_brf
+  )
+
+## Plotting
 p1 <-
-  plot_contour_bm_below_thresh(sum_stats_f_frac_df = ,
-                               spec_disp_noise = )
+  plot_contour_bm_below_thresh(sum_stats_f_frac_df = sum_stats_f_frac_df_brf_nd_white,
+                               spec_disp_noise = brf_nd_white_nice)
 
 p2 <-
-  plot_contour_yld_below_thresh(sum_stats_f_frac_df = ,
-                                spec_disp_noise = )
-
-con <- DBI::dbConnect(duckdb::duckdb(),
-                        dbdir = "data/sim_out.duckdb",
-                        read_only = FALSE)
-
-# use species specific vB params to create a weight at age data.frame that can be used to convert abundance at age to biomass at age
-species_name <- brf_nd_mei_nice[[2]]
-brf_waa_g <- sim_species_parms[[species_name]][["biom_const"]] * sim_species_derived_vars[[species_name]][["length_at_age"]] ^
-                    sim_species_parms[[species_name]][["biom_exp"]]
-
-brf_waa_g_df <- data.frame(age = 1: sim_species_parms[[species_name]]$A_max,
-                           waa_g = brf_waa_g)
-
-# use functions to create useful data structures
-# FLEP to F reference tables by species
-spec_fleps_2_fs <-
-  get_fs_from_fleps(species = species_name,
-                    flep_inds = species_flep_fished_ind,
-                    f_vals =  fishing_mortality_values)
-
-## Qry 
-qry <- paste0("SELECT  sim_num, reserve_frac, flep_ratio, year, age, 
-              sum(number) as abundance,
-              sum(yield) as yield,
-              FROM '", table_name_nd_white, 
-              "' WHERE sim_num IN (", toString(sims_2_use), ") AND year > 500 
-              GROUP BY sim_num, reserve_frac, flep_ratio, year, age
-              ORDER BY sim_num, reserve_frac, flep_ratio, year, age
-              ")
-
-sim_res_out <- dbGetQuery(conn = con, qry)
-
-F_brf_maxes_yield <- get_f_maxes_yield(input_df = sim_res_out,
-                                         fleps_2_fs = spec_fleps_2_fs)
-F_brf_maxes_yield
-
-out_fs <- df_add_fs_out (input_df = sim_res_out,
-                         spec_fleps_2_fs = spec_fleps_2_fs,
-                         F_maxes_yield = F_brf_maxes_yield, waa_g_df = brf_waa_g_df)
-out_fs
-
-med_yield <- get_median_yield(input_df = out_fs) 
-med_yield
-
-med_biomass <- get_median_biomass(input_df = out_fs, age_mat = sim_species_parms$`Blue rockfish`$A_mat)
-med_biomass
-
-out_yld_bm_sims_f_frac_yr <-
-  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs,
-                                     age_mat = sim_species_parms$`Blue rockfish`$A_mat)#, sims_num_2_use = sims_2_use
-
-# out_yld_bm_sims_f_frac_yr
-# pipeline works to here
-
-sum_stats_f_frac_df <-
-  summary_stats_by_f_frac(
-    out_sim_f_frac_yr = out_yld_bm_sims_f_frac_yr,
-    median_yield = med_yield,
-    median_biomass = med_biomass
-  )
-sum_stats_f_frac_df
-
-## Plotting
-
-p1 <- sum_stats_f_frac_df[[2]] %>%
-  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
-  ggplot(.,
-       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_biomass_thresh)) +
-  metR::geom_contour_fill(bins = 12) +
-  ggtitle(paste0(
-        brf_white_nd_nice[[2]],
-        " ",
-        brf_white_nd_nice[[1]],
-        " ",
-        brf_white_nd_nice[[3]],
-        ":\nTime below mean median biomass "
-      )) +
-      xlab("Fraction of coastline in reserves") +
-      ylab("Harvest Rate (F/Fmsy)") +
-      scale_fill_viridis_c(option = "D", direction = -1) +
-      geom_segment(aes(
-        x = 0,
-        xend = max_reserve_frac,
-        y = 1,
-        yend = 1
-      ), colour = "black",
-      linetype = 2) +
-      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
-      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
-      theme_bw()
-
-p2 <- sum_stats_f_frac_df[[2]] %>%
-  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
-  ggplot(.,
-       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_yield_thresh)) +
-  metR::geom_contour_fill(bins = 12) + 
-  ggtitle(paste0(
-        brf_white_nd_nice[[2]],
-        " ",
-        brf_white_nd_nice[[1]],
-        " ",
-        brf_white_nd_nice[[3]],
-        ":\nTime below median max yield"
-      )) +
-      xlab("Fraction of coastline in reserves") +
-      ylab("Harvest Rate (F/Fmsy)") +
-      scale_fill_viridis_c(option = "D", direction = -1) +
-      geom_segment(aes(
-        x = 0,
-        xend = max_reserve_frac,
-        y = 1,
-        yend = 1
-      ), colour = "black",
-      linetype = 2) +
-      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
-      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
-      theme_bw()
-
-# Species: Blue rockfish
-# Dispersal: Larval Pool Dispersal
-# Environmental noise: White
-# use species specific vB params to create a weight at age data.frame that can be used to convert abundance at age to biomass at age
-species_name <- brf_mei_lp_nice[[2]]
-brf_waa_g <- sim_species_parms[[species_name]][["biom_const"]] * sim_species_derived_vars[[species_name]][["length_at_age"]] ^
-                    sim_species_parms[[species_name]][["biom_exp"]]
-
-brf_waa_g_df <- data.frame(age = 1: sim_species_parms[[species_name]]$A_max,
-                           waa_g = brf_waa_g)
-
-# use functions to create useful data structures
-# FLEP to F reference tables by species
-spec_fleps_2_fs <-
-  get_fs_from_fleps(species = species_name,
-                    flep_inds = species_flep_fished_ind,
-                    f_vals =  fishing_mortality_values)
-
-## Qry 
-qry <- paste0("SELECT  sim_num, reserve_frac, flep_ratio, year, age, 
-              sum(number) as abundance,
-              sum(yield) as yield,
-              FROM '", table_name_lp_white, 
-              "' WHERE sim_num IN (", toString(sims_2_use), ") AND year > 500 
-              GROUP BY sim_num, reserve_frac, flep_ratio, year, age
-              ORDER BY sim_num, reserve_frac, flep_ratio, year, age
-              ")
-
-sim_res_out <- dbGetQuery(conn = con, qry)
-
-#######
-
-########### PIPELINING
-F_brf_maxes_yield <- get_f_maxes_yield(input_df = sim_res_out,
-                                         fleps_2_fs = spec_fleps_2_fs)
-F_brf_maxes_yield
-
-out_fs <- df_add_fs_out (input_df = sim_res_out,
-                         spec_fleps_2_fs = spec_fleps_2_fs,
-                         F_maxes_yield = F_brf_maxes_yield, waa_g_df = brf_waa_g_df)
-out_fs
-
-med_yield <- get_median_yield(input_df = out_fs) 
-med_yield
-
-med_biomass <- get_median_biomass(input_df = out_fs,
-                                  age_mat = sim_species_parms$`Blue rockfish`$A_mat)
-med_biomass
-
-out_yld_bm_sims_f_frac_yr <-
-  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs, 
-                                     age_mat = sim_species_parms$`Blue rockfish`$A_mat)
-
-# pipeline works to here
-
-sum_stats_f_frac_df <-
-  summary_stats_by_f_frac(
-    out_sim_f_frac_yr = out_yld_bm_sims_f_frac_yr,
-    median_yield = med_yield,
-    median_biomass = med_biomass
-  )
-sum_stats_f_frac_df
-
-## Plotting
-
-p3 <- sum_stats_f_frac_df[[2]] %>%
-  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
-  ggplot(.,
-       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_biomass_thresh)) +
-  metR::geom_contour_fill(bins = 12) +
-  ggtitle(paste0(
-        brf_white_lp_nice[[2]],
-        " ",
-        brf_white_lp_nice[[1]],
-        " ",
-        brf_white_lp_nice[[3]],
-        ":\nTime below mean median biomass "
-      )) +
-      xlab("Fraction of coastline in reserves") +
-      ylab("Harvest Rate (F/Fmsy)") +
-      scale_fill_viridis_c(option = "D", direction = -1) +
-      geom_segment(aes(
-        x = 0,
-        xend = max_reserve_frac,
-        y = 1,
-        yend = 1
-      ), colour = "black",
-      linetype = 2) +
-      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
-      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
-      theme_bw()
-
-p4 <- sum_stats_f_frac_df[[2]] %>%
-  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
-  ggplot(.,
-       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_yield_thresh)) +
-  metR::geom_contour_fill(bins = 12) + 
-  ggtitle(paste0(
-        brf_white_lp_nice[[2]],
-        " ",
-        brf_white_lp_nice[[1]],
-        " ",
-        brf_white_lp_nice[[3]],
-        ":\nTime below median max yield"
-      )) +
-      xlab("Fraction of coastline in reserves") +
-      ylab("Harvest Rate (F/Fmsy)") +
-      scale_fill_viridis_c(option = "D", direction = -1) +
-      geom_segment(aes(
-        x = 0,
-        xend = max_reserve_frac,
-        y = 1,
-        yend = 1
-      ), colour = "black",
-      linetype = 2) +
-      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
-      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
-      theme_bw()
-
-# print(p1)
-# print(p2)
-# print(p3)
-# print(p4)
-
-p_s1 <- plot_grid(p1, p2, p3, p4, labels = letters[1:4], label_size = 9, byrow = FALSE)
+  plot_contour_yld_below_thresh(sum_stats_f_frac_df = sum_stats_f_frac_df_brf_nd_white,
+                                spec_disp_noise = brf_nd_white_nice)
+p3 <-
+  plot_contour_bm_below_thresh(sum_stats_f_frac_df = sum_stats_f_frac_df_brf_lp_white,
+                               spec_disp_noise = brf_lp_white_nice)
+
+p4 <-
+  plot_contour_yld_below_thresh(sum_stats_f_frac_df = sum_stats_f_frac_df_brf_lp_white,
+                                spec_disp_noise = brf_lp_white_nice)
+p_s1 <-
+  plot_grid(
+    p1,
+    p2,
+    p3,
+    p4,
+    labels = letters[1:4],
+    label_size = 9,
+    byrow = FALSE
+  )
 
@@
 
-DBI::dbDisconnect(conn = con, shutdown=TRUE)
+# DBI::dbDisconnect(conn = con, shutdown=TRUE)
 
@@
 
-print(p1)
-print(p2)
-
 ### Cabezon
@@
 
-### Supp Fig 4
-
-Yield contours for Cabezon and China rockfish
-
--   white noise (or do we want ENSO?) --- white vs ENSO
-
--   Larval pool dispersal
-
-```{r}
-#| label: supp_fig_4
-#| 
-```
+###

### 2023-12-24 R/functions.R

@@ -1415,3 +1415,389 @@ summary_stats_by_f_frac <- function(out_sim_f_frac_yr,
   return(list(sim_f_frac_df, summ_f_frac_df))
 }
 
+#' Retrieves simulation data from a DuckDB database table for subequent analyses
+#'
+#' @param table_name The name of the DuckDb table containing the simulation data.
+#'
+#' @return A data frame containing the retrieved simulation data, with columns:
+#' \itemize{
+#'   \item sim_num
+#'   \item reserve_frac
+#'   \item flep_ratio
+#'   \item year
+#'   \item age
+#'   \item abundance
+#'   \item yield
+#' }
+#'
+#' @details This function retrieves simulation data for years after a 500 yr burn-in period,
+#' aggregates results from both the fished and unfished patches and returns
+#'the results by simulation number, reserve fraction, FLEP ratio, year, and age.
+#'
+#' @examples
+#' table_name_brf_nd_mei <- "no_dispersal_blue_rockfish_mei_135_75"
+#' sim_data <- qry_get_sim_data_for_analysis(table_name = table_name_brf_nd_mei)
+#'
+#' @export
+
+qry_get_sim_data_for_analysis <- function(table_name) {
+    con <- DBI::dbConnect(duckdb::duckdb(),
+                          dbdir = "data/sim_out.duckdb",
+                          read_only = TRUE)
+    
+    qry <- paste0("SELECT  sim_num, reserve_frac, flep_ratio, year, age, 
+              sum(number) as abundance,
+              sum(yield) as yield,
+              FROM '", table_name, 
+                  "' WHERE year > 500 
+              GROUP BY sim_num, reserve_frac, flep_ratio, year, age
+              ORDER BY sim_num, reserve_frac, flep_ratio, year, age
+              ")
+    
+    sim_res_out <- dbGetQuery(conn = con, qry)
+    
+    DBI::dbDisconnect(conn = con)
+    
+    return(sim_res_out)
+  }
+
+#' Creates a contour plot of the fraction of years below a biomass threshold.
+#'
+#' @param sum_stats_f_frac_df A list of data frames where the second element 
+#'                            holds the data for the contour plot.
+#' @param spec_disp_noise_nice A list containing strings used for constructing the plot title.
[…]

### 2023-12-24 _targets.R

@@ -4,6 +4,7 @@ source(file.path("R", "functions.R"))
 options(tidyverse.quiet = TRUE)
 tar_option_set(
   packages = c(
+    "renv",
     "tidyverse",
     "data.table",
     "duckdb",

### 2024-01-05 ms_figures_supp_figs.qmd
Update readme instructions

@@
   r_seed = 34,
-  frac_reserves = c(0, 0.25, 0.50),
+  frac_reserves = c(0, 0.15, 0.30),
   f_fmsys = c(0, 0.5, 1.00, 2.)
@@
   r_seed = 34,
-  frac_reserves = c(0, 0.25, 0.50),
+  frac_reserves = c(0, 0.15, 0.30),
   f_fmsys = c(0.5, 1.00, 2.)
@@
 
-frac_reserves <- c(0, 0.25, 0.5)
+frac_reserves <- c(0, 0.15, 0.3)
 f_fmsys <- c(0, 0.5, 1.00, 2)
